---
title: |
  Code Notebook 1
subtitle: |
  EU 25 Behavioral Games Survey Experiment 2019: Question Wording Exploration
author:
  - name: Tristan Muno
    email: tristan.muno@uni-mannheim.de
    affiliations:
      - name: University of Mannheim
        department: School of Social Sciences
date: last-modified
date-format: MMMM D, YYYY
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: true
    code-tools: true
    embed-resources: true
execute:
  echo: true
  warning: true
  eval: true
  message: true
---

# Setup {#sec-setup}

```{r}
#| label: setup

start_time <- Sys.time()

options(width = 80)

p_required <- c(
  "tidyverse", # data wrangling
  "here", # relative paths
  "sessioninfo" # session info
)
packages <- rownames(installed.packages())
p_to_install <- p_required[!(p_required %in% packages)]
if (length(p_to_install) > 0) {
  install.packages(p_to_install)
}
sapply(p_required, require, character.only = TRUE)
rm(p_required, p_to_install, packages)
```

Country labels follow the list-element order used throughout the project (25 EU
member states, excluding Luxembourg, Malta, Cyprus).

```{r}
#| label: country-labels

country_labels <- c(
  "Austria",
  "Belgium",
  "Bulgaria",
  "Croatia",
  "Czechia",
  "Denmark",
  "Estonia",
  "Finland",
  "France",
  "Germany",
  "Greece",
  "Hungary",
  "Ireland",
  "Italy",
  "Latvia",
  "Lithuania",
  "Netherlands",
  "Poland",
  "Portugal",
  "Romania",
  "Slovakia",
  "Slovenia",
  "Spain",
  "Sweden",
  "United Kingdom"
)
```

# Load Raw Data {#sec-load}

Each wave is an R list of 25 country dataframes in Dynata wide-export format.
Row 1 of each dataframe holds question wordings (Dynata exports the wording
row immediately below the column headers); row 2 holds Dynata internal import
IDs.
Real respondent rows are identified by `DistributionChannel == "anonymous"`.

```{r}
#| label: load

wave1 <- readRDS(here("data", "01_raw", "Wave1.rds"))
wave2 <- readRDS(here("data", "01_raw", "Wave2.rds"))
wave3 <- readRDS(here("data", "01_raw", "Wave3.rds"))

waves <- list(`1` = wave1, `2` = wave2, `3` = wave3)
```

Verify that each wave is a list of 25 dataframes.

```{r}
#| label: verify-structure

map_int(waves, length)
```

# Sample Sizes {#sec-n}

Respondent counts per country per wave, excluding the wording and import-ID rows
(i.e. keeping only `DistributionChannel == "anonymous"` rows).

```{r}
#| label: sample-sizes

sample_sizes <- map2_dfr(waves, names(waves), function(wave_list, wn) {
  map2_dfr(wave_list, seq_along(wave_list), function(df, i) {
    n_respondents <- df |>
      filter(DistributionChannel == "anonymous") |>
      nrow()
    tibble(
      wave = as.integer(wn),
      country = country_labels[i],
      n_cols = ncol(df),
      n_resp = n_respondents
    )
  })
})

sample_sizes |>
  pivot_wider(
    id_cols = country,
    names_from = wave,
    values_from = n_resp,
    names_prefix = "wave"
  ) |>
  arrange(country) |>
  knitr::kable(
    caption = "Respondents per country per wave (anonymous rows only)"
  )
```

Column counts vary across countries because of country-specific questions.
The table below shows how many columns each country dataframe has.

```{r}
#| label: col-counts

sample_sizes |>
  pivot_wider(
    id_cols = country,
    names_from = wave,
    values_from = n_cols,
    names_prefix = "wave"
  ) |>
  arrange(country) |>
  knitr::kable(caption = "Column count per country per wave")
```

# Extract Question Wordings {#sec-wordings}

Row 1 of each country dataframe contains the question wording for every column.
We extract these into a long-format lookup table: one row per
`wave × country × column`.

```{r}
#| label: extract-wordings

extract_wordings <- function(wave_list, wave_num, countries) {
  map2_dfr(wave_list, seq_along(wave_list), function(df, i) {
    # row 1 = question wording (Dynata export convention)
    wording_row <- df[1, , drop = FALSE]
    tibble(
      wave = as.integer(wave_num),
      country = countries[i],
      col_name = names(df),
      wording = as.character(wording_row[1, ])
    )
  })
}

wording_map <- map2_dfr(
  waves,
  names(waves),
  ~ extract_wordings(.x, .y, country_labels)
)

glimpse(wording_map)
```

Sanity check: confirm that row-1 values are not real respondent data by
verifying the `DistributionChannel` wording cell is not `"anonymous"`.

```{r}
#| label: sanity-check-wording-row

wording_map |>
  filter(col_name == "DistributionChannel") |>
  count(wave, wording)
```

# Column Coverage {#sec-coverage}

## How many unique column names exist per wave? {#sec-coverage-per-wave}

```{r}
#| label: unique-cols-per-wave

wording_map |>
  group_by(wave) |>
  summarise(n_unique_cols = n_distinct(col_name)) |>
  knitr::kable(caption = "Unique column names per wave")
```

## Common core: columns present in all 75 wave × country combinations {#sec-common-core}

A column is "common core" if it appears in every country in every wave.

```{r}
#| label: common-core

n_combinations <- length(country_labels) * length(waves) # 75

common_core <- wording_map |>
  group_by(col_name) |>
  summarise(n_present = n_distinct(paste(wave, country))) |>
  filter(n_present == n_combinations) |>
  pull(col_name)

cat(
  "Common core columns (present in all 75 wave × country combos):",
  length(common_core),
  "\n"
)
print(common_core)
```

## Wave-specific columns {#sec-wave-specific}

Columns present in at least one wave but absent from at least one other wave
(aggregated across all countries).

```{r}
#| label: wave-specific

wave_presence <- wording_map |>
  group_by(col_name, wave) |>
  summarise(present = TRUE, .groups = "drop") |>
  pivot_wider(
    names_from = wave,
    values_from = present,
    names_prefix = "wave",
    values_fill = FALSE
  )

wave_specific <- wave_presence |>
  filter(!(wave1 & wave2 & wave3))

cat("Columns absent from at least one wave:", nrow(wave_specific), "\n")

wave_specific |>
  arrange(desc(wave1), desc(wave2), desc(wave3)) |>
  knitr::kable(caption = "Wave-specific columns (TRUE = present in that wave)")
```

## Country-specific columns {#sec-country-specific}

Within each wave, columns that appear in fewer than all 25 countries.

```{r}
#| label: country-specific

country_specific <- wording_map |>
  group_by(wave, col_name) |>
  summarise(n_countries = n_distinct(country), .groups = "drop") |>
  filter(n_countries < length(country_labels)) |>
  arrange(wave, n_countries, col_name)

cat(
  "Wave × column combinations present in <25 countries:",
  nrow(country_specific),
  "\n"
)

country_specific |>
  knitr::kable(
    caption = "Country-specific columns: how many of the 25 countries have them"
  )
```

Which countries account for the country-specific columns?

```{r}
#| label: country-specific-who

# Columns absent from some countries: which countries are missing them?
ubiquitous_per_wave <- wording_map |>
  group_by(wave, col_name) |>
  summarise(n_countries = n_distinct(country), .groups = "drop") |>
  filter(n_countries == length(country_labels)) |>
  select(wave, col_name)

country_specific_detail <- wording_map |>
  anti_join(ubiquitous_per_wave, by = c("wave", "col_name")) |>
  group_by(wave, country) |>
  summarise(n_extra_cols = n_distinct(col_name), .groups = "drop") |>
  arrange(wave, desc(n_extra_cols))

country_specific_detail |>
  pivot_wider(
    names_from = wave,
    values_from = n_extra_cols,
    names_prefix = "wave",
    values_fill = 0
  ) |>
  arrange(country) |>
  knitr::kable(
    caption = "Number of country-specific extra columns per country per wave"
  )
```

# Wording Conflicts {#sec-conflicts}

A conflict occurs when the same column name carries different question wordings
across waves.
This is the most dangerous case: a naive `bind_rows()` would silently merge
columns that mean different things.

```{r}
#| label: wording-conflicts

# Collapse to one wording per wave × col_name (take the most common wording
# within that wave, since country translations cause minor variation)
dominant_wording <- wording_map |>
  group_by(wave, col_name, wording) |>
  summarise(n = n(), .groups = "drop") |>
  group_by(wave, col_name) |>
  slice_max(n, n = 1, with_ties = FALSE) |>
  select(wave, col_name, wording)

# Flag col_names whose dominant wording differs across waves
conflicts <- dominant_wording |>
  group_by(col_name) |>
  filter(n_distinct(wording) > 1) |>
  arrange(col_name, wave) |>
  ungroup()

cat(
  "Column names with differing wordings across waves:",
  n_distinct(conflicts$col_name),
  "\n"
)

conflicts |>
  knitr::kable(caption = "Cross-wave wording conflicts")
```

# Save Lookup Table {#sec-save}

The full `wording_map` (one row per wave × country × column) is the load-bearing
artifact for all subsequent renaming decisions.
Edit this CSV to fix naming decisions; do not hard-code renames in pipeline
scripts.

```{r}
#| label: save-wording-map

write_csv(
  wording_map,
  here("data", "02_processed", "question_wording_map.csv")
)

cat(
  "Saved:",
  nrow(wording_map),
  "rows to data/02_processed/question_wording_map.csv\n"
)
```

# Session Info {#sec-session}

```{r}
#| label: exec-time
#| eval: true

end_time <- Sys.time()
cat("Execution time:", round(end_time - start_time, 2), "seconds\n")
```

```{r}
#| label: session-info
#| eval: true

sessioninfo::session_info()
```
