---
title: |
  Code Notebook 2
subtitle: |
  EU 25 Behavioral Games Survey Experiment 2019: Dataset Compilation 1
author:
  - name: Tristan Muno
    email: tristan.muno@uni-mannheim.de
    affiliations:
      - name: University of Mannheim
        department: School of Social Sciences
date: last-modified
date-format: MMMM D, YYYY
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: true
    code-tools: true
    embed-resources: true
execute:
  echo: true
  warning: true
  eval: true
  message: true
---

# Setup {#sec-setup}

```{r}
#| label: setup

start_time <- Sys.time()

options(width = 80)

p_required <- c(
  "tidyverse", # data wrangling
  "here", # relative paths
  "future", # parallel computing
  "furrr", # future backend purrr functions
  "sessioninfo" # session info
)
packages <- rownames(installed.packages())
p_to_install <- p_required[!(p_required %in% packages)]
if (length(p_to_install) > 0) {
  install.packages(p_to_install)
}
sapply(p_required, require, character.only = TRUE)
rm(p_required, p_to_install, packages)
```

Country labels correspond to the positional order of list elements across all
three raw wave files (25 EU member states, excluding Luxembourg, Malta, Cyprus).

```{r}
#| label: country-labels

country_labels <- c(
  "Austria",
  "Belgium",
  "Bulgaria",
  "Croatia",
  "Czechia",
  "Denmark",
  "Estonia",
  "Finland",
  "France",
  "Germany",
  "Greece",
  "Hungary",
  "Ireland",
  "Italy",
  "Latvia",
  "Lithuania",
  "Netherlands",
  "Poland",
  "Portugal",
  "Romania",
  "Slovakia",
  "Slovenia",
  "Spain",
  "Sweden",
  "United Kingdom"
)
```

# Load Data {#sec-load}

Each wave is an R list of 25 country dataframes (Dynata wide-export format).
The question-wording lookup table produced by `01_explore.qmd` is the
load-bearing artifact for all column-name decisions in this notebook.

```{r}
#| label: load

wave1 <- readRDS(here("data", "01_raw", "Wave1.rds"))
wave2 <- readRDS(here("data", "01_raw", "Wave2.rds"))
wave3 <- readRDS(here("data", "01_raw", "Wave3.rds"))

wording_map <- read_csv(
  here("data", "02_processed", "question_wording_map.csv"),
  show_col_types = FALSE
)

# turn df objects to tibble objects
wave1 <- wave1 |>
  map(as_tibble)

wave2 <- wave2 |>
  map(as_tibble)

wave3 <- wave3 |>
  map(as_tibble)

# empty strings to NA
clean_empty_to_na <- function(df) {
  df |>
    mutate(across(where(is.character), ~ na_if(trimws(.x), "")))
}

wave1 <- map(wave1, clean_empty_to_na)
wave2 <- map(wave2, clean_empty_to_na)
wave3 <- map(wave3, clean_empty_to_na)
```

# Phase 1 — Column Name Synchronisation {#sec-phase1}

Dynata assigns numeric choice-IDs when a question includes an open-text
"Other" option.
Because party lists and response-option orderings differ per country, the choice
ID — and therefore the suffix — varies (e.g. `Q4_29_TEXT` vs `Q4_58_TEXT`).
All such variants represent the same logical variable; the canonical name drops
the numeric suffix (`Q4_TEXT`).

No coalescing is required: exploratory analysis confirmed that within every
wave × country combination there is at most one column matching each base
question + `_TEXT` pattern.

## Build the sync map {#sec-phase1-build}

The sync map is derived entirely from `question_wording_map.csv` — no
hand-coded renames.
The rule is: any column whose name matches `Q{n}_{k}_TEXT` is renamed to
`Q{n}_TEXT`.
All other column names are left unchanged.

```{r}
#| label: build-col-sync-map

col_sync_map <- wording_map |>
  # keep only columns whose names carry a numeric choice-ID suffix
  filter(str_detect(col_name, "^Q\\d+_\\d+_TEXT$")) |>
  mutate(
    canonical = str_replace(col_name, "^(Q\\d+)_\\d+_TEXT$", "\\1_TEXT")
  ) |>
  # one entry per wave × country × original name (wordings not needed here)
  distinct(wave, country, col_name, canonical)

cat(
  "Sync-map rows:",
  nrow(col_sync_map),
  "| Unique originals:",
  n_distinct(col_sync_map$col_name),
  "| Unique canonicals:",
  n_distinct(col_sync_map$canonical),
  "\n"
)
```

Summary: how many columns need renaming per wave, aggregated across countries.

```{r}
#| label: sync-map-summary

col_sync_map |>
  group_by(wave) |>
  summarise(
    n_renames = n(),
    n_countries = n_distinct(country),
    n_originals = n_distinct(col_name),
    n_canonicals = n_distinct(canonical),
    .groups = "drop"
  ) |>
  knitr::kable(caption = "Column renames per wave (Phase 1)")
```

Inspect the canonical names that consolidate the most country variants — these
are the "hottest" columns where Dynata numbering diverges the most.

```{r}
#| label: sync-map-top-variants

col_sync_map |>
  group_by(wave, canonical) |>
  summarise(
    n_variants = n_distinct(col_name),
    variants = paste(sort(unique(col_name)), collapse = " | "),
    .groups = "drop"
  ) |>
  filter(n_variants > 1) |>
  arrange(wave, desc(n_variants)) |>
  knitr::kable(
    caption = "Canonical names with >1 original variant across countries"
  )
```

## Apply function {#sec-phase1-apply}

`sync_colnames()` applies the wave- and country-specific subset of the sync map
to a single dataframe.
Columns not in the map are passed through unchanged.

```{r}
#| label: sync-colnames-fn

sync_colnames <- function(df, wave_num, country_name, sync_map) {
  # lookup: original → canonical, for this wave × country only
  lookup <- sync_map |>
    filter(wave == wave_num, country == country_name) |>
    select(col_name, canonical)

  if (nrow(lookup) == 0) {
    return(df)
  }

  # keep only renames for columns that actually exist in df
  lookup <- lookup |> filter(col_name %in% names(df))

  rename(df, !!!setNames(lookup$col_name, lookup$canonical))
}
```

Verify on a spot-check pair: Austria wave 1 (`Q4_29_TEXT → Q4_TEXT`) and
Ireland wave 1 (`Q4_29_TEXT → Q4_TEXT`), plus Bulgaria wave 1 which uses the
divergent `Q4_58_TEXT` form.

```{r}
#| label: phase1-spot-check

check <- function(wave_list, wave_num, country_idx, country_name, orig, canon) {
  df <- wave_list[[country_idx]]
  has_orig <- orig %in% names(df)
  has_canon <- canon %in% names(df)
  df_sync <- sync_colnames(df, wave_num, country_name, col_sync_map)
  after_orig <- orig %in% names(df_sync)
  after_canon <- canon %in% names(df_sync)
  tibble(
    country = country_name,
    wave = wave_num,
    original = orig,
    canonical = canon,
    had_orig = has_orig,
    had_canon = has_canon,
    after_has_orig = after_orig,
    after_has_canon = after_canon,
    ok = has_orig & !has_canon & !after_orig & after_canon
  )
}

spot <- bind_rows(
  # Wave 1: most countries use Q4_29_TEXT
  check(wave1, 1, 1, "Austria", "Q4_29_TEXT", "Q4_TEXT"),
  check(wave1, 1, 13, "Ireland", "Q4_29_TEXT", "Q4_TEXT"),
  # Wave 1 outliers: Belgium uses _30_, UK uses _26_
  check(wave1, 1, 2, "Belgium", "Q4_30_TEXT", "Q4_TEXT"),
  check(wave1, 1, 25, "United Kingdom", "Q4_26_TEXT", "Q4_TEXT"),
  # Wave 2: Bulgaria uses _58_, Czechia uses _31_
  check(wave2, 2, 3, "Bulgaria", "Q4_58_TEXT", "Q4_TEXT"),
  check(wave2, 2, 5, "Czechia", "Q4_31_TEXT", "Q4_TEXT"),
  # Wave 3: same patterns persist
  check(wave3, 3, 3, "Bulgaria", "Q4_58_TEXT", "Q4_TEXT"),
  check(wave3, 3, 5, "Czechia", "Q4_31_TEXT", "Q4_TEXT")
)

knitr::kable(spot, caption = "Phase 1 spot-check: before/after rename")
```

All `ok` values must be `TRUE`.

```{r}
#| label: phase1-spot-check-assert

stopifnot(all(spot$ok, na.rm = TRUE))
cat("Phase 1 spot-check passed.\n")
```

## Column count invariant {#sec-phase1-invariant}

Renaming must not change the number of columns.
Verify for all 75 wave × country combinations.

```{r}
#| label: phase1-col-count

waves <- list(`1` = wave1, `2` = wave2, `3` = wave3)

col_count_check <- map2_dfr(waves, names(waves), function(wave_list, wn) {
  wn_int <- as.integer(wn)
  map2_dfr(wave_list, seq_along(wave_list), function(df, i) {
    ctry <- country_labels[i]
    before <- ncol(df)
    after <- ncol(sync_colnames(df, wn_int, ctry, col_sync_map))
    tibble(wave = wn_int, country = ctry, before, after, ok = before == after)
  })
})

n_fail <- sum(!col_count_check$ok, na.rm = TRUE)
cat("Combinations failing column-count invariant:", n_fail, "\n")
if (n_fail > 0) {
  col_count_check |> filter(!ok) |> print()
}
stopifnot(n_fail == 0)
```

# Phase 2 — Game Data Consolidation {#sec-phase2}

Waves 2 and 3 only; skipped entirely for Wave 1 (which has no games).

Due to Dynata survey branching, each respondent is randomly routed to one
of eleven column-sets per game.
This produces 33 column-sets for the dictator game and 33 for the trust game
(3 canonical games × 11 branching variants each).
Each slot occupies exactly 6 consecutive columns in the raw data:

```
Q{n}_First.Click  Q{n}_Last.Click  Q{n}_Page.Submit  Q{n}_Click.Count
Q{m}_4  Q{m}_5
```

where `Q{n}` is the timing question and `Q{m}_4` / `Q{m}_5` are player 1
and player 2 token allocations.

Because Q-numbers differ per country (Dynata renumbers branching paths
country-by-country), no hardcoded lookup is possible.
Instead, slots are detected by their structural signature in column order.
Instruction-page timing blocks (one before the dict games, one before the trust
games) are detected by scanning backward up to 30 columns from each game
group's first slot, taking the closest 4-column timing block found
(the dict instruction block is not immediately adjacent because Q60's 10 columns
sit between it and the first game slot).
The `Q60` fields holding the randomised attribute order and per-game attribute
values are parsed and split into individual columns in the same consolidation
step.

## Slot detection {#sec-phase2-detect}

`detect_game_slots()` scans column names in order, returning a list of 66
slot objects.
It emits a warning if the count is not exactly 66.

```{r}
#| label: detect-game-slots-fn

detect_game_slots <- function(df) {
  cols <- names(df)
  n <- length(cols)

  timing_sfx <- c("First.Click", "Last.Click", "Page.Submit", "Click.Count")

  slots <- list()
  i <- 1L

  while (i <= n - 5L) {
    window <- cols[i:(i + 5L)]

    t_match <- str_match(
      window[1:4],
      "^(Q\\d+)_(First\\.Click|Last\\.Click|Page\\.Submit|Click\\.Count)$"
    )
    o_match <- str_match(
      window[5:6],
      "^(Q\\d+)_(4|5)$"
    )

    timing_ok <- !any(is.na(t_match)) &&
      n_distinct(t_match[, 2]) == 1 &&
      setequal(t_match[, 3], timing_sfx)
    outcome_ok <- !any(is.na(o_match)) &&
      n_distinct(o_match[, 2]) == 1 &&
      setequal(o_match[, 3], c("4", "5"))

    if (timing_ok && outcome_ok) {
      slots <- c(
        slots,
        list(list(
          timing_q = t_match[1, 2],
          outcome_q = o_match[1, 2],
          firstclick = window[match("First.Click", t_match[, 3])],
          lastclick = window[match("Last.Click", t_match[, 3])],
          pagesubmit = window[match("Page.Submit", t_match[, 3])],
          clickcount = window[match("Click.Count", t_match[, 3])],
          pl1 = window[which(o_match[, 3] == "4") + 4L],
          pl2 = window[which(o_match[, 3] == "5") + 4L]
        ))
      )
      i <- i + 6L
    } else {
      i <- i + 1L
    }
  }

  if (length(slots) != 66L) {
    warning(
      "Expected 66 game slots (33 dict + 33 trust), found ",
      length(slots),
      ". Check column structure."
    )
  }

  slots
}
```

## Consolidation {#sec-phase2-consolidate}

`consolidate_games()` groups the 66 detected slots into 6 canonical games
(slots 1–11 → `dict1`, 12–22 → `dict2`, 23–33 → `dict3`,
34–44 → `trust1`, 45–55 → `trust2`, 56–66 → `trust3`), coalesces the 11
variants per field into 36 canonical game columns (all prefixed `cj_`,
including timing fields — they belong to the conjoint block),
then adds 8 instruction-page timing columns (`cj_dict_instr_*` / `cj_trust_instr_*`
detected positionally as the 4-column timing block immediately preceding each
game group), then parses `Q60_1`–`Q60_8` into 43 attribute columns
(`cj_attr_order` plus 7 attributes × 6 games), and drops all 414 source
columns (396 game + 8 instruction + 10 Q60).
The dict/trust column ordering (dict before trust) matches the survey design.

```{r}
#| label: consolidate-games-fn

consolidate_games <- function(df) {
  slots <- detect_game_slots(df)
  n_slots <- length(slots)
  cols_df <- names(df)

  game_labels <- c("dict1", "dict2", "dict3", "trust1", "trust2", "trust3")
  game_fields <- c(
    "pl1",
    "pl2",
    "firstclick",
    "lastclick",
    "pagesubmit",
    "clickcount"
  )
  attr_fields <- c("nat", "party", "eupos", "rel", "age", "sex", "class")
  timing_sfx <- c("First.Click", "Last.Click", "Page.Submit", "Click.Count")
  sfx_short <- c(
    "First.Click" = "firstclick",
    "Last.Click" = "lastclick",
    "Page.Submit" = "pagesubmit",
    "Click.Count" = "clickcount"
  )

  # Treatment condition lookup: slot index within a group of 11 → label
  treatment_map <- c(
    rep("1_conat_eustance_partisan", 4), # slots 1–4
    rep("2_conat_partisan", 2), # slots 5–6
    rep("3_eunat_eustance", 2), # slots 7–8
    rep("4_somenat", 3) # slots 9–11
  )

  # --- game slot coalescing + treatment detection ---
  game_source_cols <- slots |>
    map(\(s) unlist(s[game_fields])) |>
    unlist() |>
    unique()

  game_cols <- list()
  treatment_cols <- list()

  for (g in seq_along(game_labels)) {
    slot_range <- ((g - 1L) * 11L + 1L):(g * 11L)
    if (max(slot_range) > n_slots) {
      next
    }
    group <- slots[slot_range]

    # coalesce outcome/timing fields as before
    for (fld in game_fields) {
      src_vecs <- map(group, \(s) na_if(df[[s[[fld]]]], ""))
      game_cols[[paste0("cj_", game_labels[g], "_", fld)]] <-
        reduce(src_vecs, coalesce)
    }

    # detect treatment: find which slot within the group has a non-NA pl1 value
    pl1_cols <- map_chr(group, \(s) s[["pl1"]])
    pl1_mat <- map(pl1_cols, \(col) na_if(df[[col]], "")) |>
      map(is.na) |>
      do.call(cbind, args = _) # n_rows × 11 logical matrix; TRUE = missing

    # for each respondent: index of the first non-NA slot (1–11), else NA
    slot_hit <- apply(pl1_mat, 1, \(row) {
      hit <- which(!row)
      if (length(hit) == 0L) NA_integer_ else hit[[1L]]
    })

    treatment_cols[[paste0("cj_", game_labels[g], "_treatment")]] <-
      treatment_map[slot_hit] # NA propagates naturally via integer NA index
  }

  # --- instruction-page timing ---
  instr_source_cols <- character(0)
  instr_cols <- list()

  find_instr_block <- function(slot_idx) {
    slot_col_names <- unlist(slots[[slot_idx]][game_fields])
    slot_start <- min(which(cols_df %in% slot_col_names))
    for (start_pos in (slot_start - 4L):max(1L, slot_start - 30L)) {
      window <- cols_df[start_pos:(start_pos + 3L)]
      t_match <- str_match(
        window,
        "^(Q\\d+)_(First\\.Click|Last\\.Click|Page\\.Submit|Click\\.Count)$"
      )
      if (
        !any(is.na(t_match)) &&
          n_distinct(t_match[, 2]) == 1 &&
          setequal(t_match[, 3], timing_sfx)
      ) {
        return(list(window = window, t_match = t_match))
      }
    }
    NULL
  }

  if (n_slots >= 34L) {
    for (tgt in list(
      list(slot = 1L, label = "dict_instr"),
      list(slot = 34L, label = "trust_instr")
    )) {
      blk <- find_instr_block(tgt$slot)
      if (!is.null(blk)) {
        for (sfx in timing_sfx) {
          col_name <- blk$window[match(sfx, blk$t_match[, 3])]
          instr_cols[[paste0("cj_", tgt$label, "_", sfx_short[[sfx]])]] <-
            na_if(df[[col_name]], "")
          instr_source_cols <- c(instr_source_cols, col_name)
        }
      } else {
        warning("Could not detect instruction timing block before ", tgt$label)
      }
    }
  }

  # --- Q60 attribute parsing ---
  attr_map <- c(
    "2" = "nat",
    "3" = "party",
    "4" = "eupos",
    "5" = "rel",
    "6" = "age",
    "7" = "sex",
    "8" = "class"
  )
  game_6 <- c("dict1", "dict2", "dict3", "trust1", "trust2", "trust3")

  q60_attr_order <- if ("Q60_1" %in% cols_df) df[["Q60_1"]] else NULL

  q60_game_cols <- list()
  for (suffix in names(attr_map)) {
    col <- paste0("Q60_", suffix)
    if (!col %in% cols_df) {
      next
    }
    attr_name <- attr_map[[suffix]]
    split_vals <- str_split(df[[col]], ",")
    for (k in seq_along(game_6)) {
      q60_game_cols[[paste0("cj_", game_6[k], "_", attr_name)]] <-
        map_chr(split_vals, \(v) {
          if (length(v) >= k) str_trim(v[[k]]) else NA_character_
        })
    }
  }

  q60_source_cols <- intersect(paste0("Q60_", 1:10), cols_df)
  all_source_cols <- unique(c(
    game_source_cols,
    instr_source_cols,
    q60_source_cols
  ))

  # --- assemble in canonical order ---
  # treatment column placed right after pl1/pl2, before timing fields
  ordered_cols <- list()

  if (!is.null(q60_attr_order)) {
    ordered_cols[["cj_attr_order_raw"]] <- q60_attr_order
  }

  for (sfx in sfx_short) {
    nm <- paste0("cj_dict_instr_", sfx)
    if (!is.null(instr_cols[[nm]])) ordered_cols[[nm]] <- instr_cols[[nm]]
  }
  for (g in c("dict1", "dict2", "dict3")) {
    for (fld in game_fields) {
      ordered_cols[[paste0("cj_", g, "_", fld)]] <-
        game_cols[[paste0("cj_", g, "_", fld)]]
    }
    ordered_cols[[paste0("cj_", g, "_treatment")]] <-
      treatment_cols[[paste0("cj_", g, "_treatment")]]
    for (af in attr_fields) {
      ordered_cols[[paste0("cj_", g, "_", af, "_raw")]] <-
        q60_game_cols[[paste0("cj_", g, "_", af)]]
    }
  }
  for (sfx in sfx_short) {
    nm <- paste0("cj_trust_instr_", sfx)
    if (!is.null(instr_cols[[nm]])) ordered_cols[[nm]] <- instr_cols[[nm]]
  }
  for (g in c("trust1", "trust2", "trust3")) {
    for (fld in game_fields) {
      ordered_cols[[paste0("cj_", g, "_", fld)]] <-
        game_cols[[paste0("cj_", g, "_", fld)]]
    }
    ordered_cols[[paste0("cj_", g, "_treatment")]] <-
      treatment_cols[[paste0("cj_", g, "_treatment")]]
    for (af in attr_fields) {
      ordered_cols[[paste0("cj_", g, "_", af, "_raw")]] <-
        q60_game_cols[[paste0("cj_", g, "_", af)]]
    }
  }

  ordered_cols <- ordered_cols[!map_lgl(ordered_cols, is.null)]

  bind_cols(
    select(df, -all_of(all_source_cols)),
    as_tibble(ordered_cols)
  )
}
```

## Verification {#sec-phase2-verify}

```{r}
#| label: phase2-slot-check

aut2_raw <- wave2[[1]] |>
  slice(-1, -2) |>
  filter(DistributionChannel == "anonymous")
aut2_slots <- detect_game_slots(aut2_raw)
cat("Austria wave 2 — slots detected:", length(aut2_slots), "\n")
cat(
  "Slot  1: timing =",
  aut2_slots[[1]]$timing_q,
  "| outcome =",
  aut2_slots[[1]]$outcome_q,
  "\n"
)
cat(
  "Slot 12: timing =",
  aut2_slots[[12]]$timing_q,
  "| outcome =",
  aut2_slots[[12]]$outcome_q,
  "\n"
)
cat(
  "Slot 34: timing =",
  aut2_slots[[34]]$timing_q,
  "| outcome =",
  aut2_slots[[34]]$outcome_q,
  "\n"
)
cat(
  "Slot 66: timing =",
  aut2_slots[[66]]$timing_q,
  "| outcome =",
  aut2_slots[[66]]$outcome_q,
  "\n"
)
stopifnot(length(aut2_slots) == 66L)
```

Each respondent should have exactly one non-empty source slot per canonical
game (the hallmark of correct Dynata branching).

```{r}
#| label: phase2-branching-check

dict1_pl1_cols <- map_chr(aut2_slots[1:11], "pl1")

n_filled <- aut2_raw |>
  select(all_of(dict1_pl1_cols)) |>
  mutate(across(everything(), \(x) x != "")) |>
  rowSums(na.rm = TRUE)

cat(
  "Respondents with exactly 1 dict-game-1 slot filled:",
  sum(n_filled == 1, na.rm = TRUE),
  "of",
  nrow(aut2_raw),
  "\n"
)
cat("Respondents with 0 or 1 filled:", sum(n_filled <= 1, na.rm = TRUE), "\n")
cat("Respondents with > 1 filled:", sum(n_filled > 1, na.rm = TRUE), "\n")

stopifnot(all(n_filled <= 1, na.rm = TRUE))
```

Ireland wave 2 uses different Q-numbers — verify the slot count still works.

```{r}
#| label: phase2-ireland-check

irl2_raw <- wave2[[13]] |>
  slice(-1, -2) |>
  filter(DistributionChannel == "anonymous")
irl2_slots <- detect_game_slots(irl2_raw)
cat("Ireland wave 2 — slots detected:", length(irl2_slots), "\n")
cat(
  "Ireland slot 1 outcome Q:",
  irl2_slots[[1]]$outcome_q,
  " (Austria had:",
  aut2_slots[[1]]$outcome_q,
  ")\n"
)
stopifnot(length(irl2_slots) == 66L)
```

After consolidation: 87 canonical `cj_` columns added, 414 source columns
removed (396 game + 8 instruction + 10 Q60), net column count reduction = 414 - 87 = 327.

```{r}
#| label: phase2-col-reduction

aut2_cons <- consolidate_games(aut2_raw)

# 36 game (6 × 6 fields) + 8 instr timing + 42 per-game attrs = 86 matching ^cj_(dict|trust)
# plus cj_attr_order (1) = 87 total cj_ cols
new_cj_game <- names(aut2_cons)[str_detect(
  names(aut2_cons),
  "^cj_(dict|trust)\\d+_(pl|first|last|page|click)"
)]
new_cj_instr <- names(aut2_cons)[str_detect(
  names(aut2_cons),
  "^cj_(dict|trust)_instr_"
)]
new_cj_attrs <- names(aut2_cons)[str_detect(
  names(aut2_cons),
  "^cj_(dict|trust)\\d+_(nat|party|eupos|rel|age|sex|class)_raw$"
)]
cat("Game outcome/timing cols (cj_):", length(new_cj_game), "\n")
cat("Instruction timing cols (cj_):", length(new_cj_instr), "\n")
cat("Per-game attribute cols (cj_):", length(new_cj_attrs), "\n")
cat("cj_attr_order present:", "cj_attr_order" %in% names(aut2_cons), "\n")

remaining_source <- intersect(map_chr(aut2_slots, "pl1"), names(aut2_cons))
cat("Source pl1 cols still present:", length(remaining_source), "\n")
stopifnot(length(remaining_source) == 0)
stopifnot(length(new_cj_game) == 36L)
stopifnot(length(new_cj_instr) == 8L)
stopifnot(length(new_cj_attrs) == 42L)
stopifnot("cj_attr_order_raw" %in% names(aut2_cons))
```

Value spot-check: the first respondent routed to slot 1 should have the same
`pl1` value in the consolidated column as in the raw source.

```{r}
#| label: phase2-value-check

slot1_pl1 <- aut2_slots[[1]]$pl1
r_idx <- which(aut2_raw[[slot1_pl1]] != "")[1]
raw_val <- aut2_raw[[slot1_pl1]][r_idx]
cons_val <- aut2_cons$cj_dict1_pl1[r_idx]
cat("Source", slot1_pl1, ":", raw_val, "| cj_dict1_pl1:", cons_val, "\n")
stopifnot(identical(raw_val, cons_val))
cat("Value check passed.\n")
```

# Phase 3 — Build Per-Wave Datasets {#sec-phase3}

Each per-wave dataset is assembled by:

1. Stripping the question-wording row (row 1 of each country dataframe)
2. Filtering to `DistributionChannel == "anonymous"` (real respondents only)
3. Applying Phase 1 column sync
4. Applying Phase 2 game consolidation (Waves 2 & 3 only)
5. Adding `meta_wave` and `meta_country`
6. `bind_rows()` across all 25 countries — column mismatches become `NA`

```{r}
#| label: build-wave-fn

build_wave <- function(wave_list, wave_num, country_vec, sync_map) {
  map2_dfr(wave_list, seq_along(wave_list), function(df, i) {
    ctry <- country_vec[i]

    df <- df |>
      # strip wording row (row 1) and import-ID row (row 2)
      slice(-1, -2) |>
      # real respondents only
      filter(DistributionChannel == "anonymous") |>
      # Phase 1: canonical column names
      sync_colnames(wave_num, ctry, sync_map)

    # Phase 2: game consolidation (waves 2 and 3 only)
    if (wave_num > 1L) {
      df <- consolidate_games(df)
    }

    df |>
      mutate(
        meta_wave = wave_num,
        meta_country = ctry,
        .before = everything()
      )
  })
}
```

```{r}
#| label: build-waves

plan(multisession, workers = 3L)

wave_results <- future_map(
  list(
    list(wave_list = wave1, wave_num = 1L),
    list(wave_list = wave2, wave_num = 2L),
    list(wave_list = wave3, wave_num = 3L)
  ),
  \(args) {
    build_wave(args$wave_list, args$wave_num, country_labels, col_sync_map)
  },
  .options = furrr_options(seed = NULL)
)

df_wave1 <- wave_results[[1]]
df_wave2 <- wave_results[[2]]
df_wave3 <- wave_results[[3]]

plan(sequential) # restore default after
```

## Row counts {#sec-phase3-rowcounts}

```{r}
#| label: row-counts

row_counts <- bind_rows(
  df_wave1 |> count(meta_wave, meta_country),
  df_wave2 |> count(meta_wave, meta_country),
  df_wave3 |> count(meta_wave, meta_country)
) |>
  pivot_wider(
    id_cols = meta_country,
    names_from = meta_wave,
    values_from = n,
    names_prefix = "wave"
  ) |>
  arrange(meta_country)

knitr::kable(
  row_counts,
  caption = "Respondents per country per wave (anonymous rows only)"
)
```

## Column coverage after sync {#sec-phase3-coverage}

```{r}
#| label: col-coverage

col_coverage <- tibble(
  wave = c(1L, 2L, 3L),
  n_cols = c(ncol(df_wave1), ncol(df_wave2), ncol(df_wave3)),
  n_rows = c(nrow(df_wave1), nrow(df_wave2), nrow(df_wave3))
)

knitr::kable(
  col_coverage,
  caption = "Dimensions of per-wave datasets after Phase 1"
)
```

Confirm that the `_\d+_TEXT` column name pattern is absent from all three
per-wave datasets (i.e. all such columns have been successfully renamed).

```{r}
#| label: no-numbered-text-cols

check_no_numbered_text <- function(df, label) {
  bad <- names(df)[str_detect(names(df), "^Q\\d+_\\d+_TEXT$")]
  if (length(bad) > 0) {
    cat(
      label,
      ": FAIL — remaining numbered-TEXT columns:",
      paste(bad, collapse = ", "),
      "\n"
    )
  } else {
    cat(label, ": OK — no numbered-TEXT columns remain.\n")
  }
  invisible(bad)
}

bad1 <- check_no_numbered_text(df_wave1, "Wave 1")
bad2 <- check_no_numbered_text(df_wave2, "Wave 2")
bad3 <- check_no_numbered_text(df_wave3, "Wave 3")

stopifnot(length(bad1) == 0, length(bad2) == 0, length(bad3) == 0)
```

# Save wave stacked data

```{r}
#| label: save

write_rds(
  df_wave1,
  file = here(
    "data",
    "02_processed",
    "wave1_compiled.rds"
  )
)

write_rds(
  df_wave2,
  file = here(
    "data",
    "02_processed",
    "wave2_compiled.rds"
  )
)

write_rds(
  df_wave3,
  file = here(
    "data",
    "02_processed",
    "wave3_compiled.rds"
  )
)
```

# Session Info {#sec-session}

```{r}
#| label: exec-time
#| eval: true

end_time <- Sys.time()
cat("Execution time:", round(end_time - start_time, 2), "seconds\n")
```

```{r}
#| label: session-info
#| eval: true

sessioninfo::session_info()
```
