---
title: |
  Code Notebook 2
subtitle: |
  EU 25 Behavioral Games Survey Experiment 2019: Clean Wave 1
author:
  - name: Tristan Muno
    email: tristan.muno@uni-mannheim.de
    affiliations:
      - name: University of Mannheim
        department: School of Social Sciences
date: last-modified
date-format: MMMM D, YYYY
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: true
    code-tools: true
    embed-resources: true
execute:
  echo: true
  warning: true
  eval: true
  message: true
---

# Setup {#sec-setup}

```{r}
#| label: setup
start_time <- Sys.time()

options(width = 80)

p_required <- c(
  "tidyverse", # data wrangling
  "here", # relative paths
  "sessioninfo" # session info
)
packages <- rownames(installed.packages())
p_to_install <- p_required[!(p_required %in% packages)]
if (length(p_to_install) > 0) {
  install.packages(p_to_install)
}
sapply(p_required, require, character.only = TRUE)
rm(p_required, p_to_install, packages)
```

```{r}
#| label: load-data
# wave 1 -----------------------------------------------------------------------
df_wave1 <- readRDS(
  here(
    "data",
    "02_processed",
    "wave1_compiled.rds"
  )
)

# load wording map
wording_map <- read_csv(
  here(
    "data",
    "02_processed",
    "question_wording_map.csv"
  )
)
```

# Phase 4: Coalesce

Some variables store identical questions but are split into different columns.

## Wave 1 Framing Questions

```{r}
#| label: explore-w1-framing
# Short console code block to check that these are actually one variable
# ------------------------------------------------------------------------------

wording_map |>
  filter(wave == 1 & country == "Austria") |>
  count(wording, sort = T)

# Q7_1 etc: Markets & Competition
df_wave1 |>
  select(
    Q40_1, # position frame
    Q37_1, #
    Q34_1, #
    Q31_1, #
    Q28_1, #
    Q25_1, #
    Q22_1, # valence frame
    Q19_1, #
    Q16_1, #
    Q13_1, #
    Q10_1, #
    Q7_1 #
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# Q7_2 etc: Security & Defense
df_wave1 |>
  select(
    Q40_2, # position frame
    Q37_2, #
    Q34_2, #
    Q31_2, #
    Q28_2, #
    Q25_2, #
    Q22_2, # valence frame
    Q19_2, #
    Q16_2, #
    Q13_2, #
    Q10_2, #
    Q7_2 #
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# Q7_3 etc: Asylyum & Immigration
df_wave1 |>
  select(
    Q40_3, # position frame
    Q37_3, #
    Q34_3, #
    Q31_3, #
    Q28_3, #
    Q25_3, #
    Q22_3, # valence frame
    Q19_3, #
    Q16_3, #
    Q13_3, #
    Q10_3, #
    Q7_3 #
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# Q7_4 etc: Environment and Energy
df_wave1 |>
  select(
    Q40_4, # position frame
    Q37_4, #
    Q34_4, #
    Q31_4, #
    Q28_4, #
    Q25_4, #
    Q22_4, # valence frame
    Q19_4, #
    Q16_4, #
    Q13_4, #
    Q10_4, #
    Q7_4 #
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# Q7_5 etc: Trade
df_wave1 |>
  select(
    Q40_5, # position frame
    Q37_5, #
    Q34_5, #
    Q31_5, #
    Q28_5, #
    Q25_5, #
    Q22_5, # valence frame
    Q19_5, #
    Q16_5, #
    Q13_5, #
    Q10_5, #
    Q7_5 #
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)


# Q7_6 etc: Agriculture
df_wave1 |>
  select(
    Q40_6, # position frame
    Q37_6, #
    Q34_6, #
    Q31_6, #
    Q28_6, #
    Q25_6, #
    Q22_6, # valence frame
    Q19_6, #
    Q16_6, #
    Q13_6, #
    Q10_6, #
    Q7_6 #
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# Q8 etc Besinnen Sie sich bitte...
df_wave1 |>
  select(Q41, Q38, Q35, Q32, Q29, Q26, Q23, Q20, Q17, Q14, Q11, Q8) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# Q9 etc: In welchem Maß vertrauen Sie...
df_wave1 |>
  select(Q42, Q39, Q36, Q33, Q30, Q27, Q24, Q21, Q18, Q15, Q12, Q9) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)
```

Note: there are two systematically different frames (Valence and Position), each with different wordings across languages, but only one was asked per respondent.

Q7_* are valence framing questions and Q25_* are position framing questions, q8 and q9 are the follow ups

```{r}
#| label: coalesce-w1-framing-vars
df_wave1 <- df_wave1 |>
  mutate(
    # BLOCK I: VALENCE FRAMING -------------------------------------------------
    # market: valence
    Q7_1 = coalesce(
      Q7_1,
      Q10_1,
      Q13_1,
      Q16_1,
      Q19_1,
      Q22_1
    ),
    # Security: valence
    Q7_2 = coalesce(
      Q7_2,
      Q10_2,
      Q13_2,
      Q16_2,
      Q19_2,
      Q22_2
    ),
    # Asylum: valence
    Q7_3 = coalesce(
      Q7_3,
      Q10_3,
      Q13_3,
      Q16_3,
      Q19_3,
      Q22_3
    ),
    # Energy: valence
    Q7_4 = coalesce(
      Q7_4,
      Q10_4,
      Q13_4,
      Q16_4,
      Q19_4,
      Q22_4
    ),
    # Trade: valence
    Q7_5 = coalesce(
      Q7_5,
      Q10_5,
      Q13_5,
      Q16_5,
      Q19_5,
      Q22_5
    ),
    # Agriculture: valence
    Q7_6 = coalesce(
      Q7_6,
      Q10_6,
      Q13_6,
      Q16_6,
      Q19_6,
      Q22_6
    ),
    # BLOCK II: POSITION FRAMING -----------------------------------------------
    # market: position
    Q25_1 = coalesce(
      Q25_1,
      Q28_1,
      Q31_1,
      Q34_1,
      Q37_1,
      Q40_1
    ),
    # security: position
    Q25_2 = coalesce(
      Q25_2,
      Q28_2,
      Q31_2,
      Q34_2,
      Q37_2,
      Q40_2
    ),
    # asylum: position
    Q25_3 = coalesce(
      Q25_3,
      Q28_3,
      Q31_3,
      Q34_3,
      Q37_3,
      Q40_3
    ),
    # environment: position
    Q25_4 = coalesce(
      Q25_4,
      Q28_4,
      Q31_4,
      Q34_4,
      Q37_4,
      Q40_4
    ),
    # trade: position
    Q25_5 = coalesce(
      Q25_5,
      Q28_5,
      Q31_5,
      Q34_5,
      Q37_5,
      Q40_5
    ),
    # agriculture: position
    Q25_6 = coalesce(
      Q25_6,
      Q28_6,
      Q31_6,
      Q34_6,
      Q37_6,
      Q40_6
    ),
    # follow up questions, same for valence and position framing ---------------
    Q8 = coalesce(Q41, Q38, Q35, Q32, Q29, Q26, Q23, Q20, Q17, Q14, Q11, Q8),
    Q9 = coalesce(Q42, Q39, Q36, Q33, Q30, Q27, Q24, Q21, Q18, Q15, Q12, Q9)
  ) |>
  # remove old vars
  select(
    # valence ------------------------------------------------------------------
    -Q10_1,
    -Q13_1,
    -Q16_1,
    -Q19_1,
    -Q22_1,
    -Q10_2,
    -Q13_2,
    -Q16_2,
    -Q19_2,
    -Q22_2,
    -Q10_3,
    -Q13_3,
    -Q16_3,
    -Q19_3,
    -Q22_3,
    -Q10_4,
    -Q13_4,
    -Q16_4,
    -Q19_4,
    -Q22_4,
    -Q10_5,
    -Q13_5,
    -Q16_5,
    -Q19_5,
    -Q22_5,
    -Q10_6,
    -Q13_6,
    -Q16_6,
    -Q19_6,
    -Q22_6,
    # position -----------------------------------------------------------------
    -Q28_1,
    -Q31_1,
    -Q34_1,
    -Q37_1,
    -Q40_1,
    -Q28_2,
    -Q31_2,
    -Q34_2,
    -Q37_2,
    -Q40_2,
    -Q28_3,
    -Q31_3,
    -Q34_3,
    -Q37_3,
    -Q40_3,
    -Q28_4,
    -Q31_4,
    -Q34_4,
    -Q37_4,
    -Q40_4,
    -Q28_5,
    -Q31_5,
    -Q34_5,
    -Q37_5,
    -Q40_5,
    -Q28_6,
    -Q31_6,
    -Q34_6,
    -Q37_6,
    -Q40_6,
    # follow ups ---------------------------------------------------------------
    -Q41,
    -Q38,
    -Q35,
    -Q32,
    -Q29,
    -Q26,
    -Q23,
    -Q20,
    -Q17,
    -Q14,
    -Q11,
    -Q42,
    -Q39,
    -Q36,
    -Q33,
    -Q30,
    -Q27,
    -Q24,
    -Q21,
    -Q18,
    -Q15,
    -Q12,
  )
```

## Wave 1 Priming Questions

Ensure no respondent has >1 values across the spread out variables.

```{r}
#| label: w1-explore-primes
# populist item battery --------------------------------------------------------
df_wave1 |>
  select(
    Q60_1,
    Q63_1,
    Q66_1,
    Q68_1,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave1 |>
  select(
    Q60_2,
    Q63_2,
    Q66_2,
    Q68_2,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave1 |>
  select(
    Q60_3,
    Q63_3,
    Q66_3,
    Q68_3,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave1 |>
  select(
    Q60_4,
    Q63_4,
    Q66_4,
    Q68_4,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave1 |>
  select(
    Q60_5,
    Q63_5,
    Q66_5,
    Q68_5,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave1 |>
  select(
    Q60_6,
    Q63_6,
    Q66_6,
    Q68_6,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave1 |>
  select(
    Q60_7,
    Q63_7,
    Q66_7,
    Q68_7,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# prospective vote -------------------------------------------------------------
df_wave1 |>
  select(
    Q61,
    Q64,
    Q67,
    Q69,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# Text answer for "other" option
df_wave1 |>
  select(
    Q61_TEXT,
    Q64_TEXT,
    Q67_TEXT,
    Q69_TEXT,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# EU long term vs demand of people
df_wave1 |>
  select(
    Q65_1,
    Q71_1
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave1 |>
  select(
    Q65_2,
    Q71_2
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# for greece, filter did not work, hence only for greece no coalesce
```

```{r}
#| label: w1-prime1-coalesce
df_wave1 <- df_wave1 |>
  mutate(
    # condition indicator -------------------------------------------------------
    prime_respresp_condition = case_when(
      !is.na(Q60_1) ~ "responsiveness",
      !is.na(Q63_1) ~ "responsibility",
      !is.na(Q66_1) ~ "control_text",
      !is.na(Q68_1) ~ "control_notext",
    ),
    # populism battery items (conditions → item 1–7) ----------------------------
    Q60_1 = coalesce(Q60_1, Q63_1, Q66_1, Q68_1),
    Q60_2 = coalesce(Q60_2, Q63_2, Q66_2, Q68_2),
    Q60_3 = coalesce(Q60_3, Q63_3, Q66_3, Q68_3),
    Q60_4 = coalesce(Q60_4, Q63_4, Q66_4, Q68_4),
    Q60_5 = coalesce(Q60_5, Q63_5, Q66_5, Q68_5),
    Q60_6 = coalesce(Q60_6, Q63_6, Q66_6, Q68_6),
    Q60_7 = coalesce(Q60_7, Q63_7, Q66_7, Q68_7),
    # prospective vote (conditions → Q61) ---------------------------------------
    Q61 = coalesce(Q61, Q64, Q67, Q69),
    Q61_TEXT = coalesce(Q61_TEXT, Q64_TEXT, Q67_TEXT, Q69_TEXT),
    # EU long-term vs demand of people (non-Greece only) ------------------------
    Q71_1 = if_else(meta_country != "Greece", coalesce(Q71_1, Q65_1), Q71_1),
    Q71_2 = if_else(meta_country != "Greece", coalesce(Q71_2, Q65_2), Q71_2),
    # Greece: branching filter failed, value lives in Q65_* not Q71_*
    Q65_1 = if_else(meta_country != "Greece", NA, Q65_1),
    Q65_2 = if_else(meta_country != "Greece", NA, Q65_2)
  ) |>
  select(
    # drop redundant battery columns -------------------------------------------
    -Q63_1,
    -Q63_2,
    -Q63_3,
    -Q63_4,
    -Q63_5,
    -Q63_6,
    -Q63_7,
    -Q66_1,
    -Q66_2,
    -Q66_3,
    -Q66_4,
    -Q66_5,
    -Q66_6,
    -Q66_7,
    -Q68_1,
    -Q68_2,
    -Q68_3,
    -Q68_4,
    -Q68_5,
    -Q68_6,
    -Q68_7,
    # drop redundant vote columns ----------------------------------------------
    -Q64,
    -Q67,
    -Q69,
    -Q64_TEXT,
    -Q67_TEXT,
    -Q69_TEXT,
  )
```

```{r}
#| label: w1-explore-primes-gridlock
# scales item 1 ---------------------------------------------------------------
df_wave1 |>
  select(
    Q73_1,
    Q78_1,
    Q83_1,
    Q87_1,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# scales item 2 ---------------------------------------------------------------
df_wave1 |>
  select(
    Q73_2,
    Q78_2,
    Q83_2,
    Q87_2,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# scales item 3 ---------------------------------------------------------------
df_wave1 |>
  select(
    Q73_3,
    Q78_3,
    Q83_3,
    Q87_3,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# scales item 4 ---------------------------------------------------------------
df_wave1 |>
  select(
    Q74_1,
    Q79_1,
    Q84_1,
    Q88_1,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# scales item 5 ---------------------------------------------------------------
df_wave1 |>
  select(
    Q74_2,
    Q79_2,
    Q84_2,
    Q88_2,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# party attachment -------------------------------------------------------------
df_wave1 |>
  select(
    Q75,
    Q80,
    Q85,
    Q89,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# closeness -------------------------------------------------------------------
df_wave1 |>
  select(
    Q76,
    Q81,
    Q86,
    Q90,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# Q82_1: no cross-condition equivalent — standalone missingness check ---------
df_wave1 |>
  select(Q82_1) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)
```

```{r}
#| label: w1-coalesce-primes-gridlock
df_wave1 <- df_wave1 |>
  mutate(
    # condition indicator -------------------------------------------------------
    prime_gridlock_condition = case_when(
      !is.na(Q73_1) ~ "gridlock",
      !is.na(Q78_1) ~ "no_gridlock",
      !is.na(Q83_1) ~ "control_text",
      !is.na(Q87_1) ~ "control_notext",
    ),
    # BLOCK: GRIDLOCK PRIMING SCALES (Q73/Q78/Q83/Q87 → Q73) ------------------
    # item 1
    Q73_1 = coalesce(Q73_1, Q78_1, Q83_1, Q87_1),
    # item 2
    Q73_2 = coalesce(Q73_2, Q78_2, Q83_2, Q87_2),
    # item 3
    Q73_3 = coalesce(Q73_3, Q78_3, Q83_3, Q87_3),
    # BLOCK: GRIDLOCK PRIMING SCALES (Q74/Q79/Q84/Q88 → Q74) ------------------
    # item 1
    Q74_1 = coalesce(Q74_1, Q79_1, Q84_1, Q88_1),
    # item 2
    Q74_2 = coalesce(Q74_2, Q79_2, Q84_2, Q88_2),
    # BLOCK: PARTY ATTACHMENT (Q75/Q80/Q85/Q89 → Q75) -------------------------
    Q75 = coalesce(Q75, Q80, Q85, Q89),
    Q75_TEXT = coalesce(Q75_TEXT, Q80_TEXT, Q85_TEXT, Q89_TEXT),
    # BLOCK: CLOSENESS (Q76/Q81/Q86/Q90 → Q76) --------------------------------
    Q76 = coalesce(Q76, Q81, Q86, Q90),
  ) |>
  select(
    # Q73 scale duplicates ------------------------------------------------------
    -Q78_1,
    -Q83_1,
    -Q87_1,
    -Q78_2,
    -Q83_2,
    -Q87_2,
    -Q78_3,
    -Q83_3,
    -Q87_3,
    # Q74 scale duplicates ------------------------------------------------------
    -Q79_1,
    -Q84_1,
    -Q88_1,
    -Q79_2,
    -Q84_2,
    -Q88_2,
    # party attachment duplicates -----------------------------------------------
    -Q80,
    -Q85,
    -Q89,
    -Q80_TEXT,
    -Q85_TEXT,
    -Q89_TEXT,
    # closeness duplicates ------------------------------------------------------
    -Q81,
    -Q86,
    -Q90,
  )
```


```{r}
#| label: w1-compliance-exp-explore
# timings ----------------------------------------------------------------------
df_wave1 |>
  select(
    Q91_First.Click,
    Q94_First.Click,
    Q98_First.Click,
    Q102_First.Click,
    Q106_First.Click,
    Q110_First.Click,
    Q114_First.Click,
    Q118_First.Click,
    Q122_First.Click,
    Q126_First.Click,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave1 |>
  select(
    Q91_Last.Click,
    Q94_Last.Click,
    Q98_Last.Click,
    Q102_Last.Click,
    Q106_Last.Click,
    Q110_Last.Click,
    Q114_Last.Click,
    Q118_Last.Click,
    Q122_Last.Click,
    Q126_Last.Click,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave1 |>
  select(
    Q91_Page.Submit,
    Q94_Page.Submit,
    Q98_Page.Submit,
    Q102_Page.Submit,
    Q106_Page.Submit,
    Q110_Page.Submit,
    Q114_Page.Submit,
    Q118_Page.Submit,
    Q122_Page.Submit,
    Q126_Page.Submit,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave1 |>
  select(
    Q91_Click.Count,
    Q94_Click.Count,
    Q98_Click.Count,
    Q102_Click.Count,
    Q106_Click.Count,
    Q110_Click.Count,
    Q114_Click.Count,
    Q118_Click.Count,
    Q122_Click.Count,
    Q126_Click.Count,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)


# approval nat. gov ------------------------------------------------------------
df_wave1 |>
  select(
    Q93,
    Q96,
    Q100,
    Q104,
    Q108,
    Q112,
    Q116,
    Q120,
    Q124,
    Q128,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# approval EU ------------------------------------------------------------------
df_wave1 |>
  select(
    Q97,
    Q101,
    Q105,
    Q109,
    Q113,
    Q117,
    Q121,
    Q125,
    Q129,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# Q130 standalone --------------------------------------------------------------
df_wave1 |>
  select(Q130) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)
```

```{r}
#| label: w1-compliance-exp-coalesce
df_wave1 <- df_wave1 |>
  mutate(
    # condition indicator --------------------------------------------------------
    prime_compliance_condition = case_when(
      !is.na(Q91_First.Click) ~ "nat_legislation",
      !is.na(Q94_First.Click) ~ "transpose",
      !is.na(Q98_First.Click) ~ "no_transpose_sanction",
      !is.na(Q102_First.Click) ~ "no_transpose_sanction_consistency",
      !is.na(Q106_First.Click) ~ "no_transpose_sanction_economic",
      !is.na(Q110_First.Click) ~ "no_transpose_sanction_legality",
      !is.na(Q114_First.Click) ~ "no_transpose_sanction_reputation",
      !is.na(Q118_First.Click) ~ "no_transpose_nosanction",
      !is.na(Q122_First.Click) ~ "no_transpose_nosanction_consistency",
      !is.na(Q126_First.Click) ~ "no_transpose_nosanction_reputation"
    ),
    # timing: First.Click --------------------------------------------------------
    Q91_First.Click = coalesce(
      Q91_First.Click,
      Q94_First.Click,
      Q98_First.Click,
      Q102_First.Click,
      Q106_First.Click,
      Q110_First.Click,
      Q114_First.Click,
      Q118_First.Click,
      Q122_First.Click,
      Q126_First.Click
    ),
    # timing: Last.Click ---------------------------------------------------------
    Q91_Last.Click = coalesce(
      Q91_Last.Click,
      Q94_Last.Click,
      Q98_Last.Click,
      Q102_Last.Click,
      Q106_Last.Click,
      Q110_Last.Click,
      Q114_Last.Click,
      Q118_Last.Click,
      Q122_Last.Click,
      Q126_Last.Click
    ),
    # timing: Page.Submit --------------------------------------------------------
    Q91_Page.Submit = coalesce(
      Q91_Page.Submit,
      Q94_Page.Submit,
      Q98_Page.Submit,
      Q102_Page.Submit,
      Q106_Page.Submit,
      Q110_Page.Submit,
      Q114_Page.Submit,
      Q118_Page.Submit,
      Q122_Page.Submit,
      Q126_Page.Submit
    ),
    # timing: Click.Count --------------------------------------------------------
    Q91_Click.Count = coalesce(
      Q91_Click.Count,
      Q94_Click.Count,
      Q98_Click.Count,
      Q102_Click.Count,
      Q106_Click.Count,
      Q110_Click.Count,
      Q114_Click.Count,
      Q118_Click.Count,
      Q122_Click.Count,
      Q126_Click.Count
    ),
    # approval nat. gov ----------------------------------------------------------
    Q93 = coalesce(
      Q93,
      Q96,
      Q100,
      Q104,
      Q108,
      Q112,
      Q116,
      Q120,
      Q124,
      Q128
    ),
    # approval EU ----------------------------------------------------------------
    Q97 = coalesce(
      Q97,
      Q101,
      Q105,
      Q109,
      Q113,
      Q117,
      Q121,
      Q125,
      Q129
    )
  ) |>
  select(
    # timing duplicates ----------------------------------------------------------
    -Q94_First.Click,
    -Q98_First.Click,
    -Q102_First.Click,
    -Q106_First.Click,
    -Q110_First.Click,
    -Q114_First.Click,
    -Q118_First.Click,
    -Q122_First.Click,
    -Q126_First.Click,
    -Q94_Last.Click,
    -Q98_Last.Click,
    -Q102_Last.Click,
    -Q106_Last.Click,
    -Q110_Last.Click,
    -Q114_Last.Click,
    -Q118_Last.Click,
    -Q122_Last.Click,
    -Q126_Last.Click,
    -Q94_Page.Submit,
    -Q98_Page.Submit,
    -Q102_Page.Submit,
    -Q106_Page.Submit,
    -Q110_Page.Submit,
    -Q114_Page.Submit,
    -Q118_Page.Submit,
    -Q122_Page.Submit,
    -Q126_Page.Submit,
    -Q94_Click.Count,
    -Q98_Click.Count,
    -Q102_Click.Count,
    -Q106_Click.Count,
    -Q110_Click.Count,
    -Q114_Click.Count,
    -Q118_Click.Count,
    -Q122_Click.Count,
    -Q126_Click.Count,
    # approval duplicates --------------------------------------------------------
    -Q96,
    -Q100,
    -Q104,
    -Q108,
    -Q112,
    -Q116,
    -Q120,
    -Q124,
    -Q128,
    -Q101,
    -Q105,
    -Q109,
    -Q113,
    -Q117,
    -Q121,
    -Q125,
    -Q129,
  )
```

```{r}
#| label: w1-court-exp-explore
# timings ----------------------------------------------------------------------
df_wave1 |>
  select(
    Q135_First.Click,
    Q138_First.Click,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave1 |>
  select(
    Q135_Last.Click,
    Q138_Last.Click,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave1 |>
  select(
    Q135_Page.Submit,
    Q138_Page.Submit,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave1 |>
  select(
    Q135_Click.Count,
    Q138_Click.Count,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# scale item 1 -----------------------------------------------------------------
df_wave1 |>
  select(
    Q137_1,
    Q140_1,
    Q142_1,
    Q143_1,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# scale item 2 -----------------------------------------------------------------
df_wave1 |>
  select(
    Q137_2,
    Q140_2,
    Q142_2,
    Q143_2,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# Q141 ------------------------------------------------------------------------
df_wave1 |>
  select(Q141, Q144, Q142) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)
```

```{r}
#| label: w1-court-exp-coalesce
df_wave1 <- df_wave1 |>
  mutate(
    # control_text and control_notext arms have no timing vars (Dynata export omission), so condition is inferred from outcome columns Q141 / Q143_1 instead of click timings
    # condition indicator --------------------------------------------------------
    prime_court_condition = case_when(
      !is.na(Q135_First.Click) ~ "majority",
      !is.na(Q138_First.Click) ~ "minority",
      !is.na(Q141) ~ "control_text",
      !is.na(Q143_1) ~ "control_notext"
    ),
    # timing: First.Click --------------------------------------------------------
    Q135_First.Click = coalesce(
      Q135_First.Click,
      Q138_First.Click
    ),
    # timing: Last.Click ---------------------------------------------------------
    Q135_Last.Click = coalesce(
      Q135_Last.Click,
      Q138_Last.Click
    ),
    # timing: Page.Submit --------------------------------------------------------
    Q135_Page.Submit = coalesce(
      Q135_Page.Submit,
      Q138_Page.Submit
    ),
    # timing: Click.Count --------------------------------------------------------
    Q135_Click.Count = coalesce(
      Q135_Click.Count,
      Q138_Click.Count
    ),
    # scale item 1 ---------------------------------------------------------------
    Q137_1 = coalesce(
      Q137_1,
      Q140_1,
      Q142_1,
      Q143_1,
      Q141_1 # Poland
    ),
    # scale item 2 ---------------------------------------------------------------
    Q137_2 = coalesce(
      Q137_2,
      Q140_2,
      Q142_2,
      Q143_2,
      Q141_2 # Poland
    ),
    # Court Assessment
    Q141 = coalesce(
      Q141,
      Q142, # Poland
      Q144
    )
  ) |>
  select(
    # timing duplicates ----------------------------------------------------------
    -Q138_First.Click,
    -Q138_Last.Click,
    -Q138_Page.Submit,
    -Q138_Click.Count,
    # scale duplicates -----------------------------------------------------------
    -Q140_1,
    -Q142_1,
    -Q143_1,
    -Q140_2,
    -Q142_2,
    -Q143_2,
    -Q144,
    -Q142,
    -Q141_1,
    -Q141_2
  )
```

```{r}
#| label: w1-immigr-econ-exp-explore
# EU self ------------------------------------------------------------------
df_wave1 |>
  select(
    Q160,
    Q166,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# EU party placements ----------------------------------------------------------
df_wave1 |>
  select(
    Q161_1,
    Q167_1,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave1 |>
  select(
    Q161_2,
    Q167_2,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave1 |>
  select(
    Q161_3,
    Q167_3,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave1 |>
  select(
    Q161_4,
    Q167_4,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave1 |>
  select(
    Q161_5,
    Q167_5,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)


df_wave1 |>
  select(
    Q161_6,
    Q167_6,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave1 |>
  select(
    Q161_7,
    Q167_7,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave1 |>
  select(
    Q161_8,
    Q167_8,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave1 |>
  select(
    Q161_9,
    Q167_9,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave1 |>
  select(
    Q161_10,
    Q167_10,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# EU bodies placements ---------------------------------------------------------
df_wave1 |>
  select(
    Q162_1,
    Q168_1
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave1 |>
  select(
    Q162_2,
    Q168_2
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave1 |>
  select(
    Q162_3,
    Q168_3
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave1 |>
  select(
    Q162_4,
    Q168_4
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave1 |>
  select(
    Q162_5,
    Q168_5
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# Econ eval rel. 12 months ago -------------------------------------------------
df_wave1 |>
  select(
    Q163,
    Q169
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# Econ responsible nat gov -----------------------------------------------------
df_wave1 |>
  select(
    Q164_1,
    Q170_1
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# Econ responsible EU -----------------------------------------------------
df_wave1 |>
  select(
    Q164_2,
    Q170_2
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# Econ responsible global econ -----------------------------------------------------
df_wave1 |>
  select(
    Q164_4,
    Q170_3
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# News consumption -------------------------------------------------------------
df_wave1 |>
  select(
    Q165_1,
    Q171_1
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave1 |>
  select(
    Q165_2,
    Q171_2
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave1 |>
  select(
    Q165_3,
    Q171_3
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)
```

```{r}
#| label: w1-immigr-econ-exp-coalesce
df_wave1 <- df_wave1 |>
  mutate(
    # condition indicator --------------------------------------------------------
    prime_econblame_condition = case_when(
      !is.na(Q164_3) ~ "immigration_displayed",
      !is.na(Q170_3) ~ "immigration_not_displayed"
    ),
    Q160 = coalesce(Q160, Q166),
    # party EU placements
    Q161_1 = coalesce(Q161_1, Q167_1),
    Q161_2 = coalesce(Q161_2, Q167_2),
    Q161_3 = coalesce(Q161_3, Q167_3),
    Q161_4 = coalesce(Q161_4, Q167_4),
    Q161_5 = coalesce(Q161_5, Q167_5),
    Q161_6 = coalesce(Q161_6, Q167_6),
    Q161_7 = coalesce(Q161_7, Q167_7),
    Q161_8 = coalesce(Q161_8, Q167_8),
    Q161_9 = coalesce(Q161_9, Q167_9),
    Q161_10 = coalesce(Q161_10, Q167_10),
    # EU bodies EU placement
    Q162_1 = coalesce(Q162_1, Q168_1),
    Q162_2 = coalesce(Q162_2, Q168_2),
    Q162_3 = coalesce(Q162_3, Q168_3),
    Q162_4 = coalesce(Q162_4, Q168_4),
    Q162_5 = coalesce(Q162_5, Q168_5),
    # Econ eval 12 mo ago
    Q163 = coalesce(Q163, Q169),
    # econ responsible
    Q164_1 = coalesce(Q164_1, Q170_1),
    Q164_2 = coalesce(Q164_2, Q170_2),
    # Q164_3 is treatment: option to blame immigrants only shown for some
    # did not work in Denmark and Finland
    Q164_3 = if_else(
      meta_country == "Denmark" | meta_country == "Finland",
      coalesce(Q164_3, Q170_3),
      Q164_3
    ),
    Q164_4 = if_else(
      meta_country != "Denmark" & meta_country != "Finland",
      coalesce(Q164_4, Q170_3),
      coalesce(Q164_4, Q170_4)
    ),
    # news consumption
    Q165_1 = coalesce(Q165_1, Q171_1),
    Q165_2 = coalesce(Q165_2, Q171_2),
    Q165_3 = coalesce(Q165_3, Q171_3)
  ) |>
  select(
    -Q166,
    -Q167_1,
    -Q167_2,
    -Q167_3,
    -Q167_4,
    -Q167_5,
    -Q167_6,
    -Q167_7,
    -Q167_8,
    -Q167_9,
    -Q167_10,
    -Q168_1,
    -Q168_2,
    -Q168_3,
    -Q168_4,
    -Q168_5,
    -Q169,
    -Q170_1,
    -Q170_2,
    -Q170_3,
    -Q171_1,
    -Q171_2,
    -Q171_3,
    -Q170_4
  )
```

```{r}
#| label: w1-q147-explore
df_wave1 |>
  select(
    Q147_1,
    Q149_1
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave1 |>
  select(
    Q147_2,
    Q149_2
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)
```

```{r}
#| label: w1-q147-coalesce
df_wave1 <- df_wave1 |>
  mutate(
    Q147_1 = coalesce(Q147_1, Q149_1),
    Q147_2 = coalesce(Q147_2, Q149_2)
  ) |>
  select(
    -Q149_1,
    -Q149_2
  )
```

```{r}
#| label: w1-czechia-q157-correction
# in czechia, q157 and 156 are flipped
df_wave1 <- df_wave1 |>
  mutate(
    # store originals
    Q156_1_tmp = Q156_1,
    Q156_2_tmp = Q156_2,
    Q156_3_tmp = Q156_3,

    Q157_1_tmp = Q157_1,
    Q157_2_tmp = Q157_2,
    Q157_3_tmp = Q157_3,
    Q157_4_tmp = Q157_4,
    Q157_5_tmp = Q157_5,

    # swap only for Czechia
    Q156_1 = if_else(meta_country == "Czechia", Q157_1_tmp, Q156_1),
    Q156_2 = if_else(meta_country == "Czechia", Q157_2_tmp, Q156_2),
    Q156_3 = if_else(meta_country == "Czechia", Q157_3_tmp, Q156_3),
    Q156_4 = if_else(meta_country == "Czechia", Q157_4_tmp, Q156_4),
    Q156_5 = if_else(meta_country == "Czechia", Q157_5_tmp, Q156_5),

    Q157_1 = if_else(meta_country == "Czechia", Q156_1_tmp, Q157_1),
    Q157_2 = if_else(meta_country == "Czechia", Q156_2_tmp, Q157_2),
    Q157_3 = if_else(meta_country == "Czechia", Q156_3_tmp, Q157_3)
  ) |>
  select(
    -ends_with("_tmp"),
    -Q157_4,
    -Q157_5
  )
```


## Wave 1 Variable Structure (remaining, post-Phase 3)

### Conjoint Randomization
- `Q6_1–7` — issue/party order randomization (A–F)

### Conjoint Experiments (party program comparison)
- `Q45/50/55` — timings | `Q46/51/56` — profile pairs (A×B, C×D, E×F)
- `Q47_1–2 / Q52_1–2 / Q57_1–2` — party ratings

### Priming Experiment 1 (responsiveness deficit)
- `Q59` — text | `Q60_1–7` — populism battery | `Q61` — prospective vote

### Priming Experiment 2 (responsibility deficit)
- `Q62` — text | `Q63_1–7` — populism battery | `Q64` — prospective vote

### Priming Experiment 3 (resp./resp. control)
- `Q65` — text | `Q65_1–2` — EU long-term vs. demand | `Q66_1–7` — populism battery | `Q67` — prospective vote

### Priming Experiment 4 (no text control)
- `Q68` — populism battery | `Q69` — prospective vote

### Post-prime items
- `Q70` — validation (if prime 1 or 2 shown)
- `Q71_1–2` — EU long-term vs. demand (if prime 3 NOT shown)

### Priming Experiment: Gridlock (5 conditions)
Each condition: text → agree/disagree scales → party attachment → closeness

| Condition | Text | Scales | Party att. | Closeness |
|-----------|------|--------|------------|-----------|
| Gridlock | Q72 | Q73_1–3, Q74_1–2 | Q75 | Q76 |
| No gridlock | Q77 | Q78_1–3, Q79_1–2 | Q80 | Q81 |
| Control (text) | Q82, Q82_1 | Q83_1–3, Q84_1–2 | Q85 | Q86 |
| Control (no text) | — | Q87_1–3, Q88_1–2 | Q89 | Q90 |

### Compliance Experiments (immigration; 10 conditions)
Each condition: timings → scenario text → approval nat. gov → approval EU (where applicable)

| Condition | Timings | Approval nat. | Approval EU |
|-----------|---------|---------------|-------------|
| National legislation | Q91 | Q93 | — |
| Transpose | Q94 | Q96 | Q97 |
| No transpose + sanction | Q98 | Q100 | Q101 |
| No transpose + sanction (consistency) | Q102 | Q104 | Q105 |
| No transpose + sanction (economic) | Q106 | Q108 | Q109 |
| No transpose + sanction (legality) | Q110 | Q112 | Q113 |
| No transpose + sanction (reputation) | Q114 | Q116 | Q117 |
| No transpose, no sanction | Q118 | Q120 | Q121 |
| No transpose, no sanction (consistency) | Q122 | Q124 | Q125 |
| No transpose, no sanction (reputation) | Q126 | Q128 | Q129 |

- `Q130` — verification (if Q92 shown)

### EU/Court Knowledge & Attitudes
- `Q131_1–5` — informed about EU | `Q132_1–5` — trust in EU
- `Q133_1–2` — CJEU scale | `Q134` — informed about nat. const. court

### Court Experiments (4 conditions)
| Condition | Timings | Text | Scale |
|-----------|---------|------|-------|
| Majority | Q135 | Q136 | Q137_1–2 |
| Minority | Q138 | Q139 | Q140_* |
| Control (text) | — | Q141 | Q142 |
| Control (no text) | — | — | Q143 |

- `Q144` — view of court position (if Q136, Q139, or Q143 shown)

### Attitudes & Outcomes
- `Q145_1–4` — pol. interest (nat/EU), econ nativism, cult. nativism
- `Q146_*` — EU knowledge checks
- `Q147_1–2 / Q149_1–2` — country/personal EU benefit (two versions)
- `Q148 / Q150` — important election issues (two versions)
- `Q151_1–6` — policy attitudes (market, security, asylum, environment, trade, agriculture)
- `Q152_*` — tolerance/plurality | `Q153` — LR self-placement
- `Q154_* / Q155_1–2 / Q156_*` — LR placements (nat parties, nat gov, court, EU bodies)
- `Q157_*` — political efficacy (nat) | `Q158` — voted 2014 EP | `Q159` — retrospective 2014 vote
- `Q160 / Q161_* / Q162_*` — EU integration placements (self, nat parties, EU bodies) [with immigration blame]
- `Q163–Q164_4` — econ eval + responsibility attributions (nat gov, EU, immigrants, global)
- `Q165_1–3` — news consumption (TV, internet, newspaper)
- `Q166–Q171_*` — identical block to Q160–Q165 but **without immigration blame option**
- `Q172` — age left education | `Q173` — current occupation | `Q174` — last occupation
- `Q175` — financial strain (troubles paying bills)


# Rename Wave 1

```{r}
#| label: wave1-rename
df_wave1_renamed <- df_wave1 |>
  rename(
    meta_startdate = StartDate,
    meta_enddate = EndDate,
    meta_status = Status,
    meta_ipaddress = IPAddress,
    meta_progress = Progress,
    meta_duration_s = Duration..in.seconds.,
    meta_finished = Finished,
    meta_recordeddate = RecordedDate,
    meta_responseid = ResponseId,
    meta_recipient_lastname = RecipientLastName,
    meta_recipient_firstname = RecipientFirstName,
    meta_recipient_email = RecipientEmail,
    meta_external_ref = ExternalReference,
    meta_latitude = LocationLatitude,
    meta_longitude = LocationLongitude,
    meta_distchannel = DistributionChannel,
    meta_lang = UserLanguage,
    meta_country_raw = Country,
    meta_psid = PSID,
    meta_pid = PID,
    meta_device = Device,
    # demographics
    q_gender_raw = Q2,
    q_age_raw = Q3_1,
    q_nationality_raw = Q4,
    q_nationality_other_raw = Q4_TEXT,
    q_identity_country_raw = Q5_1,
    q_identity_eu_raw = Q5_2,
    q_identity_europe_raw = Q5_3,
    q_policy_comp_eu_natgov_raw = Q8,
    q_eu_trust_val_raw = Q9,
    # conjoint randomisation (Q6 JS fills 7 form fields with shuffled labels/party order)
    cj_rand_issue_order_raw = Q6_1,
    cj_rand_party_a_raw = Q6_2,
    cj_rand_party_b_raw = Q6_3,
    cj_rand_party_c_raw = Q6_4,
    cj_rand_party_d_raw = Q6_5,
    cj_rand_party_e_raw = Q6_6,
    cj_rand_party_f_raw = Q6_7,
    # policy competence valence (EU vs national govt, 6 policy domains)
    q_policy_comp_val_market_raw = Q7_1,
    q_policy_comp_val_security_raw = Q7_2,
    q_policy_comp_val_immigration_raw = Q7_3,
    q_policy_comp_val_environment_raw = Q7_4,
    q_policy_comp_val_trade_raw = Q7_5,
    q_policy_comp_val_agriculture_raw = Q7_6,
    # policy competence positions (respondent's own position, same 6 domains)
    q_policy_comp_pos_market_raw = Q25_1,
    q_policy_comp_pos_security_raw = Q25_2,
    q_policy_comp_pos_immigration_raw = Q25_3,
    q_policy_comp_pos_environment_raw = Q25_4,
    q_policy_comp_pos_trade_raw = Q25_5,
    q_policy_comp_pos_agriculture_raw = Q25_6,
    # conjoint task 1
    cj_task1_firstclick = Q45_First.Click,
    cj_task1_lastclick = Q45_Last.Click,
    cj_task1_pagesubmit = Q45_Page.Submit,
    cj_task1_clickcount = Q45_Click.Count,
    cj_task1_choice_raw = Q46,
    cj_task1_eval_a_raw = Q47_1,
    cj_task1_eval_b_raw = Q47_2,
    # conjoint task 2
    cj_task2_firstclick = Q50_First.Click,
    cj_task2_lastclick = Q50_Last.Click,
    cj_task2_pagesubmit = Q50_Page.Submit,
    cj_task2_clickcount = Q50_Click.Count,
    cj_task2_choice_raw = Q51,
    cj_task2_eval_c_raw = Q52_1,
    cj_task2_eval_d_raw = Q52_2,
    # conjoint task 3
    cj_task3_firstclick = Q55_First.Click,
    cj_task3_lastclick = Q55_Last.Click,
    cj_task3_pagesubmit = Q55_Page.Submit,
    cj_task3_clickcount = Q55_Click.Count,
    cj_task3_choice_raw = Q56,
    cj_task3_eval_e_raw = Q57_1,
    cj_task3_eval_f_raw = Q57_2,
    # attention check
    q_attn_check_raw = Q58,
    q_attn_check_text = Q58_TEXT,
    # resp. priming — populism outcome battery
    q_pop_will_raw = Q60_1,
    q_pop_people_raw = Q60_2,
    q_pop_elite_raw = Q60_3,
    q_pop_citizen_raw = Q60_4,
    q_pop_reps_raw = Q60_5,
    q_pop_goodevil_raw = Q60_6,
    q_pop_compromise_raw = Q60_7,
    # resp. priming — EU vote intention
    q_eu_vote_2014_raw = Q61,
    q_eu_vote_2014_raw_text = Q61_TEXT,
    # resp. priming — manipulation check (ctrl arm, Greece only)
    q_eu_longterm_gre_raw = Q65_1,
    q_eu_responsive_gre_raw = Q65_2,
    # resp. priming — verification
    q_resp_verif_raw = Q70,
    # resp. priming — manipulation check (treat arm)
    q_eu_longterm_raw = Q71_1,
    q_eu_responsive_raw = Q71_2,
    # gridlock priming — efficacy scales (coalesced across all 4 conditions)
    q_eu_efficacy_understand_raw = Q73_1,
    q_eu_efficacy_care_raw = Q73_2,
    q_eu_efficacy_nosay_raw = Q73_3,
    q_eu_abolish_raw = Q74_1,
    q_eu_satisfaction_raw = Q74_2,
    # gridlock priming — party attachment
    q_party_id_raw = Q75,
    q_party_id_other_raw = Q75_TEXT,
    # gridlock priming — party closeness
    q_party_closeness_raw = Q76,
    # gridlock priming — manipulation check
    q_gridlock_manip_raw = Q82_1,
    # compliance experiment — timing (post-coalesce)
    prime_compliance_firstclick = Q91_First.Click,
    prime_compliance_lastclick = Q91_Last.Click,
    prime_compliance_pagesubmit = Q91_Page.Submit,
    prime_compliance_clickcount = Q91_Click.Count,
    # compliance experiment — approval outcomes
    q_approval_natgov_raw = Q93,
    q_approval_eu_raw = Q97,
    # compliance experiment — verification
    q_compliance_verif_raw = Q130,
    # EU institution knowledge (self-reported informatedness)
    q_eu_informed_com_raw = Q131_1,
    q_eu_informed_cou_raw = Q131_2,
    q_eu_informed_ep_raw = Q131_3,
    q_eu_informed_cjeu_raw = Q131_4,
    q_eu_informed_ecb_raw = Q131_5,
    # EU institution trust
    q_eu_trust_com_raw = Q132_1,
    q_eu_trust_cou_raw = Q132_2,
    q_eu_trust_ep_raw = Q132_3,
    q_eu_trust_cjeu_raw = Q132_4,
    q_eu_trust_ecb_raw = Q132_5,
    # CJEU attitudes
    q_cjeu_abolish_raw = Q133_1,
    q_cjeu_satisfaction_raw = Q133_2,
    # national constitutional court knowledge
    q_natcourt_informed_raw = Q134,
    # court experiment — timing (majority/minority conditions)
    prime_court_firstclick = Q135_First.Click,
    prime_court_lastclick = Q135_Last.Click,
    prime_court_pagesubmit = Q135_Page.Submit,
    prime_court_clickcount = Q135_Click.Count,
    # national constitutional court scale (post-experiment, all conditions)
    q_natcourt_1_raw = Q137_1,
    q_natcourt_2_raw = Q137_2,
    # court position view (control_text condition only)
    q_court_pos_raw = Q141,
    # agree scales
    q_nat_int_raw = Q145_1,
    q_eu_int_raw = Q145_2,
    q_nativ_econ_raw = Q145_3,
    q_nativ_cult_raw = Q145_4,
    # true/false knowledge checks
    q_eu_know_1_raw = Q146_1,
    q_eu_know_2_raw = Q146_2,
    q_eu_know_3_raw = Q146_3,
    q_eu_know_4_raw = Q146_4,
    q_eu_know_5_raw = Q146_5,

    # EU attitudes (block 1)
    q_eu_benefit_nat_raw = Q147_1,
    q_eu_pos_personal_raw = Q147_2,
    q_elec_issue_imp_pos_raw = Q148,
    q_elec_issue_imp_val_raw = Q150,

    # Policy attitudes
    q_pol_market_raw = Q151_1,
    q_pol_security_raw = Q151_2,
    q_pol_immigration_raw = Q151_3,
    q_pol_environment_raw = Q151_4,
    q_pol_trade_raw = Q151_5,
    q_pol_agriculture_raw = Q151_6,

    # Tolerance / plurality
    q_norm_tol_opposition_raw = Q152_1,
    q_norm_order_over_freedom_raw = Q152_2,
    q_norm_disobey_unjustlaw_raw = Q152_3,
    q_norm_disobey_gov_raw = Q152_4,
    q_norm_bypass_law_raw = Q152_5,
    q_norm_gov_bend_law_raw = Q152_6,

    # Ideology
    q_lr_self_raw = Q153,
    q_lr_party_1_raw = Q154_1,
    q_lr_party_2_raw = Q154_2,
    q_lr_party_3_raw = Q154_3,
    q_lr_party_4_raw = Q154_4,
    q_lr_party_5_raw = Q154_5,
    q_lr_party_6_raw = Q154_6,
    q_lr_party_7_raw = Q154_7,
    q_lr_party_8_raw = Q154_8,
    # only in some net/bel cases
    q_lr_party_9_raw = Q154_9,
    q_lr_party_10_raw = Q154_10,
    q_lr_party_11_raw = Q154_11,
    q_lr_party_12_raw = Q154_12,
    q_lr_party_13_raw = Q154_13,

    q_lr_gov_nat_raw = Q155_1,
    q_lr_court_nat_raw = Q155_2,

    q_lr_com_raw = Q156_1,
    q_lr_cou_raw = Q156_2,
    q_lr_ep_raw = Q156_3,
    q_lr_cjeu_raw = Q156_4,
    q_lr_ecb_raw = Q156_5,

    # Political efficacy / informed
    q_eff_internal_raw = Q157_1,
    q_eff_external_resp_raw = Q157_2,
    q_eff_external_nosay_raw = Q157_3,

    # Voting
    q_vote_eu_2014_raw = Q158,
    q_vote_eu_2014_rec_raw = Q159,
    q_vote_eu_2014_rec_text_raw = Q159_TEXT,

    # EU integration & placements
    q_euint_self_raw = Q160,

    q_euint_party_1_raw = Q161_1,
    q_euint_party_2_raw = Q161_2,
    q_euint_party_3_raw = Q161_3,
    q_euint_party_4_raw = Q161_4,
    q_euint_party_5_raw = Q161_5,
    q_euint_party_6_raw = Q161_6,
    q_euint_party_7_raw = Q161_7,
    q_euint_party_8_raw = Q161_8,
    # for belgium
    q_euint_party_9_raw = Q161_9,
    q_euint_party_10_raw = Q161_10,

    q_euint_com_raw = Q162_1,
    q_euint_cou_raw = Q162_2,
    q_euint_ep_raw = Q162_3,
    q_euint_cjeu_raw = Q162_4,
    q_euint_ecb_raw = Q162_5,

    # Economic evaluations
    q_econ_eval_retro_raw = Q163,

    # Economic blame
    q_econ_resp_natgov_raw = Q164_1,
    q_econ_resp_eu_raw = Q164_2,
    q_econ_resp_imm_raw = Q164_3,
    q_econ_resp_global_raw = Q164_4,

    # Media consumption
    q_news_tv_raw = Q165_1,
    q_news_online_raw = Q165_2,
    q_news_print_raw = Q165_3,

    # Socio-demographics
    q_edu_age_stop_raw = Q172_1,
    q_occ_current_raw = Q173,
    q_occ_last_raw = Q174,
    q_fin_strain_raw = Q175
  )
```

# Condensed W1 Question Wordings

```{r}
#| label: w1-question-wordings
rename_vec <- c(
  # demographics
  q_gender_raw = "Q2",
  q_age_raw = "Q3_1",
  q_nationality_raw = "Q4",
  q_nationality_other_raw = "Q4_TEXT",
  q_identity_country_raw = "Q5_1",
  q_identity_eu_raw = "Q5_2",
  q_identity_europe_raw = "Q5_3",
  q_policy_comp_eu_natgov_raw = "Q8",
  q_eu_trust_val_raw = "Q9",
  # conjoint randomisation
  cj_rand_issue_order = "Q6_1",
  cj_rand_party_a = "Q6_2",
  cj_rand_party_b = "Q6_3",
  cj_rand_party_c = "Q6_4",
  cj_rand_party_d = "Q6_5",
  cj_rand_party_e = "Q6_6",
  cj_rand_party_f = "Q6_7",
  # policy competence valence
  q_policy_comp_val_market_raw = "Q7_1",
  q_policy_comp_val_security_raw = "Q7_2",
  q_policy_comp_val_immigration_raw = "Q7_3",
  q_policy_comp_val_environment_raw = "Q7_4",
  q_policy_comp_val_trade_raw = "Q7_5",
  q_policy_comp_val_agriculture_raw = "Q7_6",
  # policy competence positions
  q_policy_comp_pos_market_raw = "Q25_1",
  q_policy_comp_pos_security_raw = "Q25_2",
  q_policy_comp_pos_immigration_raw = "Q25_3",
  q_policy_comp_pos_environment_raw = "Q25_4",
  q_policy_comp_pos_trade_raw = "Q25_5",
  q_policy_comp_pos_agriculture_raw = "Q25_6",
  # conjoint tasks
  cj_task1_choice_raw = "Q46",
  cj_task1_eval_a_raw = "Q47_1",
  cj_task1_eval_b_raw = "Q47_2",
  cj_task2_choice_raw = "Q51",
  cj_task2_eval_c_raw = "Q52_1",
  cj_task2_eval_d_raw = "Q52_2",
  cj_task3_choice_raw = "Q56",
  cj_task3_eval_e_raw = "Q57_1",
  cj_task3_eval_f_raw = "Q57_2",
  # attention check
  q_attn_check_raw = "Q58",
  q_attn_check_text = "Q58_TEXT",
  # populism battery
  q_pop_will_raw = "Q60_1",
  q_pop_people_raw = "Q60_2",
  q_pop_elite_raw = "Q60_3",
  q_pop_citizen_raw = "Q60_4",
  q_pop_reps_raw = "Q60_5",
  q_pop_goodevil_raw = "Q60_6",
  q_pop_compromise_raw = "Q60_7",
  # EU vote intention
  q_eu_vote_2014_raw = "Q61",
  q_eu_vote_2014_raw_text = "Q61_TEXT",
  # manipulation check (ctrl arm, Greece only)
  q_eu_longterm_gre_raw = "Q65_1",
  q_eu_responsive_gre_raw = "Q65_2",
  # verification
  q_resp_verif_raw = "Q70",
  # manipulation check (treat arm)
  q_eu_longterm_raw = "Q71_1",
  q_eu_responsive_raw = "Q71_2",
  # efficacy scales
  q_eu_efficacy_understand_raw = "Q73_1",
  q_eu_efficacy_care_raw = "Q73_2",
  q_eu_efficacy_nosay_raw = "Q73_3",
  q_eu_abolish_raw = "Q74_1",
  q_eu_satisfaction_raw = "Q74_2",
  # party attachment / closeness
  q_party_id_raw = "Q75",
  q_party_id_other_raw = "Q75_TEXT",
  q_party_closeness_raw = "Q76",
  # manipulation check
  q_gridlock_manip_raw = "Q82_1",
  # compliance experiment outcomes
  q_approval_natgov_raw = "Q93",
  q_approval_eu_raw = "Q97",
  q_compliance_verif_raw = "Q130",
  # EU institution knowledge
  q_eu_informed_com_raw = "Q131_1",
  q_eu_informed_cou_raw = "Q131_2",
  q_eu_informed_ep_raw = "Q131_3",
  q_eu_informed_cjeu_raw = "Q131_4",
  q_eu_informed_ecb_raw = "Q131_5",
  # EU institution trust
  q_eu_trust_com_raw = "Q132_1",
  q_eu_trust_cou_raw = "Q132_2",
  q_eu_trust_ep_raw = "Q132_3",
  q_eu_trust_cjeu_raw = "Q132_4",
  q_eu_trust_ecb_raw = "Q132_5",
  # CJEU attitudes
  q_cjeu_abolish_raw = "Q133_1",
  q_cjeu_satisfaction_raw = "Q133_2",
  # national court knowledge
  q_natcourt_informed_raw = "Q134",
  # national court scale
  q_natcourt_1_raw = "Q137_1",
  q_natcourt_2_raw = "Q137_2",
  # court position
  q_court_pos_raw = "Q141",
  # agree scales
  q_nat_int_raw = "Q145_1",
  q_eu_int_raw = "Q145_2",
  q_nativ_econ_raw = "Q145_3",
  q_nativ_cult_raw = "Q145_4",
  # knowledge checks
  q_eu_know_1_raw = "Q146_1",
  q_eu_know_2_raw = "Q146_2",
  q_eu_know_3_raw = "Q146_3",
  q_eu_know_4_raw = "Q146_4",
  q_eu_know_5_raw = "Q146_5",
  # EU attitudes
  q_eu_benefit_nat_raw = "Q147_1",
  q_eu_pos_personal_raw = "Q147_2",
  q_elec_issue_imp_pos_raw = "Q148",
  q_elec_issue_imp_val_raw = "Q150",
  # policy attitudes
  q_pol_market_raw = "Q151_1",
  q_pol_security_raw = "Q151_2",
  q_pol_immigration_raw = "Q151_3",
  q_pol_environment_raw = "Q151_4",
  q_pol_trade_raw = "Q151_5",
  q_pol_agriculture_raw = "Q151_6",
  # tolerance / plurality
  q_norm_tol_opposition_raw = "Q152_1",
  q_norm_order_over_freedom_raw = "Q152_2",
  q_norm_disobey_unjustlaw_raw = "Q152_3",
  q_norm_disobey_gov_raw = "Q152_4",
  q_norm_bypass_law_raw = "Q152_5",
  q_norm_gov_bend_law_raw = "Q152_6",
  # ideology
  q_lr_self_raw = "Q153",
  q_lr_party_1_raw = "Q154_1",
  q_lr_party_2_raw = "Q154_2",
  q_lr_party_3_raw = "Q154_3",
  q_lr_party_4_raw = "Q154_4",
  q_lr_party_5_raw = "Q154_5",
  q_lr_party_6_raw = "Q154_6",
  q_lr_party_7_raw = "Q154_7",
  q_lr_party_8_raw = "Q154_8",
  q_lr_party_9_raw = "Q154_9",
  q_lr_party_10_raw = "Q154_10",
  q_lr_party_11_raw = "Q154_11",
  q_lr_party_12_raw = "Q154_12",
  q_lr_party_13_raw = "Q154_13",
  q_lr_gov_nat_raw = "Q155_1",
  q_lr_court_nat_raw = "Q155_2",
  q_lr_com_raw = "Q156_1",
  q_lr_cou_raw = "Q156_2",
  q_lr_ep_raw = "Q156_3",
  q_lr_cjeu_raw = "Q156_4",
  q_lr_ecb_raw = "Q156_5",
  # political efficacy
  q_eff_internal_raw = "Q157_1",
  q_eff_external_resp_raw = "Q157_2",
  q_eff_external_nosay_raw = "Q157_3",
  # voting
  q_vote_eu_2014_raw = "Q158",
  q_vote_eu_2014_rec_raw = "Q159",
  q_vote_eu_2014_rec_text_raw = "Q159_TEXT",
  # EU integration
  q_euint_self_raw = "Q160",
  q_euint_party_1_raw = "Q161_1",
  q_euint_party_2_raw = "Q161_2",
  q_euint_party_3_raw = "Q161_3",
  q_euint_party_4_raw = "Q161_4",
  q_euint_party_5_raw = "Q161_5",
  q_euint_party_6_raw = "Q161_6",
  q_euint_party_7_raw = "Q161_7",
  q_euint_party_8_raw = "Q161_8",
  q_euint_party_9_raw = "Q161_9",
  q_euint_party_10_raw = "Q161_10",
  q_euint_com_raw = "Q162_1",
  q_euint_cou_raw = "Q162_2",
  q_euint_ep_raw = "Q162_3",
  q_euint_cjeu_raw = "Q162_4",
  q_euint_ecb_raw = "Q162_5",
  # economic evaluations
  q_econ_eval_retro_raw = "Q163",
  q_econ_resp_natgov_raw = "Q164_1",
  q_econ_resp_eu_raw = "Q164_2",
  q_econ_resp_imm_raw = "Q164_3",
  q_econ_resp_global_raw = "Q164_4",
  # media consumption
  q_news_tv_raw = "Q165_1",
  q_news_online_raw = "Q165_2",
  q_news_print_raw = "Q165_3",
  # socio-demographics
  q_edu_age_stop_raw = "Q172_1",
  q_occ_current_raw = "Q173",
  q_occ_last_raw = "Q174",
  q_fin_strain_raw = "Q175"
)

wording_map_w1 <- wording_map |>
  filter(wave == 1, col_name %in% rename_vec) |>
  left_join(
    tibble(col_name = rename_vec, new_name = names(rename_vec)),
    by = "col_name"
  ) |>
  select(col_name, new_name, country, wording)
```

# Overview of Experiments

Wave 1 included 5 priming experiments. The following code adds variables storing the priming treatments (english translation), as these are absent in the data (Source: `data/01_raw/W1_EU25_Survey_Ireland_basic.pdf`).

```{r}
#| label: w1-priming-texts
df_wave1_renamed <- df_wave1_renamed |>
  mutate(
    cj_task_instruction = "Imagine that you are voting for one of the two parties in the upcoming European election. The following summary table shows the party programs issued by these two parties.",
    prime_respresp_text = case_match(
      prime_respresp_condition,
      "responsibility" ~ "Please read the following information about the European Union (EU). Please take your time to read it carefully. Recently, many experts have pointed out that the EU should act upon its long-term goals, even if its decisions sometimes do not respond to the pressing demand of the people. For Page 17 of 90 example, the EU should take necessary measures to protect the environment for the present and future generations, even if this means imposing tough rules on carbon dioxide (CO2) and pollutant emissions without listening to the will of the people. A recent study by leading researchers also finds the evidence to support this view using an advanced statistical method. According to this research, the estimate of what they call “responsibility” of the EU is strikingly lower than many people thought.",
      "control_notext" ~ "",
      "responsiveness" ~ "Please read the following information about the European Union (EU). Please take your time to read it carefully. Recently, many experts have pointed out that the EU should respond to the pressing demand of the people even if it would endanger its long-term goals. For example, the EU should not impose tough rules on carbon dioxide (CO2) and pollutant emissions without listening to the will of the people, even if these actions are necessary to protect the environment for present and future generations. A recent study by leading researchers also finds the evidence to support this view using an advanced statistical method. According to this research, the estimate of what they call “responsiveness” of the EU is strikingly lower than many people thought.",
      "control_text" ~ "In thinking about the European Union (EU) and its decisions more generally, some people argue that it tends to act upon its long-term goals without listening to the pressing demand of the people. On the other hand, others contend that the EU tends to pander to the demand of people, rather than to act upon its long-term goals."
    ),
    prime_gridlock_text = case_match(
      prime_gridlock_condition,
      "control_notext" ~ "",
      "gridlock" ~ "Please read the following information about the European Union (EU). Please take your time to read it carefully. Recently, many experts have pointed out that the EU cannot reach an agreement well, leading to continued conflicts and inaction on important issues. For example, the views and interests of the Member States and the various EU institutions are often very different. As a result, the EU did not promptly address the European refugee crisis in 2015, although swift action was necessary to guarantee secure borders and fair procedures. A recent study by leading researchers also finds the evidence to support this view using an advanced statistical method. According to this research, the estimate of what they call “gridlock” of the EU is strikingly higher than many people thought.",
      "no_gridlock" ~ "Please read the following information about the European Union (EU). Please take your time to read it carefully. Recently, many experts have pointed out that the EU reaches an agreement too easily, rather than representing different views and interests on important issues. For example, the EU has often neglected the different views of the Member States and the various institutions. As a result, the EU made a hasty decision on the European refugee crisis in 2015, although thoughtful action was necessary to guarantee secure borders and fair procedures. A recent study by leading researchers also finds the evidence to support this view using an advanced statistical method. According to this research, the estimate of what they call “gridlock” of the EU is strikingly lower than many people thought.",
      "control_text" ~ "In thinking about the European Union (EU) and its decisions more generally, some people argue that it tends to fail to reach an agreement and generate continued conflicts and inaction on important issues. On the other hand, others contend that the EU tends to reach an agreement too easily, rather than representing different views and interests. When it comes to the question of whether the EU tends to fail to reach an agreement or it tends to reach an agreement too easily, what is your opinion?"
    ),
    prime_compliance_text = case_match(
      prime_compliance_condition,
      "no_transpose_sanction_consistency" ~ "You will now read about a situation our country has faced in the past and will probably face again. Different leaders have handled the situation in different ways. We will describe one approach <SURVEY_COUNTRY> leaders have taken. After describing this scenario, we will ask you questions about their decision. The EU currently will introduce a directive that reforms the current system to handle immigration. This reform is expected to prevent irregular immigrants and improve external border controls. EU countries will have to act to implement this directive in their national law within 20 months. According to the EU treaties, when a country does not adopt a law to transpose the directive, the Commission may refer the case to the Court of Justice of the EU. The Court may then decide on the case and can impose financial penalties on a noncompliant member state. However, the <SURVEY_COUNTRY> government is planning not to transpose it into national law. The <SURVEY_COUNTRY_LEADER> said that this legislation would not help to address the serious problem of irregular immigration. As a result, <SURVEY_COUNTRY> will break a promise made to the EU, and it is very likely to face the financial penalty as the Court of Justice of the EU is very likely to uphold the Commission's enforcement action.",
      "no_transpose_nosanction_consistency" ~ "You will now read about a situation our country has faced in the past and will probably face again. Different leaders have handled the situation in different ways. We will describe one approach <SURVEY_COUNTRY> leaders have taken. After describing this scenario, we will ask you questions about their decision. The EU will introduce a directive that reforms the current system to handle immigration. This reform is expected to prevent irregular immigrants and improve external border controls. EU countries will have to act to implement this directive in their national law within 20 months. According to the EU treaties, when a country does not adopt a law to transpose the directive, the Commission may refer the case to the Court of Justice of the EU. The Court may then decide on the case and can impose financial penalties on a noncompliant member state. However, the <SURVEY_COUNTRY> government is planning not to transpose it into national law. The <SURVEY_COUNTRY_LEADER> said that this legislation would not help to address the serious problem of irregular immigration. Nevertheless, <SURVEY_COUNTRY> is very unlikely to face the financial penalty as the Court of Justice of the EU may not uphold the Commission's enforcement action. However, it will break a promise made to the EU.",
      "no_transpose_sanction_reputation" ~ "You will now read about a situation our country has faced in the past and will probably face again. Different leaders have handled the situation in different ways. We will describe one approach <SURVEY_COUNTRY> leaders have taken. After describing this scenario, we will ask you questions about their decision. The EU will introduce a directive that reforms the current system to handle immigration. This reform is expected to prevent irregular immigrants and improve external border controls. EU countries will have to act to implement this directive in their national law within 20 months. According to the EU treaties, when a country does not adopt a law to transpose the directive, the Commission may refer the case to the Court of Justice of the EU. The Court may then decide on the case and can impose financial penalties on a noncompliant member state. However, the <SURVEY_COUNTRY> government is planning not to transpose it into national law. The <SURVEY_COUNTRY_LEADER> said that this legislation would not help to address the serious problem of irregular immigration. As a result, the government's decision will significantly hurt the reputation of <SURVEY_COUNTRY> in Europe, and it is very likely to face the financial penalty as the Court of Justice of the EU is very likely to uphold the Commission's enforcement action.",
      "transpose" ~ "You will now read about a situation our country has faced in the past and will probably face again. Different leaders have handled the situation in different ways. We will describe one approach <SURVEY_COUNTRY> leaders have taken. After describing this scenario, we will ask you questions about their decision. The EU will introduce a directive that reforms the current system to handle immigration. This reform is expected to prevent irregular immigrants and improve external border controls. EU countries will have to act to implement this directive in their national law within 20 months. According to the EU treaties, when a country does not adopt a law to transpose the directive, the Commission may refer the case to the Court of Justice of the EU. The Court may then decide on the case and can impose financial penalties on a noncompliant member state. Accordingly, the <SURVEY_COUNTRY> government is planning to transpose it into national law. The <SURVEY_COUNTRY_LEADER> said that this legislation would help to address the serious problem of irregular immigration",
      "nat_legislation" ~ "You will now read about a situation our country has faced in the past and will probably face again. Different leaders have handled the situation in different ways. We will describe one approach <SURVEY_COUNTRY> leaders have taken. After describing this scenario, we will ask you questions about their decision. The <SURVEY_COUNTRY> government will introduce legislation that reforms the current system to handle immigration. The <SURVEY_COUNTRY_LEADER> said that this legislation would help to address the serious problem of irregular immigration.",
      "no_transpose_nosanction" ~ "You will now read about a situation our country has faced in the past and will probably face again. Different leaders have handled the situation in different ways. We will describe one approach <SURVEY_COUNTRY> leaders have taken. After describing this scenario, we will ask you questions about their decision. The EU will introduce a directive that reforms the current system to handle immigration. This reform is expected to prevent irregular immigrants and improve external border controls. EU countries will have to act to implement this directive in their national law within 20 months. According to the EU treaties, when a country does not adopt a law to transpose the directive, the Commission may refer the case to the Court of Justice of the EU. The Court may then decide on the case and can impose financial penalties on a noncompliant member state. However, the <SURVEY_COUNTRY> government is planning not to transpose it into national law. The <SURVEY_COUNTRY_LEADER> said that this legislation would not help to address the serious problem of irregular immigration. Nevertheless, <SURVEY_COUNTRY> is very unlikely to face the financial penalty as the Court of Justice of the EU may not uphold the Commission's enforcement action.",
      "no_transpose_sanction_economic" ~ "You will now read about a situation our country has faced in the past and will probably face again. Different leaders have handled the situation in different ways. We will describe one approach <SURVEY_COUNTRY> leaders have taken. After describing this scenario, we will ask you questions about their decision. The EU will introduce a directive that reforms the current system to handle immigration. This reform is expected to prevent irregular immigrants and improve external border controls. EU countries will have to act to implement this directive in their national law within 20 months. According to the EU treaties, when a country does not adopt a law to transpose the directive, the Commission may refer the case to the Court of Justice of the EU. The Court may then decide on the case and can impose financial penalties on a noncompliant member state. However, the <SURVEY_COUNTRY> government is planning not to transpose it into national law. The <SURVEY_COUNTRY_LEADER> said that this legislation would not help to address the serious problem of irregular immigration. As a result, the EU will retaliate by imposing significant financial penalty, and <SURVEY_COUNTRY> is very likely to face the financial penalty as the Court of Justice of the EU is very likely to uphold the Commission's enforcement action.",
      "no_transpose_sanction_legality" ~ "You will now read about a situation our country has faced in the past and will probably face again. Different leaders have handled the situation in different ways. We will describe one approach <SURVEY_COUNTRY> leaders have taken. After describing this scenario, we will ask you questions about their decision. The EU will introduce a directive that reforms the current system to handle immigration. This reform is expected to prevent irregular immigrants and improve external border controls. EU countries will have to act to implement this directive in their national law within 20 months. According to the EU treaties, when a country does not adopt a law to transpose the directive, the Commission may refer the case to the Court of Justice of the EU. The Court may then decide on the case and can impose financial penalties on a noncompliant member state. However, the <SURVEY_COUNTRY> government is planning not to transpose it into national law. The <SURVEY_COUNTRY_LEADER> said that this legislation would not help to address the serious problem of irregular immigration. As a result, <SURVEY_COUNTRY> will violate EU law, and it is very likely to face the financial penalty as the Court of Justice of the EU is very likely to uphold the Commission's enforcement action.",
      "no_transpose_sanction" ~ "You will now read about a situation our country has faced in the past and will probably face again. Different leaders have handled the situation in different ways. We will describe one approach <SURVEY_COUNTRY> leaders have taken. After describing this scenario, we will ask you questions about their decision. The EU will introduce a directive that reforms the current system to handle immigration. This reform is expected to prevent irregular immigrants and improve external border controls. EU countries will have to act to implement this directive in their national law within 20 months. According to the EU treaties, when a country does not adopt a law to transpose the directive, the Commission may refer the case to the Court of Justice of the EU. The Court may then decide on the case and can impose financial penalties on a noncompliant member state. However, the <SURVEY_COUNTRY> government is planning not to transpose it into national law. The <SURVEY_COUNTRY_LEADER> said that this legislation would not help to address the serious problem of irregular immigration. As a result, <SURVEY_COUNTRY> is very likely to face the financial penalty as the Court of Justice of the EU is very likely to uphold the Commission's enforcement action.",
      "no_transpose_nosanction_reputation" ~ "You will now read about a situation our country has faced in the past and will probably face again. Different leaders have handled the situation in different ways. We will describe one approach <SURVEY_COUNTRY> leaders have taken. After describing this scenario, we will ask you questions about their decision. The EU will introduce a directive that reforms the current system to handle immigration. This reform is expected to prevent irregular immigrants and improve external border controls. EU countries will have to act to implement this directive in their national law within 20 months. According to the EU treaties, when a country does not adopt a law to transpose the directive, the Commission may refer the case to the Court of Justice of the EU. The Court may then decide on the case and can impose financial penalties on a noncompliant member state. However, the <SURVEY_COUNTRY> government is planning not to transpose it into national law. The <SURVEY_COUNTRY_LEADER> said that this legislation would not help to address the serious problem of irregular immigration. Nevertheless, <SURVEY_COUNTRY> is very unlikely to face the financial penalty as the Court of Justice of the EU may not uphold the Commission's enforcement action. However, the government's decision will significantly hurt the reputation of <SURVEY_COUNTRY> in Europe."
    ),
    prime_court_text = case_match(
      prime_court_condition,
      "minority" ~ "A recent analysis of the Supreme Court of <SURVEY_COUNTRY> decisions finds that the institution strongly favors parties or groups that are opposed to the government over the actions taken by the government. Specifically, this study finds that the Court regularly strikes down legislation passed by the government to protect parties or groups that are opposed to the government.",
      "control_notext" ~ "",
      "majority" ~ "A recent analysis of the Supreme Court of <SURVEY_COUNTRY> decisions finds that the institution strongly favors actions taken by the government over parties or groups that are opposed to the government, when it rules. Specifically, this study finds that the Court regularly upholds legislation passed by the government when it is challenged.",
      "control_text" ~ "In thinking about the Supreme Court of <SURVEY_COUNTRY> decisions more generally, some people argue that it tends to favor actions taken by the government at the expense of parties or groups that are opposed to the government when it rules. Others contend that the Court tends to protect parties or groups that are opposed to the government even if it means striking down actions taken by the government."
    )
  )
```


# Save Cleaned W1 Dataset

```{r}
#| label: save-cleaned-w1
write_rds(
  df_wave1_renamed,
  file = here(
    "data",
    "02_processed",
    "wave1_clean.rds"
  )
)

write_rds(
  wording_map_w1,
  file = here(
    "data",
    "02_processed",
    "wave1_wording.rds"
  )
)
```

# Session Info {#sec-session}

```{r}
#| label: exec-time
#| eval: true
end_time <- Sys.time()
cat("Execution time:", round(end_time - start_time, 2), "seconds\n")
```

```{r}
#| label: session-info
#| eval: true
sessioninfo::session_info()
```
