---
title: |
  Code Notebook 2
subtitle: |
  EU 25 Behavioral Games Survey Experiment 2019: Clean Wave 2
author:
  - name: Tristan Muno
    email: tristan.muno@uni-mannheim.de
    affiliations:
      - name: University of Mannheim
        department: School of Social Sciences
date: last-modified
date-format: MMMM D, YYYY
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: true
    code-tools: true
    embed-resources: true
execute:
  echo: true
  warning: true
  eval: true
  message: true
---

# Setup {#sec-setup}

```{r}
#| label: setup

start_time <- Sys.time()

options(width = 80)

p_required <- c(
  "tidyverse", # data wrangling
  "here", # relative paths
  "knitr",
  "sessioninfo" # session info
)
packages <- rownames(installed.packages())
p_to_install <- p_required[!(p_required %in% packages)]
if (length(p_to_install) > 0) {
  install.packages(p_to_install)
}
sapply(p_required, require, character.only = TRUE)
rm(p_required, p_to_install, packages)
```

```{r}
#| label: load-data

# wave 2 -----------------------------------------------------------------------
df_wave2 <- readRDS(
  here(
    "data",
    "02_processed",
    "wave2_compiled.rds"
  )
)

# load wording map
wording_map <- read_csv(
  here(
    "data",
    "02_processed",
    "question_wording_map.csv"
  )
)
```

# Phase 5: Coalesce

Some variables store identical questions but are split into different columns.

Here I produce a variable overview.

## Wave 2 Block I Overview

Block B1 Demographics
Q2 <- Gender
Q3 <- Age
Q4 <- Nationality
Q4_Text <- if Q4 = Other
Q5_1 <- attachement nat
Q5_2 <- attachement EU
Q5_3 <- attachement Europe
Q6 <- religion
Q7 <- Class

Block Verification 1
Q8 <- Verification/Attention Check
Q8_Text <- Verification/Attention Check

Block Priming Exp1: Further EU
Q9_* <- Timing vars (first.click, last.click etc.)
Q10 <- Priming text (not in data currently): "Please read the following information about the European Union (EU). Please take your time to read it carefully. Recently, many experts have argued that the European integration should be pushed further. They say that to address the main challenges facing the EU and its member countries, their national governments should act in a coordinated way with the other EU countries. Despite the cross-border issues, the national governments of the EU member states have resisted a further transfer of power to the EU. A recent study by leading researchers also finds the evidence to support this view using an advanced statistical method. According to this research, the precise estimate of what they call “EU competence” is strikingly smaller than what many people want."

Block Priming Exp1: EU gone too far
Q11_* <- Timing vars
Q12 <- text (not in data currently): "Please read the following information about the European Union (EU). Please take your time to read it carefully. Recently, many experts have argued that European integration has already gone too far. They say that to address the main challenges facing the EU and its member countries, their national governments should act independently to tailor their policies to the specific demands of their countries. Over time, the EU has expanded the range of its activities dramatically to cover almost every conceivable area of political, economic, and social life. A recent study by leading researchers also finds the evidence to support this view using an advanced statistical method. According to this research, the precise estimate of what they call “EU competence” is strikingly larger than what many people want."

Block Priming Exp1: EU gone too far econ
Q13_* <- Timing
Q14 <- Txt: "Please read the following information about the European Union (EU). Please take your time to read it carefully. Recently, many experts have argued that European integration has already gone too far. They say that to address the main challenges facing the EU and its member countries, their national governments should act independently to tailor their policies to the specific demands of their countries. Over time, the EU has expanded the range of its activities dramatically to cover almost every conceivable area of political, economic, and social life. A recent study by leading researchers also finds the evidence to support this view using an advanced statistical method. According to this research, the precise estimate of what they call “EU competence” is strikingly larger than what many people want. As a result, this situation will eventually have a negative impact on Ireland's economy, as seen in the recent economic crisis."

Block Priming Exp1: EU gone too far culture
Q15_* <- Timings
Q16 <- text: "Please read the following information about the European Union (EU). Please take your time to read it carefully. Recently, many experts have argued that European integration has already gone too far. They say that to address the main challenges facing the EU and its member countries, their national governments should act independently to tailor their policies to the specific demands of their countries. Over time, the EU has expanded the range of its activities dramatically to cover almost every conceivable area of political, economic, and social life. A recent study by leading researchers also finds the evidence to support this view using an advanced statistical method. According to this research, the precise estimate of what they call “EU competence” is strikingly larger than what many people want. As a result, this situation will eventually undermine our culture and identity, as seen in recent refugee crisis."

Block Priming Exp1: EU gone too far political
Q17_* <- Timings
Q18 <- Text: "Please read the following information about the European Union (EU). Please take your time to read it carefully. Recently, many experts have argued that the European integration has already gone too far. They say that to address the main challenges facing the EU and its member countries, their national governments should act independently to tailor their policies to the specific demands of their countries. Over time, the EU has expanded the range of its activities dramatically to cover almost every conceivable area of political, economic, and social life. A recent study by leading researchers also finds the evidence to support this view using an advanced statistical method. According to this research, the precise estimate of what they call “EU competence” of the EU is strikingly larger than what many people want. As a result, Irish government will lose much power and authority to defend our political status and influence, as seen in recent years."

Block Priming Exp1: EU gone too far control
Q19_* <- Timings
Q20 <- EU integration scale (in data)

Block Priming Exp1: Control 
Q21_1-Q21_3 <- q_eu_efficacy_understand_raw, q_eu_efficacy_care_raw, q_eu_efficacy_nosay_raw
Q22_1 to Q22_6 <- q_pop_will_raw, q_pop_people_raw, q_pop_citizen_raw, q_pop_reps_raw, q_pop_goodevil_raw, q_pop_compromise_raw
Q23_1 to Q23_6 <- q_dem_compromise_raw, q_dem_listen_raw, q_tech_experts_raw, q_tech_leaders_raw, q_party_harm_raw, q_people_incompetent_raw
Q24_1 and Q24_2 <- q_eu_longterm_raw and q_eu_responsive_raw 
Q25_1 to Q25_3 <- q_eu_imp_nat_econ, q_eu_imp_nat_cul, q_eu_imp_nat_pol
Q26_1 and Q26_2 <- q_eu_abolish_raw, q_eu_satisfaction_raw
Q27 <- q_euint_direction_raw

Block Efficacy, populism, responsiveness/responsibility, EU support
Q28_1-Q28_3 <- q_eu_efficacy_understand_raw, q_eu_efficacy_care_raw, q_eu_efficacy_nosay_raw
Q29_1 to Q29_6 <- q_pop_will_raw, q_pop_people_raw, q_pop_citizen_raw, q_pop_reps_raw, q_pop_goodevil_raw, q_pop_compromise_raw
Q30_1 to Q30_6 <- q_dem_compromise_raw, q_dem_listen_raw, q_tech_experts_raw, q_tech_leaders_raw, q_party_harm_raw, q_people_incompetent_raw
Q31_1 and Q31_2 <- q_eu_longterm_raw and q_eu_responsive_raw
Q32_1 to Q32_3 <- q_eu_imp_nat_econ, q_eu_imp_nat_cul, q_eu_imp_nat_pol
Q33_1 and Q33_2 <- q_eu_abolish_raw, q_eu_satisfaction_raw
Q34 <- q_euint_direction_raw

## Check W2 Priming Exp 1

Before coalescing, I need to check that respondents were shown at most one of the respective questions. The code below implmements this in the following logic: select the variables for which you wish to check, then count how many non-NA values are in these selected variables for each respondent, i.e., row. If the resulting counts are <= 1, we're good.

```{r}
#| label: w2-prime1-explore

# Check respondents received only 1 prime max ----------------------------------

df_wave2 |>
  select(
    Q9_Click.Count,
    Q11_Click.Count,
    Q13_Click.Count,
    Q15_Click.Count,
    Q17_Click.Count,
    Q19_Click.Count
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q9_First.Click,
    Q11_First.Click,
    Q13_First.Click,
    Q15_First.Click,
    Q17_First.Click,
    Q19_First.Click
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q9_Last.Click,
    Q11_Last.Click,
    Q13_Last.Click,
    Q15_Last.Click,
    Q17_Last.Click,
    Q19_Last.Click
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q9_Page.Submit,
    Q11_Page.Submit,
    Q13_Page.Submit,
    Q15_Page.Submit,
    Q17_Page.Submit,
    Q19_Page.Submit
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# Efficacy items ---------------------------------------------------------------
df_wave2 |>
  select(
    Q21_1,
    Q28_1,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q21_2,
    Q28_2
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q21_3,
    Q28_3
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)


# Pop Items --------------------------------------------------------------------

df_wave2 |>
  select(
    Q22_1,
    Q29_1,
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q22_2,
    Q29_2
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q22_3,
    Q29_3
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q22_4,
    Q29_4
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q22_5,
    Q29_5
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q22_6,
    Q29_6
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# Dem/Tech/Pop items
df_wave2 |>
  select(
    Q23_1,
    Q30_1
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q23_2,
    Q30_2
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q23_3,
    Q30_3
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q23_4,
    Q30_4
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q23_5,
    Q30_5
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q23_6,
    Q30_6
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# EU longterm ------------------------------------------------------------------
df_wave2 |>
  select(
    Q24_1,
    Q31_1
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# EU responsiveness ------------------------------------------------------------
df_wave2 |>
  select(
    Q24_2,
    Q31_2
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# EU impact items --------------------------------------------------------------
# EU longterm ------------------------------------------------------------------
df_wave2 |>
  select(
    Q25_1,
    Q32_1
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q25_2,
    Q32_2
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q25_3,
    Q32_3
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# more EU items ----------------------------------------------------------------
df_wave2 |>
  select(
    Q26_1,
    Q33_1
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q26_2,
    Q33_2
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q27,
    Q34
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# Check for France extra -------------------------------------------------------
# Efficacy items ---------------------------------------------------------------
df_wave2 |>
  select(
    Q21_1,
    Q28_1,
    Q35_1
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q21_2,
    Q28_2,
    Q35_2
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q21_3,
    Q28_3,
    Q35_3
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)


# Pop Items --------------------------------------------------------------------

df_wave2 |>
  select(
    Q22_1,
    Q29_1,
    Q36_1
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q22_2,
    Q29_2,
    Q36_2
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q22_3,
    Q29_3,
    Q36_3
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q22_4,
    Q29_4,
    Q36_4
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q22_5,
    Q29_5,
    Q36_5
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q22_6,
    Q29_6,
    Q36_6
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# Dem/Tech/Pop items
df_wave2 |>
  select(
    Q23_1,
    Q30_1,
    Q37_1
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q23_2,
    Q30_2,
    Q37_2
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q23_3,
    Q30_3,
    Q37_3
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q23_4,
    Q30_4,
    Q37_4
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q23_5,
    Q30_5,
    Q37_5
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q23_6,
    Q30_6,
    Q37_6
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# EU longterm ------------------------------------------------------------------
df_wave2 |>
  select(
    Q24_1,
    Q31_1,
    Q38_1
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# EU responsiveness ------------------------------------------------------------
df_wave2 |>
  select(
    Q24_2,
    Q31_2,
    Q38_2
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# EU impact items --------------------------------------------------------------
df_wave2 |>
  select(
    Q25_1,
    Q32_1,
    Q39_1
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q25_2,
    Q32_2,
    Q39_2
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q25_3,
    Q32_3,
    Q39_3
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# more EU items ----------------------------------------------------------------
df_wave2 |>
  select(
    Q26_1,
    Q33_1,
    Q40_1
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q26_2,
    Q33_2,
    Q40_2
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q27,
    Q34,
    Q41
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)
```

So france needs its own secondary variables...

## Coalesce W2 Priming Exp 1

```{r}
#| label: w2-prime1-coalesce

too_far_base <- "Please read the following information about the European Union (EU). Please take your time to read it carefully. Recently, many experts have argued that European integration has already gone too far. They say that to address the main challenges facing the EU and its member countries, their national governments should act independently to tailor their policies to the specific demands of their countries. Over time, the EU has expanded the range of its activities dramatically to cover almost every conceivable area of political, economic, and social life. A recent study by leading researchers also finds the evidence to support this view using an advanced statistical method. According to this research, the precise estimate of what they call \"EU competence\" is strikingly larger than what many people want."

df_wave2 <- df_wave2 |>
  mutate(
    # condition indicator -------------------------------------------------------
    prime_moreeu_condition = case_when(
      !is.na(Q9_First.Click) ~ "further_eu",
      !is.na(Q11_First.Click) ~ "too_far",
      !is.na(Q13_First.Click) ~ "too_far_econ",
      !is.na(Q15_First.Click) ~ "too_far_culture",
      !is.na(Q17_First.Click) ~ "too_far_political",
      !is.na(Q19_First.Click) ~ "control",
    ),
    # priming text --------------------------------------------------------------
    prime_moreeu_text = case_match(
      prime_moreeu_condition,
      "further_eu" ~ "Please read the following information about the European Union (EU). Please take your time to read it carefully. Recently, many experts have argued that the European integration should be pushed further. They say that to address the main challenges facing the EU and its member countries, their national governments should act in a coordinated way with the other EU countries. Despite the cross-border issues, the national governments of the EU member states have resisted a further transfer of power to the EU. A recent study by leading researchers also finds the evidence to support this view using an advanced statistical method. According to this research, the precise estimate of what they call \"EU competence\" is strikingly smaller than what many people want.",
      "too_far" ~ too_far_base,
      "too_far_econ" ~ paste0(
        too_far_base,
        " As a result, this situation will eventually have a negative impact on <SURVEY_COUNTRY>'s economy, as seen in the recent economic crisis."
      ),
      "too_far_culture" ~ paste0(
        too_far_base,
        " As a result, this situation will eventually undermine our culture and identity, as seen in recent refugee crisis."
      ),
      "too_far_political" ~ paste0(
        too_far_base,
        " As a result, <SURVEY_COUNTRY> government will lose much power and authority to defend our political status and influence, as seen in recent years."
      ),
      "control" ~ "",
    ),
    # coalesce timings (Q9 absorbs Q11, Q13, Q15, Q17, Q19) --------------------
    Q9_First.Click = coalesce(
      Q9_First.Click,
      Q11_First.Click,
      Q13_First.Click,
      Q15_First.Click,
      Q17_First.Click,
      Q19_First.Click
    ),
    Q9_Last.Click = coalesce(
      Q9_Last.Click,
      Q11_Last.Click,
      Q13_Last.Click,
      Q15_Last.Click,
      Q17_Last.Click,
      Q19_Last.Click
    ),
    Q9_Page.Submit = coalesce(
      Q9_Page.Submit,
      Q11_Page.Submit,
      Q13_Page.Submit,
      Q15_Page.Submit,
      Q17_Page.Submit,
      Q19_Page.Submit
    ),
    Q9_Click.Count = coalesce(
      Q9_Click.Count,
      Q11_Click.Count,
      Q13_Click.Count,
      Q15_Click.Count,
      Q17_Click.Count,
      Q19_Click.Count
    ),
    # coalesce outcome variables (Q21 absorbs Q28, etc.) -----------------------
    Q21_1 = coalesce(Q21_1, Q28_1),
    Q21_2 = coalesce(Q21_2, Q28_2),
    Q21_3 = coalesce(Q21_3, Q28_3),
    Q22_1 = coalesce(Q22_1, Q29_1),
    Q22_2 = coalesce(Q22_2, Q29_2),
    Q22_3 = coalesce(Q22_3, Q29_3),
    Q22_4 = coalesce(Q22_4, Q29_4),
    Q22_5 = coalesce(Q22_5, Q29_5),
    Q22_6 = coalesce(Q22_6, Q29_6),
    Q23_1 = coalesce(Q23_1, Q30_1),
    Q23_2 = coalesce(Q23_2, Q30_2),
    Q23_3 = coalesce(Q23_3, Q30_3),
    Q23_4 = coalesce(Q23_4, Q30_4),
    Q23_5 = coalesce(Q23_5, Q30_5),
    Q23_6 = coalesce(Q23_6, Q30_6),
    Q24_1 = coalesce(Q24_1, Q31_1),
    Q24_2 = coalesce(Q24_2, Q31_2),
    Q25_1 = coalesce(Q25_1, Q32_1),
    Q25_2 = coalesce(Q25_2, Q32_2),
    Q25_3 = coalesce(Q25_3, Q32_3),
    Q26_1 = coalesce(Q26_1, Q33_1),
    Q26_2 = coalesce(Q26_2, Q33_2),
    Q20 = coalesce(Q20, Q27, Q34)
  ) |>
  select(
    # drop redundant timing columns --------------------------------------------
    -Q11_First.Click,
    -Q11_Last.Click,
    -Q11_Page.Submit,
    -Q11_Click.Count,
    -Q13_First.Click,
    -Q13_Last.Click,
    -Q13_Page.Submit,
    -Q13_Click.Count,
    -Q15_First.Click,
    -Q15_Last.Click,
    -Q15_Page.Submit,
    -Q15_Click.Count,
    -Q17_First.Click,
    -Q17_Last.Click,
    -Q17_Page.Submit,
    -Q17_Click.Count,
    -Q19_First.Click,
    -Q19_Last.Click,
    -Q19_Page.Submit,
    -Q19_Click.Count,
    # drop redundant outcome columns ------------------------------------------
    -Q27,
    -Q28_1,
    -Q28_2,
    -Q28_3,
    -Q29_1,
    -Q29_2,
    -Q29_3,
    -Q29_4,
    -Q29_5,
    -Q29_6,
    -Q30_1,
    -Q30_2,
    -Q30_3,
    -Q30_4,
    -Q30_5,
    -Q30_6,
    -Q31_1,
    -Q31_2,
    -Q32_1,
    -Q32_2,
    -Q32_3,
    -Q33_1,
    -Q33_2,
    -Q34,
  ) |>
  rename(
    # meta vars
    meta_startdate = StartDate,
    meta_enddate = EndDate,
    meta_status = Status,
    meta_ipaddress = IPAddress,
    meta_progress = Progress,
    meta_duration_s = Duration..in.seconds.,
    meta_finished = Finished,
    meta_recordeddate = RecordedDate,
    meta_responseid = ResponseId,
    meta_recipient_lastname = RecipientLastName,
    meta_recipient_firstname = RecipientFirstName,
    meta_recipient_email = RecipientEmail,
    meta_external_ref = ExternalReference,
    meta_latitude = LocationLatitude,
    meta_longitude = LocationLongitude,
    meta_distchannel = DistributionChannel,
    meta_lang = UserLanguage,
    meta_country_raw = Country,
    meta_psid = PSID,
    meta_pid = PID,
    meta_device = Device,
    # demographics -----------------------------------------------------------------
    q_gender_raw = Q2,
    q_age_raw = Q3_1,
    q_nationality_raw = Q4,
    q_nationality_other_raw = Q4_TEXT,
    q_identity_country_raw = Q5_1,
    q_identity_eu_raw = Q5_2,
    q_identity_europe_raw = Q5_3,
    q_religion_raw = Q6,
    q_religion_other_raw = Q6_TEXT,
    q_class_raw = Q7,
    q_verif_raw = Q8,
    q_verif2_raw = Q8_TEXT,
    # timings ------------------------------------------------------------------
    prime_moreeu_firstclick = Q9_First.Click,
    prime_moreeu_lastclick = Q9_Last.Click,
    prime_moreeu_pagesubmit = Q9_Page.Submit,
    prime_moreeu_clickcount = Q9_Click.Count,
    # outcome variables --------------------------------------------------------
    q_euint_pos_raw = Q20,
    q_eu_efficacy_understand_raw = Q21_1,
    q_eu_efficacy_care_raw = Q21_2,
    q_eu_efficacy_nosay_raw = Q21_3,
    q_pop_will_raw = Q22_1,
    q_pop_people_raw = Q22_2,
    q_pop_citizen_raw = Q22_3,
    q_pop_reps_raw = Q22_4,
    q_pop_goodevil_raw = Q22_5,
    q_pop_compromise_raw = Q22_6,
    q_dem_compromise_raw = Q23_1,
    q_dem_listen_raw = Q23_2,
    q_tech_experts_raw = Q23_3,
    q_tech_leaders_raw = Q23_4,
    q_party_harm_raw = Q23_5,
    q_people_incompetent_raw = Q23_6,
    q_eu_longterm_raw = Q24_1,
    q_eu_responsive_raw = Q24_2,
    q_eu_imp_nat_econ_raw = Q25_1,
    q_eu_imp_nat_cul_raw = Q25_2,
    q_eu_imp_nat_pol_raw = Q25_3,
    q_eu_abolish_raw = Q26_1,
    q_eu_satisfaction_raw = Q26_2,
    # france has a second set, not exclusive :')
    q_euint_pos_fra_raw = Q41,
    q_eu_efficacy_understand_fra_raw = Q35_1,
    q_eu_efficacy_care_fra_raw = Q35_2,
    q_eu_efficacy_nosay_fra_raw = Q35_3,
    q_pop_will_fra_raw = Q36_1,
    q_pop_people_fra_raw = Q36_2,
    q_pop_citizen_fra_raw = Q36_3,
    q_pop_reps_fra_raw = Q36_4,
    q_pop_goodevil_fra_raw = Q36_5,
    q_pop_compromise_fra_raw = Q36_6,
    q_dem_compromise_fra_raw = Q37_1,
    q_dem_listen_fra_raw = Q37_2,
    q_tech_experts_fra_raw = Q37_3,
    q_tech_leaders_fra_raw = Q37_4,
    q_party_harm_fra_raw = Q37_5,
    q_people_incompetent_fra_raw = Q37_6,
    q_eu_longterm_fra_raw = Q38_1,
    q_eu_responsive_fra_raw = Q38_2,
    q_eu_imp_nat_econ_fra_raw = Q39_1,
    q_eu_imp_nat_cul_fra_raw = Q39_2,
    q_eu_imp_nat_pol_fra_raw = Q39_3,
    q_eu_abolish_fra_raw = Q40_1,
    q_eu_satisfaction_fra_raw = Q40_2,
  )

rm(too_far_base)
```

## W2 Block II Overview

Block Vote Choice and Partisanship

Q42 <- q_vote_turnout_likelihood_raw
Q43 <- q_vote_turnout_confirm_raw
Q44 <- q_vote_choice_past_raw
Q44_TEXT <- q_vote_choice_past_other_raw
Q45 <- q_vote_choice_intended_raw
Q45_TEXT <- q_vote_choice_intended_other_raw
Q46 <- q_vote_choice_hypo_raw
Q46_TEXT <- q_vote_choice_hypo_other_raw

Party rankings is a mess across countries:

```{r}
#| label: tbl-party-rankings-q47

wording_map |>
  filter(wave == 2 & str_detect(col_name, "Q47")) |>
  select(country, col_name) |>
  kable()
```

```{r}
#| label: tbl-party-rankings-q48

wording_map |>
  filter(wave == 2 & str_detect(col_name, "Q48")) |>
  select(country, col_name) |>
  kable()
```


Q49_1 <- q_election_challenge_polgroups_raw
Q49_2 <- q_election_impact_eu_raw
Q50 <- q_election_importance_self_raw

Q51 <- q_vote_choice_past2014_raw
Q51_TEXT <- q_vote_choice_past2014_other_raw

Q52 <- q_party_id_raw
Q52_TEXT <- q_party_id_other_raw

## W2 Block II Checks

```{r}
#| label: w2-block2-explore

# mutual exclusivity: at most 1 Q47/Q48 party column non-NA per respondent
df_wave2 |>
  select(starts_with("Q47_"), starts_with("Q48_")) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# flag anomalous respondents
df_wave2 |>
  filter(meta_responseid %in% c("R_2UbCOutJInF4vPr", "R_cMHAHAt4EiWsyqd")) |>
  select(meta_responseid, starts_with("Q47_"), starts_with("Q48_")) |>
  print()
```

```{r}
#| label: w2-block2-coalesce

df_wave2 <- df_wave2 |>
  mutate(
    # fix dual-response anomaly for 2 Danish respondents
    across(
      starts_with("Q47_"),
      ~ if_else(
        meta_responseid %in% c("R_2UbCOutJInF4vPr", "R_cMHAHAt4EiWsyqd"),
        NA_character_,
        .x
      )
    ),
    # coalesce Q47 and Q48 into six country-specific slots
    q_vote_exp_rank_party_1_raw = coalesce(Q47_5, Q48_5),
    q_vote_exp_rank_party_2_raw = case_when(
      meta_country %in%
        c(
          "Bulgaria",
          "Croatia",
          "Czechia",
          "Denmark",
          "Hungary",
          "Lithuania",
          "Netherlands",
          "Poland",
          "United Kingdom"
        ) ~ coalesce(Q47_21, Q48_21),
      meta_country %in%
        c(
          "Belgium",
          "Estonia",
          "Finland",
          "Italy",
          "Slovakia",
          "Slovenia",
          "Spain",
          "Sweden"
        ) ~ coalesce(Q47_26, Q48_26),
      meta_country == "Austria" ~ coalesce(Q47_27, Q48_27),
      meta_country == "France" ~ coalesce(Q47_27, Q48_26),
      meta_country == "Greece" ~ coalesce(Q47_31, Q48_26),
      meta_country == "Germany" ~ coalesce(Q47_32, Q48_32),
      meta_country == "Ireland" ~ coalesce(Q47_6, Q48_6),
      meta_country == "Latvia" ~ coalesce(Q47_30, Q48_26),
      meta_country == "Portugal" ~ coalesce(Q47_30, Q48_39),
      meta_country == "Romania" ~ coalesce(Q47_27, Q48_21),
      TRUE ~ NA_character_
    ),
    q_vote_exp_rank_party_3_raw = case_when(
      meta_country %in%
        c(
          "Bulgaria",
          "Croatia",
          "Czechia",
          "Denmark",
          "Hungary",
          "Lithuania",
          "Netherlands",
          "Poland",
          "United Kingdom"
        ) ~ coalesce(Q47_22, Q48_22),
      meta_country %in%
        c(
          "Belgium",
          "Estonia",
          "Finland",
          "Italy",
          "Slovakia",
          "Slovenia",
          "Spain",
          "Sweden"
        ) ~ coalesce(Q47_27, Q48_27),
      meta_country == "Austria" ~ coalesce(Q47_28, Q48_28),
      meta_country == "France" ~ coalesce(Q47_28, Q48_27),
      meta_country == "Greece" ~ coalesce(Q47_32, Q48_27),
      meta_country == "Germany" ~ coalesce(Q47_33, Q48_33),
      meta_country == "Ireland" ~ coalesce(Q47_7, Q48_7),
      meta_country == "Latvia" ~ coalesce(Q47_31, Q48_27),
      meta_country == "Portugal" ~ coalesce(Q47_31, Q48_40),
      meta_country == "Romania" ~ coalesce(Q47_28, Q48_22),
      TRUE ~ NA_character_
    ),
    q_vote_exp_rank_party_4_raw = case_when(
      meta_country %in%
        c(
          "Bulgaria",
          "Croatia",
          "Czechia",
          "Denmark",
          "Hungary",
          "Lithuania",
          "Netherlands",
          "Poland",
          "United Kingdom"
        ) ~ coalesce(Q47_23, Q48_23),
      meta_country %in%
        c(
          "Belgium",
          "Estonia",
          "Finland",
          "Italy",
          "Slovakia",
          "Slovenia",
          "Spain",
          "Sweden"
        ) ~ coalesce(Q47_28, Q48_28),
      meta_country == "Austria" ~ coalesce(Q47_29, Q48_29),
      meta_country == "France" ~ coalesce(Q47_29, Q48_28),
      meta_country == "Greece" ~ coalesce(Q47_33, Q48_28),
      meta_country == "Germany" ~ coalesce(Q47_34, Q48_34),
      meta_country == "Ireland" ~ coalesce(Q47_8, Q48_8),
      meta_country == "Latvia" ~ coalesce(Q47_32, Q48_28),
      meta_country == "Portugal" ~ coalesce(Q47_32, Q48_41),
      meta_country == "Romania" ~ coalesce(Q47_29, Q48_23),
      TRUE ~ NA_character_
    ),
    q_vote_exp_rank_party_5_raw = case_when(
      meta_country %in%
        c(
          "Bulgaria",
          "Croatia",
          "Czechia",
          "Denmark",
          "Hungary",
          "Lithuania",
          "Netherlands",
          "Poland",
          "United Kingdom"
        ) ~ coalesce(Q47_24, Q48_24),
      meta_country %in%
        c(
          "Belgium",
          "Estonia",
          "Finland",
          "Italy",
          "Slovakia",
          "Slovenia",
          "Spain",
          "Sweden"
        ) ~ coalesce(Q47_29, Q48_29),
      meta_country == "Austria" ~ coalesce(Q47_30, Q48_30),
      meta_country == "France" ~ coalesce(Q47_30, Q48_29),
      meta_country == "Greece" ~ coalesce(Q47_34, Q48_29),
      meta_country == "Germany" ~ coalesce(Q47_35, Q48_35),
      meta_country == "Ireland" ~ coalesce(Q47_9, Q48_9),
      meta_country == "Latvia" ~ coalesce(Q47_33, Q48_29),
      meta_country == "Portugal" ~ coalesce(Q47_33, Q48_42),
      meta_country == "Romania" ~ coalesce(Q47_30, Q48_24),
      TRUE ~ NA_character_
    ),
    q_vote_exp_rank_party_6_raw = case_when(
      meta_country %in%
        c(
          "Bulgaria",
          "Croatia",
          "Czechia",
          "Denmark",
          "Hungary",
          "Lithuania",
          "Netherlands",
          "Poland",
          "United Kingdom"
        ) ~ coalesce(Q47_25, Q48_25),
      meta_country %in%
        c(
          "Belgium",
          "Estonia",
          "Finland",
          "Italy",
          "Slovakia",
          "Slovenia",
          "Spain",
          "Sweden"
        ) ~ coalesce(Q47_30, Q48_30),
      meta_country == "Austria" ~ coalesce(Q47_31, Q48_31),
      meta_country == "France" ~ coalesce(Q47_31, Q48_30),
      meta_country == "Greece" ~ coalesce(Q47_35, Q48_30),
      meta_country == "Germany" ~ coalesce(Q47_36, Q48_36),
      meta_country == "Ireland" ~ coalesce(Q47_10, Q48_10),
      meta_country == "Latvia" ~ coalesce(Q47_34, Q48_30),
      meta_country == "Portugal" ~ coalesce(Q47_34, Q48_43),
      meta_country == "Romania" ~ coalesce(Q47_31, Q48_25),
      TRUE ~ NA_character_
    )
  ) |>
  select(-starts_with("Q48_")) |>
  select(-starts_with("Q47_"))
```

```{r}
#| label: w2-block2-rename

df_wave2 <- df_wave2 |>
  rename(
    q_vote_turnout_likelihood_raw = Q42,
    q_vote_turnout_confirm_raw = Q43,
    q_vote_choice_past_raw = Q44,
    q_vote_choice_past_other_raw = Q44_TEXT,
    q_vote_choice_intended_raw = Q45,
    q_vote_choice_intended_other_raw = Q45_TEXT,
    q_vote_choice_hypo_raw = Q46,
    q_vote_choice_hypo_other_raw = Q46_TEXT,
    q_election_challenge_polgroups_raw = Q49_1,
    q_election_impact_eu_raw = Q49_2,
    q_election_importance_self_raw = Q50,
    q_vote_choice_past2014_raw = Q51,
    q_vote_choice_past2014_other_raw = Q51_TEXT,
    q_party_id_raw = Q52,
    q_party_id_other_raw = Q52_TEXT
  )
```

## W2 Block III Feeling Thermometers

Q196_1 
Q196_12
Q196_13
Q196_14
Q196_15
Q196_16
Q196_17 
Q196_18 
Q196_19
Q196_20
Q196_21
Q196_22
Q196_23
Q196_24
Q196_25
Q196_26

```{r}
#| label: w2-check-thermo

df_wave2 |>
  select(
    starts_with("Q196")
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# max count is 6, so no respondent saw >6 parties, hence questions are naming artefacts
```

```{r}
#| label: w2-coalesce-thermo

df_wave2 <- df_wave2 |>
  mutate(
    q_thermo_1_raw = Q196_1,
    q_thermo_2_raw = case_when(
      meta_country %in%
        c(
          "Austria",
          "Belgium",
          "Croatia",
          "Czechia",
          "Estonia",
          "Finland",
          "France",
          "Greece",
          "Italy",
          "Latvia",
          "Slovakia",
          "Slovenia",
          "Spain",
          "Sweden"
        ) ~ Q196_17,
      meta_country %in%
        c(
          "Bulgaria",
          "Denmark",
          "Hungary",
          "Lithuania",
          "Netherlands",
          "Poland",
          "UK"
        ) ~ Q196_12,
      meta_country == "Germany" ~ Q196_22,
      meta_country == "Ireland" ~ Q196_7,
      meta_country == "Portugal" ~ Q196_27,
      meta_country == "Romania" ~ Q196_18,
      TRUE ~ NA_character_
    ),
    q_thermo_3_raw = case_when(
      meta_country %in%
        c(
          "Austria",
          "Belgium",
          "Croatia",
          "Czechia",
          "Estonia",
          "Finland",
          "France",
          "Greece",
          "Italy",
          "Latvia",
          "Slovakia",
          "Slovenia",
          "Spain",
          "Sweden"
        ) ~ Q196_18,
      meta_country %in%
        c(
          "Bulgaria",
          "Denmark",
          "Hungary",
          "Lithuania",
          "Netherlands",
          "Poland",
          "UK"
        ) ~ Q196_13,
      meta_country == "Germany" ~ Q196_23,
      meta_country == "Ireland" ~ Q196_8,
      meta_country == "Portugal" ~ Q196_28,
      meta_country == "Romania" ~ Q196_19,
      TRUE ~ NA_character_
    ),
    q_thermo_4_raw = case_when(
      meta_country %in%
        c(
          "Austria",
          "Belgium",
          "Croatia",
          "Czechia",
          "Estonia",
          "Finland",
          "France",
          "Greece",
          "Italy",
          "Latvia",
          "Slovakia",
          "Slovenia",
          "Spain",
          "Sweden"
        ) ~ Q196_19,
      meta_country %in%
        c(
          "Bulgaria",
          "Denmark",
          "Hungary",
          "Lithuania",
          "Netherlands",
          "Poland",
          "UK"
        ) ~ Q196_14,
      meta_country == "Germany" ~ Q196_24,
      meta_country == "Ireland" ~ Q196_9,
      meta_country == "Portugal" ~ Q196_29,
      meta_country == "Romania" ~ Q196_20,
      TRUE ~ NA_character_
    ),
    q_thermo_5_raw = case_when(
      meta_country %in%
        c(
          "Austria",
          "Belgium",
          "Croatia",
          "Czechia",
          "Estonia",
          "Finland",
          "France",
          "Greece",
          "Italy",
          "Latvia",
          "Slovakia",
          "Slovenia",
          "Spain",
          "Sweden"
        ) ~ Q196_20,
      meta_country %in%
        c(
          "Bulgaria",
          "Denmark",
          "Hungary",
          "Lithuania",
          "Netherlands",
          "Poland",
          "UK"
        ) ~ Q196_15,
      meta_country == "Germany" ~ Q196_25,
      meta_country == "Ireland" ~ Q196_10,
      meta_country == "Portugal" ~ Q196_30,
      meta_country == "Romania" ~ Q196_21,
      TRUE ~ NA_character_
    ),
    q_thermo_6_raw = case_when(
      meta_country %in%
        c(
          "Austria",
          "Belgium",
          "Croatia",
          "Czechia",
          "Estonia",
          "Finland",
          "France",
          "Greece",
          "Italy",
          "Latvia",
          "Slovakia",
          "Slovenia",
          "Spain",
          "Sweden"
        ) ~ Q196_21,
      meta_country %in%
        c(
          "Bulgaria",
          "Denmark",
          "Hungary",
          "Lithuania",
          "Netherlands",
          "Poland",
          "UK"
        ) ~ Q196_16,
      meta_country == "Germany" ~ Q196_26,
      meta_country == "Ireland" ~ Q196_11,
      meta_country == "Portugal" ~ Q196_31,
      meta_country == "Romania" ~ Q196_22,
      TRUE ~ NA_character_
    )
  ) |>
  select(-starts_with("Q196"))
```


## W2 Pol Participation, Campaign activity & Verification 2

Q197_1 <- q_news_tv_raw
Q197_2 <- q_news_newspaper_raw
Q197_3 <- q_news_radio_raw
Q197_4 <- q_news_social_raw
Q197_5 <- q_news_internet_raw
Q197_6 <- q_news_personal_raw
Q197_7 <- q_news_other_raw
Q197_TEXT <- q_news_other_text_raw

Q198 <- q_eu_campaign_sources_raw
Q198_TEXT <- q_eu_campaign_sources_other_raw

```{r}
#| label: w2-polpart-rename

df_wave2 <- df_wave2 |>
  rename(
    q_news_tv_raw = Q197_1,
    q_news_newspaper_raw = Q197_2,
    q_news_radio_raw = Q197_3,
    q_news_social_raw = Q197_4,
    q_news_internet_raw = Q197_5,
    q_news_personal_raw = Q197_6,
    q_news_other_raw = Q197_7,
    q_news_other_text_raw = Q197_TEXT,
    q_eu_campaign_sources_raw = Q198,
    q_eu_campaign_sources_other_raw = Q198_TEXT,
    q_eu_campaign_sources_fra_raw = Q199,
    q_eu_campaign_sources_other_fra_raw = Q199_TEXT
  )
```

## W2 CJEU Block (CJEU experiment control condition)

Q213* <- Timing vars (4)
Q214 <- q_cjeu_pos_raw
q215_1 <- q_cjeu_abolish_raw
q215_2 <- q_cjeu_satisfaction_raw

```{r}
#| label: w1-cjeu-rename

df_wave2 <- df_wave2 |>
  mutate(
    prime_cjeu_condition = case_when(
      !is.na(Q213_First.Click) ~ "control_text"
    ),
    prime_cjeu_text = case_match(
      prime_cjeu_condition,
      "control-text" ~ "In thinking about the Court of Justice of the European Union's (CJEU) decisions more generally, some people argue that it tends to favor actions taken by the European Commission at the expense of parties or groups that are opposed to the European Commission. Others contend that the CJEU tends to protect parties or groups that are opposed to the European Commission even if it means striking down actions taken by the European Commission."
    )
  ) |>
  rename(
    prime_cjeu_firstclick = Q213_First.Click,
    prime_cjeu_lastclick = Q213_Last.Click,
    prime_cjeu_pagesubmit = Q213_Page.Submit,
    prime_cjeu_clickcount = Q213_Click.Count,
    q_cjeu_pos_raw = Q214,
    q_cjeu_abolish_raw = Q215_1,
    q_cjeu_satisfaction_raw = Q215_2
  )
```

## W2 Pol knowledge, interest etc block

Q216_1 <- q_eval_econ_eur_raw
Q216_2 <- q_eval_econ_nat_raw
Q216_3 <- q_eval_fin_household_raw
Q216_4 <- q_eval_job_raw

Q217_1 <- q_satis_demo_nat_raw
Q217_2 <- q_satis_demo_eu_raw

Q222_1 <- q_nat_int_raw 
Q222_2 <- q_eu_int_raw
Q223_1 <- q_nativ_econ_raw 
Q223_2 <- q_nativ_cult_raw

Q224_1 <- q_eu_know_1_raw
Q224_2 <- q_eu_know_2_raw
Q224_3 <- q_eu_know_3_raw
Q224_4 <- q_eu_know_4_raw
Q224_5 <- q_eu_know_5_raw

Q225_1 <- q_eu_informed_com_raw
Q225_2 <- q_eu_informed_cou_raw 
Q225_3 <- q_eu_informed_ep_raw 
Q225_4 <- q_eu_informed_cjeu_raw 

Q226_1 <- q_eu_trust_com_raw
Q226_2 <- q_eu_trust_cou_raw 
Q226_3 <- q_eu_trust_ep_raw 
Q226_4 <- q_eu_trust_cjeu_raw

Q227 <- q_risk_taking
Q228 <- q_future_discount

```{r}
#| label: w2-next-block-renaming

df_wave2 <- df_wave2 |>
  rename(
    q_eval_econ_eur_raw = Q216_1,
    q_eval_econ_nat_raw = Q216_2,
    q_eval_fin_household_raw = Q216_3,
    q_eval_job_raw = Q216_4,
    q_satis_demo_nat_raw = Q217_1,
    q_satis_demo_eu_raw = Q217_2,
    q_nat_int_raw = Q222_1,
    q_eu_int_raw = Q222_2,
    q_nativ_econ_raw = Q223_1,
    q_nativ_cult_raw = Q223_2,
    q_eu_know_1_raw = Q224_1,
    q_eu_know_2_raw = Q224_2,
    q_eu_know_3_raw = Q224_3,
    q_eu_know_4_raw = Q224_4,
    q_eu_know_5_raw = Q224_5,
    q_eu_informed_com_raw = Q225_1,
    q_eu_informed_cou_raw = Q225_2,
    q_eu_informed_ep_raw = Q225_3,
    q_eu_informed_cjeu_raw = Q225_4,
    q_eu_trust_com_raw = Q226_1,
    q_eu_trust_cou_raw = Q226_2,
    q_eu_trust_ep_raw = Q226_3,
    q_eu_trust_cjeu_raw = Q226_4,
    q_risk_taking = Q227,
    q_future_discount = Q228
  )
```

## W2 LR/EU placements and efficacy block

```{r}
#| label: w2-placements-coalesce

df_wave2 <- df_wave2 |>
  mutate(
    # occupation in Finland Slovenia and with different Q-number ---------------
    Q247 = coalesce(Q247, Q267, Q365),
    Q248 = coalesce(Q248, Q268, Q367),
  ) |>
  select(
    -Q267,
    -Q268,
    -Q365,
    -Q367
  )
```

```{r}
#| label: w2-placements-renaming

df_wave2 <- df_wave2 |>
  rename(
    # self placement ---------------------------------------------------------------
    q_lr_self_raw = Q236,
    # party placements ---------------------------------------------------------
    q_lr_party_1_raw = Q237_1,
    q_lr_party_2_raw = Q237_2,
    q_lr_party_3_raw = Q237_3,
    q_lr_party_4_raw = Q237_4,
    q_lr_party_5_raw = Q237_5,
    q_lr_party_6_raw = Q237_6,
    q_lr_party_7_raw = Q237_7,
    q_lr_party_8_raw = Q237_8,
    q_lr_party_9_raw = Q237_9,
    q_lr_party_10_raw = Q237_10,
    q_lr_party_11_raw = Q237_11,
    q_lr_party_12_raw = Q237_12,
    # eu institutions placements -----------------------------------------------
    q_lr_com_raw = Q238_1,
    q_lr_cou_raw = Q238_2,
    q_lr_ep_raw = Q238_3,
    q_lr_cjeu_raw = Q238_4,
    # efficacy -----------------------------------------------------------------
    q_eu_efficacy_understand_c_raw = Q239_1,
    q_eu_efficacy_care_c_raw = Q239_2,
    q_eff_external_nosay_c_raw = Q239_3,
    # eu self placement --------------------------------------------------------
    q_euint_self_raw = Q240,
    # eu party placements ----------------------------------------------------------
    q_euint_party_1_raw = Q241_1,
    q_euint_party_2_raw = Q241_2,
    q_euint_party_3_raw = Q241_3,
    q_euint_party_4_raw = Q241_4,
    q_euint_party_5_raw = Q241_5,
    q_euint_party_6_raw = Q241_6,
    q_euint_party_7_raw = Q241_7,
    q_euint_party_8_raw = Q241_8,
    # eu bodies placement ------------------------------------------------------
    q_euint_com_raw = Q242_1,
    q_euint_cou_raw = Q242_2,
    q_euint_ep_raw = Q242_3,
    q_euint_cjeu_raw = Q242_4,
    # age at edu stop ----------------------------------------------------------
    q_edu_age_stop_raw = Q243_1,
    q_rural_urban_raw = Q244,
    q_postal_code_raw = Q245,
    q_region = Q246,
    q_occ_current_raw = Q247,
    q_occ_last_raw = Q248,

    # french duplicates
    q_vote_turnout_reason_fra_raw = Q53,
    q_vote_choice_past_fra_raw = Q54,
    q_vote_choice_past_other_fra_raw = Q54_TEXT,
    q_vote_choice_hypo_fra_raw = Q55,
    q_vote_choice_hypo_other_fra_raw = Q55_TEXT,
    q_vote_choice_ep2014_fra_raw = Q56,
    q_vote_choice_ep2014_other_fra_raw = Q56_TEXT,
    q_party_id_fra_raw = Q57,
    q_party_id_other_fra_raw = Q57_TEXT,

    # french unique questions
    q_campaign_activity_fra_raw = Q200,
    q_campaign_activity_other_fra_raw = Q200_TEXT
  )
```

POINT OF STOP: Q201 -- wtf why did french respondents get more priming? eventually drop if it can't be reconstructed

My guess: France survey in some cases showed the "full" CJEU priming experiments, as Q numbers correspond to those in W3 Irish questionaire.

Hence check if these are mutually exclusive with the overall prime control condition (I don't even know which was supposed to be right and which was wrong)

```{r}
#| label: w2-french-prime-mess

df_wave2 |>
  select(
    prime_cjeu_firstclick,
    Q201_First.Click
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)
# 201 respondents saw both

# here it seems to be correctly branched
df_wave2 |>
  select(
    Q201_First.Click,
    Q204_First.Click,
    Q207_First.Click,
    Q210_First.Click
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q201_Last.Click,
    Q204_Last.Click,
    Q207_Last.Click,
    Q210_Last.Click
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q201_Page.Submit,
    Q204_Page.Submit,
    Q207_Page.Submit,
    Q210_Page.Submit
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q201_Click.Count,
    Q204_Click.Count,
    Q207_Click.Count,
    Q210_Click.Count
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q203_1,
    Q206_1,
    Q209_1,
    Q211_1
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q203_2,
    Q206_2,
    Q209_2,
    Q211_2
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave2 |>
  select(
    Q208,
    Q212
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# did french respondents of all CJEU prime branches see the earlier control condition?
df_wave2 |>
  select(
    prime_cjeu_clickcount,
    Q207_Click.Count
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)
# yup, 206 did

```

Overview:

CJEU Priming Condition: Majority
Q201_*: Timings
Q202: Text: "A recent analysis of the Court of Justice of the European Union's (CJEU) decisions finds that the institution strongly favors actions taken by the European Commission at the expense of parties or groups that are opposed to the European Commission. Specifically, this study finds that the CJEU regularly upholds legislation passed by the European Commission."
Q203_1: q_cjeu_abolish_fra_raw
Q203_2: q_cjeu_satisfaction_fra_raw

CJEU Priming Condition: Minority
Q204_*: Timings
Q205: "A recent analysis of the Court of Justice of the European Union's (CJEU) decisions finds that the institution strongly tends to protect parties or groups that are opposed to the European Commission at the expense of actions taken by the European Commission. Specifically, this study finds that the CJEU regularly strikes down legislation passed by the Commission to protect parties or groups that are opposed to the European Commission."
Q206_1: q_cjeu_abolish_fra_raw
Q206_2: q_cjeu_satisfaction_fra_raw

CJEU Priming Condition: Control-Text
Q207_*: Timings
Q208: q_cjeu_pos_fra_raw
Q209_1: q_cjeu_abolish_fra_raw
Q209_2: q_cjeu_satisfaction_fra_raw
Text: In thinking about the Court of Justice of the European Union's (CJEU) decisions more generally, some people argue that it tends to favor actions taken by the European Commission at the expense of parties or groups that are opposed to the European Commission. Others contend that the CJEU tends to protect parties or groups that are opposed to the European Commission even if it means striking down actions taken by the European Commission.

CJEU Priming Condition: Control-NoText
Q210_*: Timings
Q211_1: q_cjeu_abolish_fra_raw
Q211_2: q_cjeu_satisfaction_fra_raw
Q212: q_cjeu_pos_fra_raw
Text: In thinking about the Court of Justice of the European Union's (CJEU) decisions more generally, some people argue that it tends to favor actions taken by the European Commission at the expense of parties or groups that are opposed to the European Commission. Others contend that the CJEU tends to protect parties or groups that are opposed to the European Commission even if it means striking down actions taken by the European Commission.

and prime_cjeu_fra_condition and prime_cjeu_fra_text

```{r}
#| label: w2-french-cjeu-coalesce-rename

df_wave2 <- df_wave2 |>
  mutate(
    # condition label
    prime_cjeu_fra_condition = case_when(
      !is.na(Q201_First.Click) ~ "majority",
      !is.na(Q204_First.Click) ~ "minority",
      !is.na(Q207_First.Click) ~ "control_text",
      !is.na(Q210_First.Click) ~ "control_notext"
    ),
    # condition text
    prime_cjeu_fra_text = case_match(
      prime_cjeu_fra_condition,
      "majority" ~ "A recent analysis of the Court of Justice of the European Union's (CJEU) decisions finds that the institution strongly favors actions taken by the European Commission at the expense of parties or groups that are opposed to the European Commission. Specifically, this study finds that the CJEU regularly upholds legislation passed by the European Commission.",
      "minority" ~ "A recent analysis of the Court of Justice of the European Union's (CJEU) decisions finds that the institution strongly tends to protect parties or groups that are opposed to the European Commission at the expense of actions taken by the European Commission. Specifically, this study finds that the CJEU regularly strikes down legislation passed by the Commission to protect parties or groups that are opposed to the European Commission.",
      c(
        "control_text",
        "control_notext"
      ) ~ "In thinking about the Court of Justice of the European Union's (CJEU) decisions more generally, some people argue that it tends to favor actions taken by the European Commission at the expense of parties or groups that are opposed to the European Commission. Others contend that the CJEU tends to protect parties or groups that are opposed to the European Commission even if it means striking down actions taken by the European Commission."
    ),
    # coalesce timings
    Q201_First.Click = coalesce(
      Q201_First.Click,
      Q204_First.Click,
      Q207_First.Click,
      Q210_First.Click
    ),
    Q201_Last.Click = coalesce(
      Q201_Last.Click,
      Q204_Last.Click,
      Q207_Last.Click,
      Q210_Last.Click
    ),
    Q201_Page.Submit = coalesce(
      Q201_Page.Submit,
      Q204_Page.Submit,
      Q207_Page.Submit,
      Q210_Page.Submit
    ),
    Q201_Click.Count = coalesce(
      Q201_Click.Count,
      Q204_Click.Count,
      Q207_Click.Count,
      Q210_Click.Count
    ),
    # coalesce outcomes
    Q203_1 = coalesce(Q203_1, Q206_1, Q209_1, Q211_1),
    Q203_2 = coalesce(Q203_2, Q206_2, Q209_2, Q211_2),
    Q208 = coalesce(Q208, Q212)
  ) |>
  select(
    -Q204_First.Click,
    -Q204_Last.Click,
    -Q204_Page.Submit,
    -Q204_Click.Count,
    -Q207_First.Click,
    -Q207_Last.Click,
    -Q207_Page.Submit,
    -Q207_Click.Count,
    -Q210_First.Click,
    -Q210_Last.Click,
    -Q210_Page.Submit,
    -Q210_Click.Count,
    -Q206_1,
    -Q206_2,
    -Q209_1,
    -Q209_2,
    -Q211_1,
    -Q211_2,
    -Q212
  ) |>
  rename(
    prime_cjeu_fra_firstclick = Q201_First.Click,
    prime_cjeu_fra_lastclick = Q201_Last.Click,
    prime_cjeu_fra_pagesubmit = Q201_Page.Submit,
    prime_cjeu_fra_clickcount = Q201_Click.Count,
    q_cjeu_pos_fra_raw = Q208,
    q_cjeu_abolish_fra_raw = Q203_1,
    q_cjeu_satisfaction_fra_raw = Q203_2
  )
```


## Rename remaining french extra items

```{r}
#| label: w2-rename-remainders

df_wave2 <- df_wave2 |>
  rename(
    # french duplicates of existing items ------------------------------------
    q_eval_econ_eur_fra_raw = Q219_1,
    q_eval_econ_nat_fra_raw = Q219_2,
    q_eval_fin_household_fra_raw = Q219_3,
    q_eval_job_fra_raw = Q219_4,
    q_nativ_econ_fra_raw = Q220_1,
    q_nativ_cult_fra_raw = Q220_2,
    q_nativ_3_fra_raw = Q220_3,
    q_nativ_4_fra_raw = Q220_4,
    q_satis_demo_nat_fra_raw = Q221_1,
    q_satis_demo_eu_fra_raw = Q221_2,
    q_nat_int_fra_raw = Q229_1,
    q_eu_int_fra_raw = Q229_2,
    q_nativ_econ_b_fra_raw = Q230_1,
    q_nativ_cult_b_fra_raw = Q230_2,
    q_eu_know_1_fra_raw = Q231_1,
    q_eu_know_2_fra_raw = Q231_2,
    q_eu_know_3_fra_raw = Q231_3,
    q_eu_know_4_fra_raw = Q231_4,
    q_eu_know_5_fra_raw = Q231_5,
    q_eu_informed_com_fra_raw = Q232_1,
    q_eu_informed_cou_fra_raw = Q232_2,
    q_eu_informed_ep_fra_raw = Q232_3,
    q_eu_informed_cjeu_fra_raw = Q232_4,
    q_eu_trust_com_fra_raw = Q233_1,
    q_eu_trust_cou_fra_raw = Q233_2,
    q_eu_trust_ep_fra_raw = Q233_3,
    q_eu_trust_cjeu_fra_raw = Q233_4,
    q_risk_taking_fra_raw = Q234,
    q_future_discount_fra_raw = Q235,
    # french-only political norms battery ------------------------------------
    q_norm_tolerance_fra_raw = Q218_1,
    q_norm_order_fra_raw = Q218_2,
    q_norm_unjust_law_fra_raw = Q218_3,
    q_norm_unvoted_gov_fra_raw = Q218_4,
    q_norm_bypass_law_fra_raw = Q218_5,
    q_norm_gov_bypass_fra_raw = Q218_6,
  )

```

# Condensed W2 Question Wordings

```{r}
#| label: w2-question-wordings

rename_vec_w2 <- c(
  # meta
  meta_startdate = "StartDate",
  meta_enddate = "EndDate",
  meta_status = "Status",
  meta_ipaddress = "IPAddress",
  meta_progress = "Progress",
  meta_duration_s = "Duration..in.seconds.",
  meta_finished = "Finished",
  meta_recordeddate = "RecordedDate",
  meta_responseid = "ResponseId",
  meta_recipient_lastname = "RecipientLastName",
  meta_recipient_firstname = "RecipientFirstName",
  meta_recipient_email = "RecipientEmail",
  meta_external_ref = "ExternalReference",
  meta_latitude = "LocationLatitude",
  meta_longitude = "LocationLongitude",
  meta_distchannel = "DistributionChannel",
  meta_lang = "UserLanguage",
  meta_country_raw = "Country",
  meta_psid = "PSID",
  meta_pid = "PID",
  meta_device = "Device",
  # demographics
  q_gender_raw = "Q2",
  q_age_raw = "Q3_1",
  q_nationality_raw = "Q4",
  q_nationality_other_raw = "Q4_TEXT",
  q_identity_country_raw = "Q5_1",
  q_identity_eu_raw = "Q5_2",
  q_identity_europe_raw = "Q5_3",
  q_religion_raw = "Q6",
  q_religion_other_raw = "Q6_TEXT",
  q_class_raw = "Q7",
  q_verif_raw = "Q8",
  q_verif2_raw = "Q8_TEXT",
  # priming exp 1 timings
  prime_moreeu_firstclick = "Q9_First.Click",
  prime_moreeu_lastclick = "Q9_Last.Click",
  prime_moreeu_pagesubmit = "Q9_Page.Submit",
  prime_moreeu_clickcount = "Q9_Click.Count",
  # derived condition/text
  prime_moreeu_condition = "prime_moreeu_condition",
  prime_moreeu_text = "prime_moreeu_text",
  # outcome variables
  q_euint_pos_raw = "Q20",
  q_eu_efficacy_understand_raw = "Q21_1",
  q_eu_efficacy_care_raw = "Q21_2",
  q_eu_efficacy_nosay_raw = "Q21_3",
  q_pop_will_raw = "Q22_1",
  q_pop_people_raw = "Q22_2",
  q_pop_citizen_raw = "Q22_3",
  q_pop_reps_raw = "Q22_4",
  q_pop_goodevil_raw = "Q22_5",
  q_pop_compromise_raw = "Q22_6",
  q_dem_compromise_raw = "Q23_1",
  q_dem_listen_raw = "Q23_2",
  q_tech_experts_raw = "Q23_3",
  q_tech_leaders_raw = "Q23_4",
  q_party_harm_raw = "Q23_5",
  q_people_incompetent_raw = "Q23_6",
  q_eu_longterm_raw = "Q24_1",
  q_eu_responsive_raw = "Q24_2",
  q_eu_imp_nat_econ_raw = "Q25_1",
  q_eu_imp_nat_cul_raw = "Q25_2",
  q_eu_imp_nat_pol_raw = "Q25_3",
  q_eu_abolish_raw = "Q26_1",
  q_eu_satisfaction_raw = "Q26_2",
  # French duplicate outcomes
  q_euint_pos_fra_raw = "Q41",
  q_eu_efficacy_understand_fra_raw = "Q35_1",
  q_eu_efficacy_care_fra_raw = "Q35_2",
  q_eu_efficacy_nosay_fra_raw = "Q35_3",
  q_pop_will_fra_raw = "Q36_1",
  q_pop_people_fra_raw = "Q36_2",
  q_pop_citizen_fra_raw = "Q36_3",
  q_pop_reps_fra_raw = "Q36_4",
  q_pop_goodevil_fra_raw = "Q36_5",
  q_pop_compromise_fra_raw = "Q36_6",
  q_dem_compromise_fra_raw = "Q37_1",
  q_dem_listen_fra_raw = "Q37_2",
  q_tech_experts_fra_raw = "Q37_3",
  q_tech_leaders_fra_raw = "Q37_4",
  q_party_harm_fra_raw = "Q37_5",
  q_people_incompetent_fra_raw = "Q37_6",
  q_eu_longterm_fra_raw = "Q38_1",
  q_eu_responsive_fra_raw = "Q38_2",
  q_eu_imp_nat_econ_fra_raw = "Q39_1",
  q_eu_imp_nat_cul_fra_raw = "Q39_2",
  q_eu_imp_nat_pol_fra_raw = "Q39_3",
  q_eu_abolish_fra_raw = "Q40_1",
  q_eu_satisfaction_fra_raw = "Q40_2",
  # vote choice
  q_vote_turnout_likelihood_raw = "Q42",
  q_vote_turnout_confirm_raw = "Q43",
  q_vote_choice_past_raw = "Q44",
  q_vote_choice_past_other_raw = "Q44_TEXT",
  q_vote_choice_intended_raw = "Q45",
  q_vote_choice_intended_other_raw = "Q45_TEXT",
  q_vote_choice_hypo_raw = "Q46",
  q_vote_choice_hypo_other_raw = "Q46_TEXT",
  q_election_challenge_polgroups_raw = "Q49_1",
  q_election_impact_eu_raw = "Q49_2",
  q_election_importance_self_raw = "Q50",
  q_vote_choice_past2014_raw = "Q51",
  q_vote_choice_past2014_other_raw = "Q51_TEXT",
  q_party_id_raw = "Q52",
  q_party_id_other_raw = "Q52_TEXT",
  # party rankings (derived)
  q_vote_exp_rank_party_1_raw = "q_vote_exp_rank_party_1_raw",
  q_vote_exp_rank_party_2_raw = "q_vote_exp_rank_party_2_raw",
  q_vote_exp_rank_party_3_raw = "q_vote_exp_rank_party_3_raw",
  q_vote_exp_rank_party_4_raw = "q_vote_exp_rank_party_4_raw",
  q_vote_exp_rank_party_5_raw = "q_vote_exp_rank_party_5_raw",
  q_vote_exp_rank_party_6_raw = "q_vote_exp_rank_party_6_raw",
  # feeling thermometers (derived)
  q_thermo_1_raw = "q_thermo_1_raw",
  q_thermo_2_raw = "q_thermo_2_raw",
  q_thermo_3_raw = "q_thermo_3_raw",
  q_thermo_4_raw = "q_thermo_4_raw",
  q_thermo_5_raw = "q_thermo_5_raw",
  q_thermo_6_raw = "q_thermo_6_raw",
  # media sources
  q_news_tv_raw = "Q197_1",
  q_news_newspaper_raw = "Q197_2",
  q_news_radio_raw = "Q197_3",
  q_news_social_raw = "Q197_4",
  q_news_internet_raw = "Q197_5",
  q_news_personal_raw = "Q197_6",
  q_news_other_raw = "Q197_7",
  q_news_other_text_raw = "Q197_TEXT",
  q_eu_campaign_sources_raw = "Q198",
  q_eu_campaign_sources_other_raw = "Q198_TEXT",
  # CJEU block
  prime_cjeu_condition = "prime_cjeu_condition",
  prime_cjeu_text = "prime_cjeu_text",
  prime_cjeu_firstclick = "Q213_First.Click",
  prime_cjeu_lastclick = "Q213_Last.Click",
  prime_cjeu_pagesubmit = "Q213_Page.Submit",
  prime_cjeu_clickcount = "Q213_Click.Count",
  q_cjeu_pos_raw = "Q214",
  q_cjeu_abolish_raw = "Q215_1",
  q_cjeu_satisfaction_raw = "Q215_2",
  # pol knowledge
  q_eval_econ_eur_raw = "Q216_1",
  q_eval_econ_nat_raw = "Q216_2",
  q_eval_fin_household_raw = "Q216_3",
  q_eval_job_raw = "Q216_4",
  q_satis_demo_nat_raw = "Q217_1",
  q_satis_demo_eu_raw = "Q217_2",
  q_nat_int_raw = "Q222_1",
  q_eu_int_raw = "Q222_2",
  q_nativ_econ_raw = "Q223_1",
  q_nativ_cult_raw = "Q223_2",
  q_eu_know_1_raw = "Q224_1",
  q_eu_know_2_raw = "Q224_2",
  q_eu_know_3_raw = "Q224_3",
  q_eu_know_4_raw = "Q224_4",
  q_eu_know_5_raw = "Q224_5",
  q_eu_informed_com_raw = "Q225_1",
  q_eu_informed_cou_raw = "Q225_2",
  q_eu_informed_ep_raw = "Q225_3",
  q_eu_informed_cjeu_raw = "Q225_4",
  q_eu_trust_com_raw = "Q226_1",
  q_eu_trust_cou_raw = "Q226_2",
  q_eu_trust_ep_raw = "Q226_3",
  q_eu_trust_cjeu_raw = "Q226_4",
  q_risk_taking = "Q227",
  q_future_discount = "Q228",
  # placements
  q_lr_self_raw = "Q236",
  q_lr_party_1_raw = "Q237_1",
  q_lr_party_2_raw = "Q237_2",
  q_lr_party_3_raw = "Q237_3",
  q_lr_party_4_raw = "Q237_4",
  q_lr_party_5_raw = "Q237_5",
  q_lr_party_6_raw = "Q237_6",
  q_lr_party_7_raw = "Q237_7",
  q_lr_party_8_raw = "Q237_8",
  q_lr_party_9_raw = "Q237_9",
  q_lr_party_10_raw = "Q237_10",
  q_lr_party_11_raw = "Q237_11",
  q_lr_party_12_raw = "Q237_12",
  q_lr_com_raw = "Q238_1",
  q_lr_cou_raw = "Q238_2",
  q_lr_ep_raw = "Q238_3",
  q_lr_cjeu_raw = "Q238_4",
  q_eu_efficacy_understand_c_raw = "Q239_1",
  q_eu_efficacy_care_c_raw = "Q239_2",
  q_eff_external_nosay_c_raw = "Q239_3",
  q_euint_self_raw = "Q240",
  q_euint_party_1_raw = "Q241_1",
  q_euint_party_2_raw = "Q241_2",
  q_euint_party_3_raw = "Q241_3",
  q_euint_party_4_raw = "Q241_4",
  q_euint_party_5_raw = "Q241_5",
  q_euint_party_6_raw = "Q241_6",
  q_euint_party_7_raw = "Q241_7",
  q_euint_party_8_raw = "Q241_8",
  q_euint_com_raw = "Q242_1",
  q_euint_cou_raw = "Q242_2",
  q_euint_ep_raw = "Q242_3",
  q_euint_cjeu_raw = "Q242_4",
  q_edu_age_stop_raw = "Q243_1",
  q_rural_urban_raw = "Q244",
  q_postal_code_raw = "Q245",
  q_region = "Q246",
  q_occ_current_raw = "Q247",
  q_occ_last_raw = "Q248",
  # French-specific items
  q_vote_turnout_reason_fra_raw = "Q53",
  q_vote_choice_past_fra_raw = "Q54",
  q_vote_choice_past_other_fra_raw = "Q54_TEXT",
  q_vote_choice_hypo_fra_raw = "Q55",
  q_vote_choice_hypo_other_fra_raw = "Q55_TEXT",
  q_vote_choice_ep2014_fra_raw = "Q56",
  q_vote_choice_ep2014_other_fra_raw = "Q56_TEXT",
  q_party_id_fra_raw = "Q57",
  q_party_id_other_fra_raw = "Q57_TEXT",
  q_campaign_activity_fra_raw = "Q200",
  q_campaign_activity_other_fra_raw = "Q200_TEXT",
  q_eu_campaign_sources_fra_raw = "Q199",
  q_eu_campaign_sources_other_fra_raw = "Q199_TEXT",
  prime_cjeu_fra_condition = "prime_cjeu_fra_condition",
  prime_cjeu_fra_text = "prime_cjeu_fra_text",
  prime_cjeu_fra_firstclick = "Q201_First.Click",
  prime_cjeu_fra_lastclick = "Q201_Last.Click",
  prime_cjeu_fra_pagesubmit = "Q201_Page.Submit",
  prime_cjeu_fra_clickcount = "Q201_Click.Count",
  q_cjeu_pos_fra_raw = "Q208",
  q_cjeu_abolish_fra_raw = "Q203_1",
  q_cjeu_satisfaction_fra_raw = "Q203_2",
  q_eval_econ_eur_fra_raw = "Q219_1",
  q_eval_econ_nat_fra_raw = "Q219_2",
  q_eval_fin_household_fra_raw = "Q219_3",
  q_eval_job_fra_raw = "Q219_4",
  q_nativ_econ_fra_raw = "Q220_1",
  q_nativ_cult_fra_raw = "Q220_2",
  q_nativ_3_fra_raw = "Q220_3",
  q_nativ_4_fra_raw = "Q220_4",
  q_satis_demo_nat_fra_raw = "Q221_1",
  q_satis_demo_eu_fra_raw = "Q221_2",
  q_nat_int_fra_raw = "Q229_1",
  q_eu_int_fra_raw = "Q229_2",
  q_nativ_econ_b_fra_raw = "Q230_1",
  q_nativ_cult_b_fra_raw = "Q230_2",
  q_eu_know_1_fra_raw = "Q231_1",
  q_eu_know_2_fra_raw = "Q231_2",
  q_eu_know_3_fra_raw = "Q231_3",
  q_eu_know_4_fra_raw = "Q231_4",
  q_eu_know_5_fra_raw = "Q231_5",
  q_eu_informed_com_fra_raw = "Q232_1",
  q_eu_informed_cou_fra_raw = "Q232_2",
  q_eu_informed_ep_fra_raw = "Q232_3",
  q_eu_informed_cjeu_fra_raw = "Q232_4",
  q_eu_trust_com_fra_raw = "Q233_1",
  q_eu_trust_cou_fra_raw = "Q233_2",
  q_eu_trust_ep_fra_raw = "Q233_3",
  q_eu_trust_cjeu_fra_raw = "Q233_4",
  q_risk_taking_fra_raw = "Q234",
  q_future_discount_fra_raw = "Q235",
  # French-only norms battery
  q_norm_tolerance_fra_raw = "Q218_1",
  q_norm_order_fra_raw = "Q218_2",
  q_norm_unjust_law_fra_raw = "Q218_3",
  q_norm_unvoted_gov_fra_raw = "Q218_4",
  q_norm_bypass_law_fra_raw = "Q218_5",
  q_norm_gov_bypass_fra_raw = "Q218_6"
)

wording_map_w2 <- wording_map |>
  filter(wave == 2, col_name %in% rename_vec_w2) |>
  left_join(
    tibble(col_name = rename_vec_w2, new_name = names(rename_vec_w2)),
    by = "col_name"
  ) |>
  select(col_name, new_name, country, wording)
```

```{r}
#| label: tbl-w2-wording-unmatched
#| tbl-cap: "W2 variables with no wording match"

cat("Distinct new_name values:", length(unique(names(rename_vec_w2))), "\n")
cat("Matched rows in wording_map_w2:", nrow(wording_map_w2), "\n")

tibble(new_name = names(rename_vec_w2), col_name = rename_vec_w2) |>
  anti_join(wording_map_w2, by = "new_name") |>
  distinct(new_name, col_name) |>
  kable()
```

# Save Cleaned W2 Dataset

```{r}
#| label: save-cleaned-w1

write_rds(
  df_wave2,
  file = here(
    "data",
    "02_processed",
    "wave2_clean.rds"
  )
)

write_rds(
  wording_map_w2,
  file = here(
    "data",
    "02_processed",
    "wave2_wording.rds"
  )
)
```


# Session Info {#sec-session}

```{r}
#| label: exec-time
#| eval: true

end_time <- Sys.time()
cat("Execution time:", round(end_time - start_time, 2), "seconds\n")
```

```{r}
#| label: session-info
#| eval: true

sessioninfo::session_info()
```
