---
title: |
  Code Notebook 2
subtitle: |
  EU 25 Behavioral Games Survey Experiment 2019: Clean Wave 3
author:
  - name: Tristan Muno
    email: tristan.muno@uni-mannheim.de
    affiliations:
      - name: University of Mannheim
        department: School of Social Sciences
date: last-modified
date-format: MMMM D, YYYY
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: true
    code-tools: true
    embed-resources: true
execute:
  echo: true
  warning: true
  eval: true
  message: true
---

# Setup {#sec-setup}

```{r}
#| label: setup

start_time <- Sys.time()

options(width = 80)

p_required <- c(
  "tidyverse", # data wrangling
  "here", # relative paths
  "sessioninfo" # session info
)
packages <- rownames(installed.packages())
p_to_install <- p_required[!(p_required %in% packages)]
if (length(p_to_install) > 0) {
  install.packages(p_to_install)
}
sapply(p_required, require, character.only = TRUE)
rm(p_required, p_to_install, packages)
```

```{r}
#| label: load-data

# wave 3 -----------------------------------------------------------------------
df_wave3 <- readRDS(
  here(
    "data",
    "02_processed",
    "wave3_compiled.rds"
  )
)

# load wording map
wording_map <- read_csv(
  here(
    "data",
    "02_processed",
    "question_wording_map.csv"
  )
)
```


# Phase 6: Coalesce {#sec-coalesce}

Wave 3 is a stripped-down Wave 2.
The priming experiment (Q9–Q19) and its duplicate outcome blocks (Q20–Q34) are absent.
The outcome batteries (Q35–Q41) are universal in Wave 3 and become the canonical variables.
Three variable groups require coalescing before renaming.

## W3 Block I Overview {#sec-block1-overview}

Block Demographics
Q2 — Gender
Q3_1 — Age
Q4 — Nationality; Q4_TEXT if Other
Q5_1/2/3 — Attachment national/EU/Europe
Q6 — Religion; Q6_TEXT if Other
Q7 — Social class
Q8 — Verification check; Q8_TEXT

Block Outcome Batteries (universal in W3)
Q35_1–3 — EU efficacy (understand, care, nosay)
Q36_1–6 — Populism items
Q37_1–6 — Democratic norms, technocracy, party items
Q38_1/2 — EU long-term, EU responsive
Q39_1–3 — EU impact on national econ/culture/politics
Q40_1/2 — EU abolish, EU satisfaction
Q41 — EU integration position

Block Vote and Party ID (universal in W3)
Q52/Q52_TEXT — Party ID
Q53 — Vote turnout likelihood
Q54/Q54_TEXT — Vote choice past
Q55/Q55_TEXT — Vote choice hypothetical
Q56/Q56_TEXT — Vote choice 2014

No coalescing is needed within this block; all columns are mutually exclusive by construction.

```{r}
#| label: w3-block1-rename

df_wave3 <- df_wave3 |>
  rename(
    # meta vars
    meta_startdate = StartDate,
    meta_enddate = EndDate,
    meta_status = Status,
    meta_ipaddress = IPAddress,
    meta_progress = Progress,
    meta_duration_s = Duration..in.seconds.,
    meta_finished = Finished,
    meta_recordeddate = RecordedDate,
    meta_responseid = ResponseId,
    meta_recipient_lastname = RecipientLastName,
    meta_recipient_firstname = RecipientFirstName,
    meta_recipient_email = RecipientEmail,
    meta_external_ref = ExternalReference,
    meta_latitude = LocationLatitude,
    meta_longitude = LocationLongitude,
    meta_distchannel = DistributionChannel,
    meta_lang = UserLanguage,
    meta_country_raw = Country,
    meta_psid = PSID,
    meta_pid = PID,
    meta_device = Device,
    # demographics
    q_gender_raw = Q2,
    q_age_raw = Q3_1,
    q_nationality_raw = Q4,
    q_nationality_other_raw = Q4_TEXT,
    q_identity_country_raw = Q5_1,
    q_identity_eu_raw = Q5_2,
    q_identity_europe_raw = Q5_3,
    q_religion_raw = Q6,
    q_religion_other_raw = Q6_TEXT,
    q_class_raw = Q7,
    q_verif_raw = Q8,
    q_verif2_raw = Q8_TEXT,
    # outcome batteries (universal in W3)
    q_eu_efficacy_understand_raw = Q35_1,
    q_eu_efficacy_care_raw = Q35_2,
    q_eu_efficacy_nosay_raw = Q35_3,
    q_pop_will_raw = Q36_1,
    q_pop_people_raw = Q36_2,
    q_pop_citizen_raw = Q36_3,
    q_pop_reps_raw = Q36_4,
    q_pop_goodevil_raw = Q36_5,
    q_pop_compromise_raw = Q36_6,
    q_dem_compromise_raw = Q37_1,
    q_dem_listen_raw = Q37_2,
    q_tech_experts_raw = Q37_3,
    q_tech_leaders_raw = Q37_4,
    q_party_harm_raw = Q37_5,
    q_people_incompetent_raw = Q37_6,
    q_eu_longterm_raw = Q38_1,
    q_eu_responsive_raw = Q38_2,
    q_eu_imp_nat_econ_raw = Q39_1,
    q_eu_imp_nat_cul_raw = Q39_2,
    q_eu_imp_nat_pol_raw = Q39_3,
    q_eu_abolish_raw = Q40_1,
    q_eu_satisfaction_raw = Q40_2,
    q_euint_pos_raw = Q41,
    # vote choice and party ID (universal in W3)
    q_party_id_raw = Q52,
    q_party_id_other_raw = Q52_TEXT,
    q_vote_turnout_likelihood_raw = Q53,
    q_vote_choice_past_raw = Q54,
    q_vote_choice_past_other_raw = Q54_TEXT,
    q_vote_choice_hypo_raw = Q55,
    q_vote_choice_hypo_other_raw = Q55_TEXT,
    q_vote_choice_past2014_raw = Q56,
    q_vote_choice_past2014_other_raw = Q56_TEXT,
  )
```

## W3 Feeling Thermometers {#sec-thermo}

Q196_* follows the same country-keyed structure as Wave 2.
Each respondent sees up to 6 party thermometer items; the column number depends on country.
Slot stability across waves is assumed; the mapping is copied verbatim from Wave 2.

```{r}
#| label: w3-check-thermo

df_wave3 |>
  select(starts_with("Q196")) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# max count <= 6 confirms questions are naming artefacts, not branching violations
```

```{r}
#| label: w3-coalesce-thermo

df_wave3 <- df_wave3 |>
  mutate(
    q_thermo_1_raw = Q196_1,
    q_thermo_2_raw = case_when(
      meta_country %in%
        c(
          "Austria",
          "Belgium",
          "Croatia",
          "Czechia",
          "Estonia",
          "Finland",
          "France",
          "Greece",
          "Italy",
          "Latvia",
          "Slovakia",
          "Slovenia",
          "Spain",
          "Sweden"
        ) ~ Q196_17,
      meta_country %in%
        c(
          "Bulgaria",
          "Denmark",
          "Hungary",
          "Lithuania",
          "Netherlands",
          "Poland",
          "UK"
        ) ~ Q196_12,
      meta_country == "Germany" ~ Q196_22,
      meta_country == "Ireland" ~ Q196_7,
      meta_country == "Portugal" ~ Q196_27,
      meta_country == "Romania" ~ Q196_18,
      TRUE ~ NA_character_
    ),
    q_thermo_3_raw = case_when(
      meta_country %in%
        c(
          "Austria",
          "Belgium",
          "Croatia",
          "Czechia",
          "Estonia",
          "Finland",
          "France",
          "Greece",
          "Italy",
          "Latvia",
          "Slovakia",
          "Slovenia",
          "Spain",
          "Sweden"
        ) ~ Q196_18,
      meta_country %in%
        c(
          "Bulgaria",
          "Denmark",
          "Hungary",
          "Lithuania",
          "Netherlands",
          "Poland",
          "UK"
        ) ~ Q196_13,
      meta_country == "Germany" ~ Q196_23,
      meta_country == "Ireland" ~ Q196_8,
      meta_country == "Portugal" ~ Q196_28,
      meta_country == "Romania" ~ Q196_19,
      TRUE ~ NA_character_
    ),
    q_thermo_4_raw = case_when(
      meta_country %in%
        c(
          "Austria",
          "Belgium",
          "Croatia",
          "Czechia",
          "Estonia",
          "Finland",
          "France",
          "Greece",
          "Italy",
          "Latvia",
          "Slovakia",
          "Slovenia",
          "Spain",
          "Sweden"
        ) ~ Q196_19,
      meta_country %in%
        c(
          "Bulgaria",
          "Denmark",
          "Hungary",
          "Lithuania",
          "Netherlands",
          "Poland",
          "UK"
        ) ~ Q196_14,
      meta_country == "Germany" ~ Q196_24,
      meta_country == "Ireland" ~ Q196_9,
      meta_country == "Portugal" ~ Q196_29,
      meta_country == "Romania" ~ Q196_20,
      TRUE ~ NA_character_
    ),
    q_thermo_5_raw = case_when(
      meta_country %in%
        c(
          "Austria",
          "Belgium",
          "Croatia",
          "Czechia",
          "Estonia",
          "Finland",
          "France",
          "Greece",
          "Italy",
          "Latvia",
          "Slovakia",
          "Slovenia",
          "Spain",
          "Sweden"
        ) ~ Q196_20,
      meta_country %in%
        c(
          "Bulgaria",
          "Denmark",
          "Hungary",
          "Lithuania",
          "Netherlands",
          "Poland",
          "UK"
        ) ~ Q196_15,
      meta_country == "Germany" ~ Q196_25,
      meta_country == "Ireland" ~ Q196_10,
      meta_country == "Portugal" ~ Q196_30,
      meta_country == "Romania" ~ Q196_21,
      TRUE ~ NA_character_
    ),
    q_thermo_6_raw = case_when(
      meta_country %in%
        c(
          "Austria",
          "Belgium",
          "Croatia",
          "Czechia",
          "Estonia",
          "Finland",
          "France",
          "Greece",
          "Italy",
          "Latvia",
          "Slovakia",
          "Slovenia",
          "Spain",
          "Sweden"
        ) ~ Q196_21,
      meta_country %in%
        c(
          "Bulgaria",
          "Denmark",
          "Hungary",
          "Lithuania",
          "Netherlands",
          "Poland",
          "UK"
        ) ~ Q196_16,
      meta_country == "Germany" ~ Q196_26,
      meta_country == "Ireland" ~ Q196_11,
      meta_country == "Portugal" ~ Q196_31,
      meta_country == "Romania" ~ Q196_22,
      TRUE ~ NA_character_
    )
  ) |>
  select(-starts_with("Q196"))
```

## W3 Campaign and Media {#sec-campaign}

Q199 (EU campaign sources) and Q200 (campaign activity) are universal in Wave 3.

```{r}
#| label: w3-campaign-rename

df_wave3 <- df_wave3 |>
  rename(
    q_eu_campaign_sources_raw = Q199,
    q_eu_campaign_sources_other_raw = Q199_TEXT,
    q_campaign_activity_raw = Q200,
    q_campaign_activity_other_raw = Q200_TEXT,
  )
```

## CJEU 4-Arm Experiment {#sec-cjeu}

Wave 3 uses the full 4-arm CJEU priming experiment: majority (Q201), minority (Q204), control-text (Q207), control-notext (Q210).
Each arm has its own timing block; outcomes Q203_1/2 absorb Q206/Q209/Q211 for abolish and satisfaction; Q208 absorbs Q212 for the CJEU position item (control conditions only).
The coalesced columns are renamed to canonical non-suffixed names (no `_fra_`).

```{r}
#| label: w3-cjeu-explore

# timings: at most 1 arm per respondent
df_wave3 |>
  select(
    Q201_Click.Count,
    Q204_Click.Count,
    Q207_Click.Count,
    Q210_Click.Count
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave3 |>
  select(
    Q201_First.Click,
    Q204_First.Click,
    Q207_First.Click,
    Q210_First.Click
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave3 |>
  select(
    Q201_Last.Click,
    Q204_Last.Click,
    Q207_Last.Click,
    Q210_Last.Click
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave3 |>
  select(
    Q201_Page.Submit,
    Q204_Page.Submit,
    Q207_Page.Submit,
    Q210_Page.Submit
  ) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# outcomes: abolish and satisfaction
df_wave3 |>
  select(Q203_1, Q206_1, Q209_1, Q211_1) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

df_wave3 |>
  select(Q203_2, Q206_2, Q209_2, Q211_2) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)

# CJEU position (control conditions only)
df_wave3 |>
  select(Q208, Q212) |>
  mutate(non_na_count = rowSums(!is.na(across(everything())))) |>
  count(non_na_count)
```

```{r}
#| label: w3-cjeu-coalesce

df_wave3 <- df_wave3 |>
  mutate(
    # condition label
    prime_cjeu_condition = case_when(
      !is.na(Q201_First.Click) ~ "majority",
      !is.na(Q204_First.Click) ~ "minority",
      !is.na(Q207_First.Click) ~ "control_text",
      !is.na(Q210_First.Click) ~ "control_notext"
    ),
    # condition text
    prime_cjeu_text = case_match(
      prime_cjeu_condition,
      "majority" ~ "A recent analysis of the Court of Justice of the European Union's (CJEU) decisions finds that the institution strongly favors actions taken by the European Commission at the expense of parties or groups that are opposed to the European Commission. Specifically, this study finds that the CJEU regularly upholds legislation passed by the European Commission.",
      "minority" ~ "A recent analysis of the Court of Justice of the European Union's (CJEU) decisions finds that the institution strongly tends to protect parties or groups that are opposed to the European Commission at the expense of actions taken by the European Commission. Specifically, this study finds that the CJEU regularly strikes down legislation passed by the Commission to protect parties or groups that are opposed to the European Commission.",
      "control_text" ~ "In thinking about the Court of Justice of the European Union's (CJEU) decisions more generally, some people argue that it tends to favor actions taken by the European Commission at the expense of parties or groups that are opposed to the European Commission. Others contend that the CJEU tends to protect parties or groups that are opposed to the European Commission even if it means striking down actions taken by the European Commission.",
      "control_notext" ~ ""
    ),
    # coalesce timings
    Q201_First.Click = coalesce(
      Q201_First.Click,
      Q204_First.Click,
      Q207_First.Click,
      Q210_First.Click
    ),
    Q201_Last.Click = coalesce(
      Q201_Last.Click,
      Q204_Last.Click,
      Q207_Last.Click,
      Q210_Last.Click
    ),
    Q201_Page.Submit = coalesce(
      Q201_Page.Submit,
      Q204_Page.Submit,
      Q207_Page.Submit,
      Q210_Page.Submit
    ),
    Q201_Click.Count = coalesce(
      Q201_Click.Count,
      Q204_Click.Count,
      Q207_Click.Count,
      Q210_Click.Count
    ),
    # coalesce outcomes
    Q203_1 = coalesce(Q203_1, Q206_1, Q209_1, Q211_1),
    Q203_2 = coalesce(Q203_2, Q206_2, Q209_2, Q211_2),
    Q208 = coalesce(Q208, Q212)
  ) |>
  select(
    -Q204_First.Click,
    -Q204_Last.Click,
    -Q204_Page.Submit,
    -Q204_Click.Count,
    -Q207_First.Click,
    -Q207_Last.Click,
    -Q207_Page.Submit,
    -Q207_Click.Count,
    -Q210_First.Click,
    -Q210_Last.Click,
    -Q210_Page.Submit,
    -Q210_Click.Count,
    -Q206_1,
    -Q206_2,
    -Q209_1,
    -Q209_2,
    -Q211_1,
    -Q211_2,
    -Q212
  ) |>
  rename(
    prime_cjeu_firstclick = Q201_First.Click,
    prime_cjeu_lastclick = Q201_Last.Click,
    prime_cjeu_pagesubmit = Q201_Page.Submit,
    prime_cjeu_clickcount = Q201_Click.Count,
    q_cjeu_pos_raw = Q208,
    q_cjeu_abolish_raw = Q203_1,
    q_cjeu_satisfaction_raw = Q203_2
  )
```

## Occupation Duplicates {#sec-occ}

Q247/Q248 (current and last occupation) have country-specific duplicates at Q267/Q268 and Q365/Q367.
These are coalesced and the redundant columns dropped before the final rename.

```{r}
#| label: w3-placements-coalesce

df_wave3 <- df_wave3 |>
  mutate(
    # occupation duplicates
    Q247 = coalesce(Q247, Q267, Q365),
    Q248 = coalesce(Q248, Q268, Q367),
  ) |>
  select(
    -Q267,
    -Q268,
    -Q365,
    -Q367
  )
```

## W3 Political Norms and Remaining Block {#sec-norms}

Q218_1–6 political norms battery is universal in Wave 3.
Q219–Q248 covers economic evaluations, nativism, satisfaction with democracy, political interest, EU knowledge, EU trust, left-right placements, EU integration placements, and final sociodemographics.

```{r}
#| label: w3-norms-rename

df_wave3 <- df_wave3 |>
  rename(
    # norms battery
    q_norm_tol_opposition_raw = Q218_1,
    q_norm_order_over_freedom_raw = Q218_2,
    q_norm_disobey_unjustlaw_raw = Q218_3,
    q_norm_disobey_gov_raw = Q218_4,
    q_norm_bypass_law_raw = Q218_5,
    q_norm_gov_bend_law_raw = Q218_6,
    # econ evaluations
    q_eval_econ_eur_raw = Q219_1,
    q_eval_econ_nat_raw = Q219_2,
    q_eval_fin_household_raw = Q219_3,
    q_eval_job_raw = Q219_4,
    # globalization
    q_global_nat_econ_raw = Q220_1,
    q_global_cult_raw = Q220_2,
    q_global_nosay_raw = Q220_3,
    q_global_control_raw = Q220_4,
    # satisfaction with democracy
    q_satis_demo_nat_raw = Q221_1,
    q_satis_demo_eu_raw = Q221_2,
    # political interest
    q_nat_int_raw = Q229_1,
    q_eu_int_raw = Q229_2,
    # nativism B
    q_nativ_econ_raw = Q230_1,
    q_nativ_cult_raw = Q230_2,
    # EU knowledge
    q_eu_know_1_raw = Q231_1,
    q_eu_know_2_raw = Q231_2,
    q_eu_know_3_raw = Q231_3,
    q_eu_know_4_raw = Q231_4,
    q_eu_know_5_raw = Q231_5,
    # EU informed
    q_eu_informed_com_raw = Q232_1,
    q_eu_informed_cou_raw = Q232_2,
    q_eu_informed_ep_raw = Q232_3,
    q_eu_informed_cjeu_raw = Q232_4,
    # EU trust
    q_eu_trust_com_raw = Q233_1,
    q_eu_trust_cou_raw = Q233_2,
    q_eu_trust_ep_raw = Q233_3,
    q_eu_trust_cjeu_raw = Q233_4,
    # preferences
    q_risk_taking = Q234,
    q_future_discount = Q235,
    # LR self
    q_lr_self_raw = Q236,
    # LR party placements
    q_lr_party_1_raw = Q237_1,
    q_lr_party_2_raw = Q237_2,
    q_lr_party_3_raw = Q237_3,
    q_lr_party_4_raw = Q237_4,
    q_lr_party_5_raw = Q237_5,
    q_lr_party_6_raw = Q237_6,
    q_lr_party_7_raw = Q237_7,
    q_lr_party_8_raw = Q237_8,
    # LR EU institutions
    q_lr_com_raw = Q238_1,
    q_lr_cou_raw = Q238_2,
    q_lr_ep_raw = Q238_3,
    q_lr_cjeu_raw = Q238_4,
    # efficacy
    q_nat_efficacy_understand_raw = Q239_1,
    q_nat_efficacy_care_raw = Q239_2,
    q_nat_efficacy_nosay_raw = Q239_3,
    # EU integration self
    q_euint_self_raw = Q240,
    # EU integration party placements
    q_euint_party_1_raw = Q241_1,
    q_euint_party_2_raw = Q241_2,
    q_euint_party_3_raw = Q241_3,
    q_euint_party_4_raw = Q241_4,
    q_euint_party_5_raw = Q241_5,
    q_euint_party_6_raw = Q241_6,
    q_euint_party_7_raw = Q241_7,
    q_euint_party_8_raw = Q241_8,
    # EU integration bodies
    q_euint_com_raw = Q242_1,
    q_euint_cou_raw = Q242_2,
    q_euint_ep_raw = Q242_3,
    q_euint_cjeu_raw = Q242_4,
    # education and sociodemographics
    q_edu_age_stop_raw = Q243_1,
    q_rural_urban_raw = Q244,
    q_postal_code_raw = Q245,
    q_region = Q246,
    q_occ_current_raw = Q247,
    q_occ_last_raw = Q248,
  )
```

# Condensed W3 Question Wordings {#sec-wordings}

```{r}
#| label: w3-question-wordings

rename_vec_w3 <- c(
  # meta
  meta_startdate = "StartDate",
  meta_enddate = "EndDate",
  meta_status = "Status",
  meta_ipaddress = "IPAddress",
  meta_progress = "Progress",
  meta_duration_s = "Duration..in.seconds.",
  meta_finished = "Finished",
  meta_recordeddate = "RecordedDate",
  meta_responseid = "ResponseId",
  meta_recipient_lastname = "RecipientLastName",
  meta_recipient_firstname = "RecipientFirstName",
  meta_recipient_email = "RecipientEmail",
  meta_external_ref = "ExternalReference",
  meta_latitude = "LocationLatitude",
  meta_longitude = "LocationLongitude",
  meta_distchannel = "DistributionChannel",
  meta_lang = "UserLanguage",
  meta_country_raw = "Country",
  meta_psid = "PSID",
  meta_pid = "PID",
  meta_device = "Device",
  # demographics
  q_gender_raw = "Q2",
  q_age_raw = "Q3_1",
  q_nationality_raw = "Q4",
  q_nationality_other_raw = "Q4_TEXT",
  q_identity_country_raw = "Q5_1",
  q_identity_eu_raw = "Q5_2",
  q_identity_europe_raw = "Q5_3",
  q_religion_raw = "Q6",
  q_religion_other_raw = "Q6_TEXT",
  q_class_raw = "Q7",
  q_verif_raw = "Q8",
  q_verif2_raw = "Q8_TEXT",
  # outcome batteries
  q_eu_efficacy_understand_raw = "Q35_1",
  q_eu_efficacy_care_raw = "Q35_2",
  q_eu_efficacy_nosay_raw = "Q35_3",
  q_pop_will_raw = "Q36_1",
  q_pop_people_raw = "Q36_2",
  q_pop_citizen_raw = "Q36_3",
  q_pop_reps_raw = "Q36_4",
  q_pop_goodevil_raw = "Q36_5",
  q_pop_compromise_raw = "Q36_6",
  q_dem_compromise_raw = "Q37_1",
  q_dem_listen_raw = "Q37_2",
  q_tech_experts_raw = "Q37_3",
  q_tech_leaders_raw = "Q37_4",
  q_party_harm_raw = "Q37_5",
  q_people_incompetent_raw = "Q37_6",
  q_eu_longterm_raw = "Q38_1",
  q_eu_responsive_raw = "Q38_2",
  q_eu_imp_nat_econ_raw = "Q39_1",
  q_eu_imp_nat_cul_raw = "Q39_2",
  q_eu_imp_nat_pol_raw = "Q39_3",
  q_eu_abolish_raw = "Q40_1",
  q_eu_satisfaction_raw = "Q40_2",
  q_euint_pos_raw = "Q41",
  # vote choice and party ID
  q_party_id_raw = "Q52",
  q_party_id_other_raw = "Q52_TEXT",
  q_vote_turnout_likelihood_raw = "Q53",
  q_vote_choice_past_raw = "Q54",
  q_vote_choice_past_other_raw = "Q54_TEXT",
  q_vote_choice_hypo_raw = "Q55",
  q_vote_choice_hypo_other_raw = "Q55_TEXT",
  q_vote_choice_past2014_raw = "Q56",
  q_vote_choice_past2014_other_raw = "Q56_TEXT",
  # thermometers (derived)
  q_thermo_1_raw = "q_thermo_1_raw",
  q_thermo_2_raw = "q_thermo_2_raw",
  q_thermo_3_raw = "q_thermo_3_raw",
  q_thermo_4_raw = "q_thermo_4_raw",
  q_thermo_5_raw = "q_thermo_5_raw",
  q_thermo_6_raw = "q_thermo_6_raw",
  # campaign and media
  q_eu_campaign_sources_raw = "Q199",
  q_eu_campaign_sources_other_raw = "Q199_TEXT",
  q_campaign_activity_raw = "Q200",
  q_campaign_activity_other_raw = "Q200_TEXT",
  # CJEU experiment
  prime_cjeu_condition = "prime_cjeu_condition",
  prime_cjeu_text = "prime_cjeu_text",
  prime_cjeu_firstclick = "Q201_First.Click",
  prime_cjeu_lastclick = "Q201_Last.Click",
  prime_cjeu_pagesubmit = "Q201_Page.Submit",
  prime_cjeu_clickcount = "Q201_Click.Count",
  q_cjeu_pos_raw = "Q208",
  q_cjeu_abolish_raw = "Q203_1",
  q_cjeu_satisfaction_raw = "Q203_2",
  # political norms
  q_norm_tol_opposition_raw = "Q218_1",
  q_norm_order_over_freedom_raw = "Q218_2",
  q_norm_disobey_unjustlaw_raw = "Q218_3",
  q_norm_disobey_gov_raw = "Q218_4",
  q_norm_bypass_law_raw = "Q218_5",
  q_norm_gov_bend_law_raw = "Q218_6",
  # econ evaluations
  q_eval_econ_eur_raw = "Q219_1",
  q_eval_econ_nat_raw = "Q219_2",
  q_eval_fin_household_raw = "Q219_3",
  q_eval_job_raw = "Q219_4",
  # nativism
  q_global_nat_econ_raw = "Q220_1",
  q_global_cult_raw = "Q220_2",
  q_global_nosay_raw = "Q220_3",
  q_global_control_raw = "Q220_4",
  # satisfaction with democracy
  q_satis_demo_nat_raw = "Q221_1",
  q_satis_demo_eu_raw = "Q221_2",
  # political interest
  q_nat_int_raw = "Q229_1",
  q_eu_int_raw = "Q229_2",
  # nativism B
  q_nativ_econ_raw = "Q230_1",
  q_nativ_cult_raw = "Q230_2",
  # EU knowledge
  q_eu_know_1_raw = "Q231_1",
  q_eu_know_2_raw = "Q231_2",
  q_eu_know_3_raw = "Q231_3",
  q_eu_know_4_raw = "Q231_4",
  q_eu_know_5_raw = "Q231_5",
  # EU informed
  q_eu_informed_com_raw = "Q232_1",
  q_eu_informed_cou_raw = "Q232_2",
  q_eu_informed_ep_raw = "Q232_3",
  q_eu_informed_cjeu_raw = "Q232_4",
  # EU trust
  q_eu_trust_com_raw = "Q233_1",
  q_eu_trust_cou_raw = "Q233_2",
  q_eu_trust_ep_raw = "Q233_3",
  q_eu_trust_cjeu_raw = "Q233_4",
  # preferences
  q_risk_taking = "Q234",
  q_future_discount = "Q235",
  # LR self
  q_lr_self_raw = "Q236",
  # LR party placements
  q_lr_party_1_raw = "Q237_1",
  q_lr_party_2_raw = "Q237_2",
  q_lr_party_3_raw = "Q237_3",
  q_lr_party_4_raw = "Q237_4",
  q_lr_party_5_raw = "Q237_5",
  q_lr_party_6_raw = "Q237_6",
  q_lr_party_7_raw = "Q237_7",
  q_lr_party_8_raw = "Q237_8",
  # LR EU institutions
  q_lr_com_raw = "Q238_1",
  q_lr_cou_raw = "Q238_2",
  q_lr_ep_raw = "Q238_3",
  q_lr_cjeu_raw = "Q238_4",
  # efficacy
  q_nat_efficacy_understand_raw = "Q239_1",
  q_nat_efficacy_care_raw = "Q239_2",
  q_nat_efficacy_nosay_raw = "Q239_3",
  # EU integration self
  q_euint_self_raw = "Q240",
  # EU integration party placements
  q_euint_party_1_raw = "Q241_1",
  q_euint_party_2_raw = "Q241_2",
  q_euint_party_3_raw = "Q241_3",
  q_euint_party_4_raw = "Q241_4",
  q_euint_party_5_raw = "Q241_5",
  q_euint_party_6_raw = "Q241_6",
  q_euint_party_7_raw = "Q241_7",
  q_euint_party_8_raw = "Q241_8",
  # EU integration bodies
  q_euint_com_raw = "Q242_1",
  q_euint_cou_raw = "Q242_2",
  q_euint_ep_raw = "Q242_3",
  q_euint_cjeu_raw = "Q242_4",
  # education and sociodemographics
  q_edu_age_stop_raw = "Q243_1",
  q_rural_urban_raw = "Q244",
  q_postal_code_raw = "Q245",
  q_region = "Q246",
  q_occ_current_raw = "Q247",
  q_occ_last_raw = "Q248"
)

wording_map_w3 <- wording_map |>
  filter(wave == 3, col_name %in% rename_vec_w3) |>
  left_join(
    tibble(col_name = rename_vec_w3, new_name = names(rename_vec_w3)),
    by = "col_name"
  ) |>
  select(col_name, new_name, country, wording)
```

```{r}
#| label: tbl-w3-wording-unmatched
#| tbl-cap: "W3 variables with no wording match"

cat("Distinct new_name values:", length(unique(names(rename_vec_w3))), "\n")
cat("Matched rows in wording_map_w3:", nrow(wording_map_w3), "\n")

tibble(new_name = names(rename_vec_w3), col_name = rename_vec_w3) |>
  anti_join(wording_map_w3, by = "new_name") |>
  distinct(new_name, col_name) |>
  knitr::kable()
```

# Save Cleaned W3 Dataset {#sec-save}

```{r}
#| label: save-cleaned-w3

write_rds(
  df_wave3,
  file = here(
    "data",
    "02_processed",
    "wave3_clean.rds"
  )
)

write_rds(
  wording_map_w3,
  file = here(
    "data",
    "02_processed",
    "wave3_wording.rds"
  )
)
```

# Session Info {#sec-session}

```{r}
#| label: exec-time
#| eval: true

end_time <- Sys.time()
cat("Execution time:", round(end_time - start_time, 2), "seconds\n")
```

```{r}
#| label: session-info
#| eval: true

sessioninfo::session_info()
```
