---
title: |
  Code Notebook 2
subtitle: |
  EU 25 Behavioral Games Survey Experiment 2019: Stack Waves
author:
  - name: Tristan Muno
    email: tristan.muno@uni-mannheim.de
    affiliations:
      - name: University of Mannheim
        department: School of Social Sciences
date: last-modified
date-format: MMMM D, YYYY
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: true
    code-tools: true
    embed-resources: true
execute:
  echo: true
  warning: true
  eval: true
  message: true
---

# Setup {#sec-setup}

```{r}
#| label: setup

start_time <- Sys.time()

options(width = 80)

p_required <- c(
  "tidyverse", # data wrangling
  "here", # relative paths
  "sessioninfo" # session info
)
packages <- rownames(installed.packages())
p_to_install <- p_required[!(p_required %in% packages)]
if (length(p_to_install) > 0) {
  install.packages(p_to_install)
}
sapply(p_required, require, character.only = TRUE)
rm(p_required, p_to_install, packages)
```

# Load Cleaned Datasets

```{r}
#| label: load-data

# wave 1 -----------------------------------------------------------------------
df_wave1 <- readRDS(
  here(
    "data",
    "02_processed",
    "wave1_clean.rds"
  )
)

# wave 2 -----------------------------------------------------------------------
df_wave2 <- readRDS(
  here(
    "data",
    "02_processed",
    "wave2_clean.rds"
  )
)

# wave 3 -----------------------------------------------------------------------
df_wave3 <- readRDS(
  here(
    "data",
    "02_processed",
    "wave3_clean.rds"
  )
)
```

# Stacking Strategy (Phase 7)

**Goal:** bind_rows(df_wave1, df_wave2, df_wave3) with columns ordered by presence across waves.

**Steps:**
  
  1. Collect the column names of all three dataframes.
  2. Classify each unique column name by how many waves contain it: present in all 3, exactly 2, or exactly 1.
  3. Within each presence tier, sort columns: universal vars first (alphabetically or by original order), then two-wave vars, then one-wave vars. Within the two- and one-wave tiers, group by which wave(s) they appear in (e.g. W1+W2, W1+W3, W2+W3; then W1-only, W2-only, W3-only).
  4. For each dataframe, add the missing columns as all-NA vectors (type can be logical NA, which bind_rows handles gracefully — or cast explicitly if needed).
  5. Reorder all three dataframes to the unified column order, then bind_rows().
  6. Add/verify meta_wave on the stacked frame (should already exist from the clean files).
  7. Save as data/processed/waves_stacked.rds.

```{r}
#| label: stack-waves

# name vectors
w1 <- names(df_wave1)
w2 <- names(df_wave2)
w3 <- names(df_wave3)

all_cols <- unique(c(w1, w2, w3))

# presence flags
in1 <- all_cols %in% w1
in2 <- all_cols %in% w2
in3 <- all_cols %in% w3
n_waves <- in1 + in2 + in3

# tier labels
tier <- case_match(
  n_waves,
  3 ~ "all3",
  2 ~ case_when(
    in1 & in2 & !in3 ~ "w1w2",
    in1 & !in2 & in3 ~ "w1w3",
    !in1 & in2 & in3 ~ "w2w3"
  ),
  1 ~ case_when(
    in1 ~ "w1only",
    in2 ~ "w2only",
    TRUE ~ "w3only"
  )
)

# tier sort key
tier_order <- c("all3", "w1w2", "w1w3", "w2w3", "w1only", "w2only", "w3only")
tier_rank <- match(tier, tier_order)

# within-tier: preserve first-wave order via position in all_cols
col_df <- tibble(
  col = all_cols,
  tier = tier,
  tier_rank = tier_rank,
  orig_pos = seq_along(all_cols)
) |>
  arrange(tier_rank, orig_pos)

col_order <- col_df$col

# add missing columns as NA
add_missing <- function(df, target_cols) {
  missing <- setdiff(target_cols, names(df))
  df[missing] <- NA
  df[target_cols]
}

df_stacked <- bind_rows(
  add_missing(df_wave1, col_order),
  add_missing(df_wave2, col_order),
  add_missing(df_wave3, col_order)
)

# assertions
stopifnot(nrow(df_stacked) == nrow(df_wave1) + nrow(df_wave2) + nrow(df_wave3))
stopifnot("meta_wave" %in% names(df_stacked))

# summary
tier_summary <- col_df |>
  group_by(tier) |>
  summarise(
    n_cols = n(),
    examples = paste(head(col, 3), collapse = ", "),
    .groups = "drop"
  ) |>
  mutate(tier = factor(tier, levels = tier_order)) |>
  arrange(tier)

print(tier_summary)

# save
saveRDS(df_stacked, here("data/02_processed/waves_stacked.rds"))
cat(
  "Saved waves_stacked.rds —",
  nrow(df_stacked),
  "rows ×",
  ncol(df_stacked),
  "cols\n"
)
```

# Session Info {#sec-session}

```{r}
#| label: exec-time
#| eval: true

end_time <- Sys.time()
cat("Execution time:", round(end_time - start_time, 2), "seconds\n")
```

```{r}
#| label: session-info
#| eval: true

sessioninfo::session_info()
```
