---
title: |
  Code Notebook 2
subtitle: |
  EU 25 Behavioral Games Survey Experiment 2019: Recode Variables
author:
  - name: Tristan Muno
    email: tristan.muno@uni-mannheim.de
    affiliations:
      - name: University of Mannheim
        department: School of Social Sciences
date: last-modified
date-format: MMMM D, YYYY
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: true
    code-tools: true
    embed-resources: true
execute:
  echo: true
  warning: true
  eval: true
  message: true
---

# Setup {#sec-setup}

```{r}
#| label: setup
start_time <- Sys.time()

options(width = 80)

p_required <- c(
  "tidyverse", # data wrangling
  "here", # relative paths
  "future", # parallel backend
  "furrr", # parallel map() functions
  "janitor", # tabyl
  "sessioninfo" # session info
)
packages <- rownames(installed.packages())
p_to_install <- p_required[!(p_required %in% packages)]
if (length(p_to_install) > 0) {
  install.packages(p_to_install)
}
sapply(p_required, require, character.only = TRUE)
rm(p_required, p_to_install, packages)
```

```{r}
#| label: load-data
# stacked waves ----------------------------------------------------------------
df_stacked <- read_rds(
  here(
    "data",
    "02_processed",
    "waves_stacked.rds"
  )
)

# load wording map
wording_map <- read_csv(
  here(
    "data",
    "02_processed",
    "question_wording_map.csv"
  )
)
```

# Recode Variable Values (Phase 8) {#sec-recode}

```{r}
#| label: collect-information
# colnames and current type ----------------------------------------------------
cols <- tibble(
  cols = df_stacked |> colnames(),
  col_type = df_stacked |> map_chr(class)
)
# pre-split by country — workers receive slices, not full df ------------------
countries <- df_stacked |> distinct(meta_country) |> pull(meta_country)
df_by_country <- countries |>
  set_names() |>
  lapply(function(country) filter(df_stacked, meta_country == country))
col_names <- names(df_stacked) # small vector, fine to export
compute_groups <- function(df_country) {
  cat(paste0("starting\n"))
  # signatures in one pass -----------------------------------------------------
  signatures <- sapply(seq_len(ncol(df_country)), function(i) {
    df_country[[i]] |>
      as.character() |>
      unique() |>
      sort() |>
      paste(collapse = "||")
  })
  # group + name back ----------------------------------------------------------
  groups <- split(seq_along(signatures), signatures)
  lapply(groups, function(idx) col_names[idx])
}
# run in parallel for each country --------------------------------------------
plan(multisession)
groups_named <- future_map(df_by_country, compute_groups)
plan(sequential)
```

## Meta Variables {#sec-meta}

```{r}
#| label: recode-meta
df_stacked_recoded <- df_stacked |>
  mutate(
    # META VARS ----------------------------------------------------------------
    meta_wave = as.integer(meta_wave),
    # meta_country = ,
    meta_startdate = as.POSIXct(meta_startdate),
    meta_enddate = as.POSIXct(meta_enddate),
    # meta_status = ,
    # meta_ipaddress = ,
    meta_progress = as.integer(meta_progress),
    meta_duration_s = as.integer(meta_duration_s),
    meta_finished = as.logical(meta_finished),
    meta_recordeddate = as.POSIXct(meta_recordeddate),
    # meta_responseid = ,
    # meta_recipient_lastname = ,
    # meta_recipient_firstname = ,
    # meta_recipient_email = ,
    # meta_external_ref = ,
    meta_latitude = as.numeric(meta_latitude),
    meta_longitude = as.numeric(meta_longitude),
    # meta_distchannel = ,
    # meta_lang = ,
  )
```

## Gender {#sec-gender}

```{r}
#| label: value-labels-gender
# GENDER -----------------------------------------------------------------------
male_vec <- c(
  "Male",
  "Männlich",
  "Мъж",
  "Muškarac",
  "Muž",
  "Mand",
  "Mees",
  "Mies",
  "Homme",
  "Männlich",
  "Άνδρας",
  "Férfi",
  "Maschio",
  "Vīrietis",
  "Vyras",
  "Man",
  "Mężczyzna",
  "Masculino",
  "Bărbat",
  "Muž",
  "Moški",
  "Hombre",
  "Man",
  "Man"
)
female_vec <- c(
  "Female",
  "Weiblich",
  "Жена",
  "Žena",
  "Žena",
  "Kvinde",
  "Naine",
  "Nainen",
  "Femme",
  "Weiblich",
  "Γυναίκα",
  "Nő",
  "Femmina",
  "Sieviete",
  "Moteris",
  "Vrouw",
  "Kobieta",
  "Feminino",
  "Femenino",
  "Femeie",
  "Žena",
  "Ženski",
  "Mujer",
  "Kvinna",
  "Vrouw",
  "2"
)
```

```{r}
#| label: recode-gender
df_stacked_recoded <- df_stacked_recoded |>
  mutate(
    # GENDER -------------------------------------------------------------------
    q_gender = case_when(
      q_gender_raw %in% male_vec ~ "male",
      q_gender_raw %in% female_vec ~ "female",
      !is.na(q_gender_raw) ~ "other"
    ),
  )
```

```{r}
#| label: validate-gender-recode
df_stacked_recoded |>
  select(q_gender, q_gender_raw) |>
  filter(is.na(q_gender) & !is.na(q_gender_raw)) |>
  distinct(q_gender_raw)
```

## Age {#sec-age}

```{r}
#| label: recode-age
df_stacked_recoded <- df_stacked_recoded |>
  mutate(
    # AGE ----------------------------------------------------------------------
    q_age = as.integer(str_extract(q_age_raw, "\\d+")),
  )
```

```{r}
#| label: validate-age-recode
df_stacked_recoded |>
  select(q_age, q_age_raw) |>
  filter(is.na(q_age) & !is.na(q_age_raw)) |>
  distinct(q_age_raw)
```

## Nationality {#sec-nationality}

```{r}
#| label: value-labels-nationality
# NATIONALITY ------------------------------------------------------------------
austria_vec <- c(
  "Österreich",
  "Австрия",
  "Austrija",
  "Rakousko",
  "Austria",
  "Itävalta",
  "Autriche",
  "Αυστρία",
  "Ausztria",
  "Oostenrijk",
  "Avstrija",
  "Österrike"
)

belgium_vec <- c(
  "Belgien",
  "Belgique",
  "België",
  "Белгия",
  "Belgija",
  "Belgie",
  "Belgia",
  "Belgio",
  "Belgium",
  "Beļģija",
  "Belgija",
  "Belgicko",
  "Bélgica"
)

bulgaria_vec <- c(
  "Bulgarien",
  "България",
  "Bugarska",
  "Bulgaaria",
  "Bulgaria",
  "Bulgarie",
  "Βουλγαρία",
  "Bulgária",
  "Bulgārija",
  "Bulgarija",
  "Bulgarije",
  "Bułgaria",
  "Bolgarija",
  "Bulharsko"
)

croatia_vec <- c(
  "Kroatien",
  "Hrvatska",
  "Chorvatsko",
  "Kroatia",
  "Croatie",
  "Croazia",
  "Croatia",
  "Kroatija",
  "Chorwacja",
  "Croaţia",
  "Hrvaška",
  "Croacia"
)

czechia_vec <- c(
  "Tschechische Republik",
  "Tsjechië",
  "Češka",
  "Česká republika",
  "Csehország",
  "Czech Republic",
  "Čekijos Respublika",
  "Czechy",
  "Češka republika",
  "Tjeckien"
)

denmark_vec <- c(
  "Dänemark",
  "Danemark",
  "Denemarken",
  "Дания",
  "Danska",
  "Dania",
  "Danmark",
  "Tanska",
  "Denmark",
  "Dānija",
  "Danija",
  "Danemarca",
  "Dánsko"
)

estonia_vec <- c(
  "Estland",
  "Estonija",
  "Estonsko",
  "Eesti",
  "Viro",
  "Estonie",
  "Észtország",
  "Estonia",
  "Igaunija",
  "Estonija"
)

finland_vec <- c(
  "Finnland",
  "Finska",
  "Finland",
  "Suomi",
  "Finlande",
  "Φινλανδία",
  "Finnország",
  "Suomija",
  "Finlanda"
)

france_vec <- c(
  "Frankreich",
  "France",
  "Frankrijk",
  "Francuska",
  "Frankrig",
  "Ranska",
  "Γαλλία",
  "Francija",
  "França",
  "Franţa",
  "Francúzsko",
  "Francia",
  "Frankrike"
)

germany_vec <- c(
  "Deutschland",
  "Allemagne",
  "Duitsland",
  "Германия",
  "Njemačka",
  "Tyskland",
  "Saksa",
  "Γερμανία",
  "Németország",
  "Germania",
  "Germany",
  "Vācija",
  "Niemcy",
  "Alemanha",
  "Nemčija",
  "Nemecko",
  "Alemania"
)

greece_vec <- c(
  "Griechenland",
  "Řecko",
  "Ελλάδα",
  "Grecia",
  "Greece",
  "Grieķija",
  "Graikija",
  "Griekenland",
  "Grecja",
  "Grčija",
  "Grécko",
  "Grekland"
)

hungary_vec <- c(
  "Ungarn",
  "Mađarska",
  "Ungari",
  "Magyarország",
  "Hungary",
  "Hongarije",
  "Ungaria",
  "Madžarska",
  "Maďarsko"
)

ireland_vec <- c(
  "Irska",
  "Ireland",
  "Īrija",
  "Airija",
  "Ierland",
  "Irlandia",
  "Irlanda"
)

italy_vec <- c(
  "Italien",
  "Italie",
  "Italië",
  "Italija",
  "Olaszország",
  "Italia",
  "Italy",
  "Itālija",
  "Itália"
)

latvia_vec <- c(
  "Lettland",
  "Letland",
  "Läti",
  "Lettonia",
  "Latvia",
  "Λετονία",
  "Latvija",
  "Letonia"
)

lithuania_vec <- c(
  "Litauen",
  "Lituanie",
  "Litouwen",
  "Leedu",
  "Lithuania",
  "Lietuva",
  "Litwa",
  "Lituania",
  "Litva"
)

netherlands_vec <- c(
  "Niederlande",
  "Pays-Bas",
  "Nederland",
  "Nizozemska",
  "Nederlandene",
  "Alankomaat (Hollanti)",
  "Netherlands",
  "Holandia",
  "Holanda",
  "Nizozemska"
)

poland_vec <- c(
  "Polen",
  "Pologne",
  "Poljska",
  "Polsko",
  "Poola",
  "Puola",
  "Πολωνία",
  "Polonia",
  "Poland",
  "Polija",
  "Lenkija",
  "Polska",
  "Polónia",
  "Poľsko"
)

portugal_vec <- c(
  "Portugal",
  "Португалия",
  "Portugalsko",
  "Portugali",
  "Portugalija",
  "Portugalia"
)

romania_vec <- c(
  "Rumänien",
  "Roumanie",
  "Roemenië",
  "Rumænien",
  "Romania",
  "Ρουμανία",
  "Románia",
  "România",
  "Rumunsko",
  "Rumanía"
)

slovakia_vec <- c(
  "Slowakei",
  "Slovaquie",
  "Slovačka",
  "Slovensko",
  "Slovakkia",
  "Szlovákia",
  "Slovakia",
  "Slovaška"
)

slovenia_vec <- c(
  "Slowenien",
  "Slovenija",
  "Slovinsko",
  "Slovenien",
  "Sloveenia",
  "Slovenia",
  "Slovēnija",
  "Slovėnija",
  "Eslovénia",
  "Eslovenia"
)

spain_vec <- c(
  "Spanien",
  "Espagne",
  "Spanje",
  "Hispaania",
  "Spagna",
  "Spain",
  "Ispanija",
  "Espanha",
  "Španija",
  "Španielsko",
  "España"
)

sweden_vec <- c(
  "Suède",
  "Zweden",
  "Sverige",
  "Ruotsi",
  "Sweden",
  "Švedija",
  "Szwecja",
  "Suedia",
  "Švedska"
)

united_kingdom_vec <- c(
  "Vereinigtes Königreich (Großbritannien, Nordirland)",
  "Verenigd Koninkrijk (Groot-Brittannië, Noord-Ierland)",
  "Ujedinjena Kraljevina Velike Britanije i Sjeverne Irske",
  "Velká Británie",
  "Storbritannien, Nordirland",
  "Yhdistynyt kuningaskunta (Iso-Britannia, Pohjois-Irlanti)",
  "Royaume-Uni (Grande Bretagne, Irlande du Nord)",
  "Egyesült Királyság (Nagy-Britannia, Észak-Írország)",
  "United Kingdom (Great Britain, Northern Ireland)",
  "Apvienotā Karaliste (Lielbritānija, Ziemeļīrija)",
  "Jungtinė Karalystė (Didžioji Britanija, Šiaurės Airija)",
  "Zjednoczone Królestwo (Wielka Brytania, Irlandia Północna)",
  "Reino Unido (Grã-Bretanha, Irlanda do Norte)",
  "Regatul Unit (Marea Britanie, Irlanda de Nord)",
  "Združeno kraljestvo (Velika Britanija, Severna Irska)",
  "Reino Unido (Gran Bretaña, Irlanda del Norte)",
  "Storbritannien (England, Skottland, Wales, Nordirland)"
)

luxembourg_vec <- c(
  "Luxemburg",
  "Luxembourg",
  "Luksemburg",
  "Liuksemburgas"
)

malta_vec <- c(
  "Malta",
  "Málta"
)

cyprus_vec <- c(
  "Cipar",
  "Kyperská republika",
  "Cypern (Syd)",
  "Cipro (sud)",
  "Κυπριακή Δημοκρατία",
  "Ciprusi - Köztársaság",
  "Kipro Respublika",
  "Cypr (południowy)",
  "Republic of Cyprus"
)

other_country_vec <- c(
  "Andere Länder",
  "Autre pays",
  "Andere landen",
  "Друга държава",
  "Ostale zemlje",
  "Jiná země",
  "Andre lande",
  "Muu riik",
  "Joku muu maa/maat",
  "Άλλες χώρες",
  "Más ország",
  "Altri paesi",
  "Other countries",
  "Citas valstis",
  "Kitos valstybės",
  "Inne kraje",
  "Outros países",
  "Alte ţări",
  "Druge države",
  "Iné krajiny",
  "Otros países",
  "Annat land",
  "Other country"
)

dont_know_vec <- c(
  "Weiß nicht",
  "Ne zna",
  "Ne znam",
  "Nevím",
  "Ved ikke",
  "Ei oska öelda",
  "En tiedä",
  "Ne sait pas",
  "Nem tudom",
  "Don't know",
  "Nezinu",
  "Nežinau",
  "Weet niet",
  "Nie wiem",
  "Não sei",
  "Nu ştiu",
  "Ne vem",
  "Nevie, bez odpovede",
  "Neviem",
  "No lo sé",
  "Vet ej"
)

# Nationality lookup
nat_lookup <- c(
  setNames(rep("Austria", length(austria_vec)), austria_vec),
  setNames(rep("Belgium", length(belgium_vec)), belgium_vec),
  setNames(rep("Bulgaria", length(bulgaria_vec)), bulgaria_vec),
  setNames(rep("Croatia", length(croatia_vec)), croatia_vec),
  setNames(rep("Czechia", length(czechia_vec)), czechia_vec),
  setNames(rep("Denmark", length(denmark_vec)), denmark_vec),
  setNames(rep("Estonia", length(estonia_vec)), estonia_vec),
  setNames(rep("Finland", length(finland_vec)), finland_vec),
  setNames(rep("France", length(france_vec)), france_vec),
  setNames(rep("Germany", length(germany_vec)), germany_vec),
  setNames(rep("Greece", length(greece_vec)), greece_vec),
  setNames(rep("Hungary", length(hungary_vec)), hungary_vec),
  setNames(rep("Ireland", length(ireland_vec)), ireland_vec),
  setNames(rep("Italy", length(italy_vec)), italy_vec),
  setNames(rep("Latvia", length(latvia_vec)), latvia_vec),
  setNames(rep("Lithuania", length(lithuania_vec)), lithuania_vec),
  setNames(rep("Luxembourg", length(luxembourg_vec)), luxembourg_vec),
  setNames(rep("Malta", length(malta_vec)), malta_vec),
  setNames(rep("Cyprus", length(cyprus_vec)), cyprus_vec),
  setNames(rep("Netherlands", length(netherlands_vec)), netherlands_vec),
  setNames(rep("Poland", length(poland_vec)), poland_vec),
  setNames(rep("Portugal", length(portugal_vec)), portugal_vec),
  setNames(rep("Romania", length(romania_vec)), romania_vec),
  setNames(rep("Slovakia", length(slovakia_vec)), slovakia_vec),
  setNames(rep("Slovenia", length(slovenia_vec)), slovenia_vec),
  setNames(rep("Spain", length(spain_vec)), spain_vec),
  setNames(rep("Sweden", length(sweden_vec)), sweden_vec),
  setNames(
    rep("United Kingdom", length(united_kingdom_vec)),
    united_kingdom_vec
  ),
  setNames(rep("Other", length(other_country_vec)), other_country_vec)
)

# Translate tokens via lookup
translate_nat <- function(x) {
  if (is.na(x)) {
    return(NA_character_)
  }
  tokens <- str_trim(str_split(x, ",")[[1]])
  translated <- nat_lookup[tokens]
  # keep original token if not found
  translated[is.na(translated)] <- tokens[is.na(translated)]
  paste(translated, collapse = ", ")
}
```

```{r}
#| label: recode-nationality
df_stacked_recoded <- df_stacked_recoded |>
  mutate(
    # NATIONALITY --------------------------------------------------------------
    q_nationality = map_chr(q_nationality_raw, translate_nat),
    q_nationality_n = map_int(q_nationality_raw, \(x) {
      if (is.na(x)) NA_integer_ else length(str_split(x, ",")[[1]])
    }),
    q_nationality_other = case_when(
      str_trim(q_nationality_other_raw) %in%
        c("afghan", "afghanistanskt") ~ "Afghanistan",
      str_trim(q_nationality_other_raw) %in%
        c("Albanië", "albania") ~ "Albania",
      str_trim(q_nationality_other_raw) %in%
        c("Algérie", "algerie", "ALGERIE") ~ "Algeria",
      str_trim(q_nationality_other_raw) %in% c("angola", "Angola") ~ "Angola",
      str_trim(q_nationality_other_raw) %in%
        c(
          "Argentina",
          "argentina",
          "Argentinien",
          "ARGENTINA",
          "argentine"
        ) ~ "Argentina",
      str_trim(q_nationality_other_raw) %in%
        c("Armenia", "Armenien") ~ "Armenia",
      str_trim(q_nationality_other_raw) %in%
        c("Australien", "AUSTRALIA", "Australia") ~ "Australia",
      str_trim(q_nationality_other_raw) %in%
        c("Österreich", "austria") ~ "Austria",
      str_trim(q_nationality_other_raw) %in%
        c("Azerbajdzjan", "Azerbaijan") ~ "Azerbaijan",
      str_trim(q_nationality_other_raw) %in%
        c("Bangladesh", "BANGLADESHI") ~ "Bangladesh",
      str_trim(q_nationality_other_raw) %in%
        c(
          "Беларусь",
          "Belarus",
          "belarus",
          "Bělorusko",
          "valko-venäjä"
        ) ~ "Belarus",
      str_trim(q_nationality_other_raw) %in% c("Bolivia") ~ "Bolivia",
      str_trim(q_nationality_other_raw) %in%
        c(
          "BiH",
          "Bih",
          "Bosna i Hercegovina",
          "Bosna in Herzegovina",
          "Bosnien & Hercegovina",
          "Bosnien & Hercegovina",
          "Bosnia",
          "bosnien",
          "Bosnien"
        ) ~ "Bosnia and Herzegovina",
      str_trim(q_nationality_other_raw) %in%
        c(
          "Brésil",
          "Brasil",
          "brasil",
          "BRASIL",
          "Brazil",
          "brazil",
          "Brazilie",
          "Brasilien",
          "ΒΡΑΖΙΛΙΑ",
          "brazilian",
          "Brazilian",
          "Brasilian",
          "Brasileira"
        ) ~ "Brazil",
      str_trim(q_nationality_other_raw) %in%
        c(
          "Kanada",
          "Canada",
          "canada",
          "Canadian",
          "canadian",
          "Kanadishe",
          "ΚΑΝΑΔΑΣ"
        ) ~ "Canada",
      str_trim(q_nationality_other_raw) %in%
        c("cabo verde", "Cabo Verde") ~ "Cape Verde",
      str_trim(q_nationality_other_raw) %in%
        c("cameroun", "Cameroun", "Cameroon") ~ "Cameroon",
      str_trim(q_nationality_other_raw) %in%
        c("centrafricaine") ~ "Central African Republic",
      str_trim(q_nationality_other_raw) %in% c("chile") ~ "Chile",
      str_trim(q_nationality_other_raw) %in%
        c("China", "Chinese", "CHINOISE") ~ "China",
      str_trim(q_nationality_other_raw) %in%
        c("colombia", "Colombia") ~ "Colombia",
      str_trim(q_nationality_other_raw) %in%
        c(
          "Hrvatska",
          "hrvatska",
          "Hrvatsko",
          "croatia"
        ) ~ "Croatia",
      str_trim(q_nationality_other_raw) %in%
        c("cubaanse", "Cuba", "cuba") ~ "Cuba",
      str_trim(q_nationality_other_raw) %in%
        c("RD CONGO") ~ "Democratic Republic of the Congo",
      str_trim(q_nationality_other_raw) %in% c("Ecuador") ~ "Ecuador",
      str_trim(q_nationality_other_raw) %in%
        c("Egypt", "Egy", "egyptian") ~ "Egypt",
      str_trim(q_nationality_other_raw) %in% c("El Salvador") ~ "El Salvador",
      str_trim(q_nationality_other_raw) %in%
        c("Eesti", "eesti", "eestlane") ~ "Estonia",
      str_trim(q_nationality_other_raw) %in% c("Fijian") ~ "Fiji",
      str_trim(q_nationality_other_raw) %in%
        c("suomi", "finska", "finland", "Finland") ~ "Finland",
      str_trim(q_nationality_other_raw) %in% c("Gruzinsko") ~ "Georgia",
      str_trim(q_nationality_other_raw) %in% c("DDR", "Tyskland") ~ "Germany",
      str_trim(q_nationality_other_raw) %in% c("Ghana") ~ "Ghana",
      str_trim(q_nationality_other_raw) %in% c("Guatemala") ~ "Guatemala",
      str_trim(q_nationality_other_raw) %in% c("guyana") ~ "Guyana",
      str_trim(q_nationality_other_raw) %in% c("Haiti") ~ "Haiti",
      str_trim(q_nationality_other_raw) %in%
        c(
          "unkari",
          "magyar",
          "Magyarország",
          "magyarország",
          "MAGYARORSZÁG"
        ) ~ "Hungary",
      str_trim(q_nationality_other_raw) %in% c("Island") ~ "Iceland",
      str_trim(q_nationality_other_raw) %in%
        c(
          "Indien",
          "india",
          "India",
          "ind",
          "Indian",
          "indian",
          "INDIA",
          "indien"
        ) ~ "India",
      str_trim(q_nationality_other_raw) %in% c("Iran", "iran") ~ "Iran",
      str_trim(q_nationality_other_raw) %in% c("irak") ~ "Iraq",
      str_trim(q_nationality_other_raw) %in%
        c(
          "Ireland",
          "Republic of Ireland",
          "republic of Ireland",
          "ireland",
          "ire"
        ) ~ "Ireland",
      str_trim(q_nationality_other_raw) %in% c("Izraela", "Israel") ~ "Israel",
      str_trim(q_nationality_other_raw) %in% c("italian") ~ "Italy",
      str_trim(q_nationality_other_raw) %in% c("Jamaica") ~ "Jamaica",
      str_trim(q_nationality_other_raw) %in%
        c("Japan", "japan", "Japanese") ~ "Japan",
      str_trim(q_nationality_other_raw) %in% c("Kazakstan") ~ "Kazakhstan",
      str_trim(q_nationality_other_raw) %in% c("kenya") ~ "Kenya",
      str_trim(q_nationality_other_raw) %in% c("Korea") ~ "Korea",
      str_trim(q_nationality_other_raw) %in% c("Latvija") ~ "Latvia",
      str_trim(q_nationality_other_raw) %in%
        c("Lebanon", "Libanon") ~ "Lebanon",
      str_trim(q_nationality_other_raw) %in%
        c("Liechtenstein") ~ "Liechtenstein",
      str_trim(q_nationality_other_raw) %in%
        c(
          "lietuva",
          "LIETUVA",
          "Lietuva",
          "Lithuania"
        ) ~ "Lithuania",
      str_trim(q_nationality_other_raw) %in% c("Madagascar") ~ "Madagascar",
      str_trim(q_nationality_other_raw) %in% c("Malawian") ~ "Malawi",
      str_trim(q_nationality_other_raw) %in%
        c("Malaysia", "malaysia") ~ "Malaysia",
      str_trim(q_nationality_other_raw) %in% c("Malta") ~ "Malta",
      str_trim(q_nationality_other_raw) %in% c("Mauritius") ~ "Mauritius",
      str_trim(q_nationality_other_raw) %in% c("Mexico") ~ "Mexico",
      str_trim(q_nationality_other_raw) %in%
        c(
          "Moldavia",
          "moldavia",
          "Republica Moldova"
        ) ~ "Moldova",
      str_trim(q_nationality_other_raw) %in%
        c("Crna Gora", "Czarnogóra") ~ "Montenegro",
      str_trim(q_nationality_other_raw) %in%
        c(
          "Morocco",
          "maroc",
          "Marokko",
          "marokko",
          "maruecos"
        ) ~ "Morocco",
      str_trim(q_nationality_other_raw) %in% c("Moçambique") ~ "Mozambique",
      str_trim(q_nationality_other_raw) %in% c("namibia") ~ "Namibia",
      str_trim(q_nationality_other_raw) %in%
        c("Nederland", "nl", "nederland") ~ "Netherlands",
      str_trim(q_nationality_other_raw) %in% c("Newzealand") ~ "New Zealand",
      str_trim(q_nationality_other_raw) %in%
        c(
          "Nigeria",
          "Nigerian",
          "nigerian",
          "nigeria",
          "NIGERIA"
        ) ~ "Nigeria",
      str_trim(q_nationality_other_raw) %in%
        c("Makedonija") ~ "North Macedonia",
      str_trim(q_nationality_other_raw) %in%
        c(
          "Norge",
          "NORGE",
          "Norwegia",
          "norge",
          "Norge.",
          "Noruego"
        ) ~ "Norway",
      str_trim(q_nationality_other_raw) %in%
        c("Pakistan", "pakistan") ~ "Pakistan",
      str_trim(q_nationality_other_raw) %in% c("Palestine") ~ "Palestine",
      str_trim(q_nationality_other_raw) %in% c("Perú", "peru") ~ "Peru",
      str_trim(q_nationality_other_raw) %in%
        c(
          "FILIPPIINI",
          "Filippiini",
          "philippines",
          "Philippines",
          "Filippernerne",
          "Filippinerna",
          "filippinerne",
          "filipinsk",
          "philiippines"
        ) ~ "Philippines",
      str_trim(q_nationality_other_raw) %in% c("poland", "Polska") ~ "Poland",
      str_trim(q_nationality_other_raw) %in% c("Portugal") ~ "Portugal",
      str_trim(q_nationality_other_raw) %in%
        c(
          "Romania",
          "Romania+",
          "romina",
          "roman",
          "Romana",
          "Rumenien",
          "romania"
        ) ~ "Romania",
      str_trim(q_nationality_other_raw) %in%
        c(
          "Russland",
          "Rußland",
          "Ryssland",
          "Россия",
          "Русия",
          "Ρωσία",
          "Ρωσσια",
          "ΡΩΣΙΑ",
          "Russia",
          "russia",
          "Venemaa",
          "venemaa",
          "Vene",
          "vene",
          "venäjä",
          "Venäjä",
          "rysska",
          "ryska",
          "Rusland",
          "Krievija",
          "krevija",
          "krievija",
          "Krīveja",
          "Rusija",
          "Rusia"
        ) ~ "Russia",
      str_trim(q_nationality_other_raw) %in%
        c(
          "Serbien",
          "Srbija",
          "Srbsko",
          "Serbisch",
          "Σερβία"
        ) ~ "Serbia",
      str_trim(q_nationality_other_raw) %in% c("Singapore") ~ "Singapore",
      str_trim(q_nationality_other_raw) %in%
        c(
          "slovensko",
          "SLOVENSKO",
          "Slovensko",
          "Slovenská republika"
        ) ~ "Slovakia",
      str_trim(q_nationality_other_raw) %in%
        c("slovenija", "SLOVENIJA") ~ "Slovenia",
      str_trim(q_nationality_other_raw) %in%
        c(
          "South Africa",
          "South African",
          "SOUTH AFRICAN",
          "south africa",
          "south Africa",
          "south african",
          "Zuid Afrika",
          "južna afrika"
        ) ~ "South Africa",
      str_trim(q_nationality_other_raw) %in% c("españa") ~ "Spain",
      str_trim(q_nationality_other_raw) %in% c("suriname") ~ "Suriname",
      str_trim(q_nationality_other_raw) %in% c("sverige", "Sverige") ~ "Sweden",
      str_trim(q_nationality_other_raw) %in%
        c(
          "schweiz",
          "Schweiz",
          "Svájc",
          "Suíça"
        ) ~ "Switzerland",
      str_trim(q_nationality_other_raw) %in%
        c(
          "Syrien",
          "syrien",
          "Syrian",
          "Syria",
          "syrer"
        ) ~ "Syria",
      str_trim(q_nationality_other_raw) %in%
        c("Thailand", "thailand") ~ "Thailand",
      str_trim(q_nationality_other_raw) %in% c("togo") ~ "Togo",
      str_trim(q_nationality_other_raw) %in%
        c("Trinidadian") ~ "Trinidad and Tobago",
      str_trim(q_nationality_other_raw) %in%
        c("Tunisie", "tunisie", "Tunisien") ~ "Tunisia",
      str_trim(q_nationality_other_raw) %in%
        c(
          "turque",
          "Turque",
          "Türkei",
          "turkki",
          "Турция",
          "Turkiet",
          "turkiet",
          "Turkki",
          "Turkey",
          "turkije",
          "Turkije",
          "Tyrkiet",
          "Turcija"
        ) ~ "Turkey",
      str_trim(q_nationality_other_raw) %in%
        c(
          "Ukraine",
          "украина",
          "ukr",
          "Ucrânia",
          "ucraina",
          "ukraine",
          "Украйна",
          "ukraina",
          "Ukraina",
          "oekraine",
          "Ucrania",
          "Ukrainian"
        ) ~ "Ukraine",
      str_trim(q_nationality_other_raw) %in%
        c(
          "England",
          "ENGLAND",
          "English",
          "Scotland",
          "Scottish",
          "Welsh"
        ) ~ "United Kingdom",
      str_trim(q_nationality_other_raw) %in%
        c(
          "Verenigde staten",
          "usa",
          "USA",
          "United States",
          "ΗΠΑ",
          "United States of America",
          "Estados Unidos",
          "EEUU"
        ) ~ "United States",
      str_trim(q_nationality_other_raw) %in%
        c("uruguay", "Uruguay") ~ "Uruguay",
      str_trim(q_nationality_other_raw) %in%
        c(
          "venezuela",
          "Venezuela",
          "VENEZUELA",
          "venezolano",
          "Venezolana",
          "venezuelana"
        ) ~ "Venezuela",
      str_trim(q_nationality_other_raw) %in%
        c("Vietnam", "vietnam") ~ "Vietnam",
      .default = NA_character_
    ),
  )
```

```{r}
#| label: validate-nationality-recode
df_stacked_recoded |>
  select(q_nationality, q_nationality_raw) |>
  filter(is.na(q_nationality) & !is.na(q_nationality_raw)) |>
  distinct(q_nationality_raw)

df_stacked_recoded |>
  select(q_nationality_other, q_nationality_other_raw) |>
  filter(is.na(q_nationality_other) & !is.na(q_nationality_other_raw)) |>
  distinct(q_nationality_other_raw)
```

## Attachement to Pol. Entities 

```{r}
#| label: value-labels-identity5
very_attached_vec <- c(
  "(1) Sehr verbunden",
  "(1) Très attaché(e)",
  "(1) Много привързан",
  "(1) Velmi oddán(a)",
  "(1) Velmi silně",
  "(1) Meget knyttet til",
  "(1) Väga seotud",
  "(1) Erittäin kiintynyt",
  "(1) Very attached",
  "(1) Molto legato",
  "(1) Nagyon kötődik",
  "(1) Πολύ συνδεδεμένος/η",
  "(1) Vrlo privržen",
  # Latvia
  "(1) Ļoti piederīgs(-a)",
  # Lithuania
  "(1) Labai prisirišęs (-usi)",
  # Netherlands
  "(1) Sterk gehecht",
  # Poland
  "(1) Bardzo związany(a)",
  # Portugal
  "(1) Muito ligado(a)",
  # Romania
  "(1) Foarte ataşat(ă)",
  # Slovakia
  "(1) Úzko spätý",
  # Slovenia
  "(1) Zelo navezan",
  "(1) Zelo navezan(a)",
  # Spain
  "(1) Muy unido/a",
  # Sweden
  "(1) Mycket fäst vid"
)
fairly_attached_vec <- c(
  "(2) Ziemlich verbunden",
  "(2) Assez attaché(e)",
  "(2) Donjakъde privrzvan",
  "(2) Prilično privržen",
  "(2) Docela oddán(a)",
  "(2) Spíše silně",
  "(2) Noget knyttet til",
  "(2) Üsna seotud",
  "(2) Melko kiintynyt",
  "(2) Fairly attached",
  "(2) Abbastanza legato",
  "(2) Eléggé kötődik",
  "(2) Αρκετά συνδεδεμένος/η",
  "Nogal gehecht",
  "(2)",
  # Latvia (bare "(2)" already covered above)
  # Lithuania (bare "(2)" already covered)
  # Netherlands
  "(2) Nogal gehecht",
  # Poland
  "(2) Raczej związany(a)",
  # Portugal
  "(2) Ligado(a)",
  # Romania
  "(2) Destul de ataşat(ă)",
  # Slovakia
  "(2) Dosť spätý",
  # Spain
  "(2) Bastante unido/a",
  # Sweden
  "(2) Ganska fäst vid"
)
moderately_attached_vec <- c(
  "(3) Einigermaßen verbunden",
  "(3) Mittelmäßig verbunden",
  "(3) Modérément attaché(e)",
  "(3) Moderat knyttet til",
  "(3) Mõõdukalt seotud",
  "(3) Moderately attached",
  "(3) Moderatamente legato",
  "(3) Közepesen kötődik",
  "(3) Μέτρια συνδεδεμένος/η",
  "Enigszins gehecht",
  "(3)",
  # Netherlands
  "(3) Enigszins gehecht",
  # Poland
  "(3) Umiarkowanie związany(a)",
  # Portugal
  "(3) Moderadamente ligado(a)",
  "(3)Moderadamente ligado(a)",
  # Romania
  "(3) Moderat atașat",
  # Slovakia
  "(3) Mierne spätý",
  # Spain
  "(3) Moderadamente unido/a",
  # Sweden
  "(3) Måttligt fäst vid"
)
not_very_attached_vec <- c(
  "(4) Nicht sehr verbunden",
  "(4) Nicht so verbunden",
  "(4) Pas très attaché(e)",
  "(4) Ne naročito privržen",
  "(4) Nepříliš oddán(a)",
  "(4) Vůbec ne",
  "(4) Ikke særligt knyttet til",
  "(4) Mitte väga seotud",
  "(4) Ette kovin kiintynyt",
  "(4) Not very attached",
  "(4) Non molto legato",
  "(4) Nem nagyon kötődik",
  "(4) Όχι πολύ συνδεδεμένος/η",
  "(4) Не много привързан",
  "Niet erg gehecht",
  "Ikke særligt knyttet til",
  "(4)",
  # Latvia
  "(4) Ne īpaši piederīgs (-a)",
  "Ne īpaši piederīgs (-a)",
  # Lithuania (bare "(4)" already covered)
  # Netherlands
  "(4) Niet erg gehecht",
  # Poland
  "(4) Raczej niezwiązany(a)",
  # Portugal
  "(4) Não muito ligado(a)",
  # Romania
  "(4) Nu prea ataşat(ă)",
  # Slovakia
  "(4) Nie veľmi spätý",
  # Slovenia (bare "(4)" already covered)
  # Spain
  "(4) No muy unido/a",
  # Sweden
  "(4) Inte särskilt fäst vid"
)
not_at_all_attached_vec <- c(
  "(5) Überhaupt nicht verbunden",
  "(5) Pas du tout attaché(e)",
  "(5) Изобщо не съм привързан",
  "(5) Uopće nisam privržen",
  "(5) Vůbec ne oddán(a)",
  "(5) Slet ikke knyttet til",
  "(5) Üldse mitte seotud",
  "(5) Ette lainkaan kiintynyt",
  "(5) Not at all attached",
  "(5) Per niente legato",
  "(5) Egyáltalán nem kötődik",
  "(5) Καθόλου συνδεδεμένος/η",
  "Helemaal niet gehecht",
  "Slet ikke knyttet til",
  # Latvia
  "(5) Vispār nejūtaties piederīgs (-a)",
  "Vispār nejūtaties piederīgs (-a)",
  # Lithuania
  "(5) Visiškai neprisirišęs (-usi)",
  # Netherlands
  "(5) Helemaal niet gehecht",
  # Poland
  "(5) W ogóle niezwiązany(a)",
  # Portugal
  "(5) Nada ligado(a)",
  # Romania
  "(5) Deloc ataşat(ă)",
  # Slovakia
  "(5) Vôbec nie spätý",
  # Slovenia
  "(5) Sploh ne navezan",
  "(5) Sploh ne navezan(a)",
  # Spain
  "(5) Nada unido/a",
  # Sweden
  "(5) Inte alls fäst vid"
)
```

```{r}
#| label: recode-vars-identity5
df_stacked_recoded <- df_stacked_recoded |>
  mutate(
    q_identity_country = case_when(
      q_identity_country_raw %in% very_attached_vec ~ 1L,
      q_identity_country_raw %in% fairly_attached_vec ~ 2L,
      q_identity_country_raw %in% moderately_attached_vec ~ 3L,
      q_identity_country_raw %in% not_very_attached_vec ~ 4L,
      q_identity_country_raw %in% not_at_all_attached_vec ~ 5L,
      .default = NA
    ),
    q_identity_eu = case_when(
      q_identity_eu_raw %in% very_attached_vec ~ 1L,
      q_identity_eu_raw %in% fairly_attached_vec ~ 2L,
      q_identity_eu_raw %in% moderately_attached_vec ~ 3L,
      q_identity_eu_raw %in% not_very_attached_vec ~ 4L,
      q_identity_eu_raw %in% not_at_all_attached_vec ~ 5L,
      .default = NA
    ),
    q_identity_europe = case_when(
      q_identity_europe_raw %in% very_attached_vec ~ 1L,
      q_identity_europe_raw %in% fairly_attached_vec ~ 2L,
      q_identity_europe_raw %in% moderately_attached_vec ~ 3L,
      q_identity_europe_raw %in% not_very_attached_vec ~ 4L,
      q_identity_europe_raw %in% not_at_all_attached_vec ~ 5L,
      .default = NA
    )
  )
```

```{r}
#| label: validate-identity5-vars
df_stacked_recoded |>
  select(q_identity_country, q_identity_country_raw) |>
  filter(is.na(q_identity_country) & !is.na(q_identity_country_raw)) |>
  distinct(q_identity_country_raw)

df_stacked_recoded |>
  select(q_identity_eu, q_identity_eu_raw) |>
  filter(is.na(q_identity_eu) & !is.na(q_identity_eu_raw)) |>
  distinct(q_identity_eu_raw)

df_stacked_recoded |>
  select(q_identity_europe, q_identity_europe_raw) |>
  filter(is.na(q_identity_europe) & !is.na(q_identity_europe_raw)) |>
  distinct(q_identity_europe_raw)
```

## Populist Attitude Items

```{r}
#| label: 7scale-agree-values
# 1
strongly_disagree_vec <- c(
  "(1) Stimme überhaupt nicht zu", # de
  "(1) Sterk mee oneens", # nl
  "(1) Напълно несъгласен/на",
  "1)\tPas du tout d'accord", # fr
  "(1) Pas du tout d'accord", # fr (alt)
  "(1) Pas du tout d’accord",
  "(1)\tPas du tout d’accord",
  "(1) Rozhodně nesouhlasím", # cs
  "(1) Meget uenig", # da
  "(1)\tMeget uenig", # da (tab)
  "(1) Ei nõustu üldse", # et
  "(1)\tEi nõustu üldse", # et (tab)
  "(1) Täysin eri mieltä", # fi
  "(1) Strongly disagree", # en
  "(1) Διαφωνώ απόλυτα", # el
  "(1) Egyáltalán nem értek egyet", # hu
  "(1)\tEgyáltalán nem értek egyet", # hu (tab)
  "(1) Pilnībā nepiekrītu", # lv
  "(1)\tPilnībā nepiekrītu", # lv (tab)
  "(1) Visiškai nesutinku", # lt
  "(1) Zupełnie się nie zgadzam", # pl
  "(1)\tZupełnie się nie zgadzam", # pl (tab)
  "(1) Discordo totalmente", # pt
  "(1) Dezacord puternic", # ro
  "(1) Vôbec nesúhlasím", # sk
  "(1)\tVôbec nesúhlasím", # sk (tab)
  "(1) Močno se ne strinjam", # sl
  "(1) Totalmente en desacuerdo", # es
  "(1) Instämmer inte alls", # sv
  "(1)\tInstämmer inte alls", # sv (tab)
  "(1) Fortemente in disaccordo", # it
  "(1) Uopće se ne slažem" # hr
)
# 2
disagree_vec <- c(
  "(2) Stimme  nicht zu", # de (double space)
  "(2) Stimme nicht zu", # de
  "(2) Mee oneens", # nl
  "2)\tPas d'accord", # fr (tab)
  "(2) Pas d'accord", # fr (alt)
  "(2) Pas d’accord",
  "(2) Несъгласен/на",
  "(2) Nesouhlasím", # cs
  "(2) Uenig", # da
  "(2)\tUenig", # da (tab)
  "(2) Ei nõustu", # et
  "(2)\tEi nõustu", # et (tab)
  "(2) Eri mieltä", # fi
  "(2) Disagree", # en
  "(2) Διαφωνώ", # el
  "(2) Nem értek egyet", # hu
  "(2)\tNem értek egyet", # hu (tab)
  "(2) Nepiekrītu", # lv
  "(2)\tNepiekrītu", # lv (tab)
  "(2) Nesutinku", # lt
  "(2) Nie zgadzam się", # pl
  "(2)\tNie zgadzam się", # pl (tab)
  "(2) Discordo", # pt
  "(2) Dezacord", # ro
  "(2) Nesúhlasím", # sk
  "(2)\tNesúhlasím", # sk (tab)
  "(2) Ne strinjam se", # sl
  "(2) En desacuerdo", # es
  "(2) Instämmer inte", # sv
  "(2)\tInstämmer inte", # sv (tab)
  "(2) In disaccordo", # it
  "(2) Ne slažem se" # hr
)
# 3
somewhat_disagree_vec <- c(
  "(3) Stimme eher nicht zu", # de
  "(3) Enigszins mee oneens", # nl
  "3)\tPlutôt pas d'accord", # fr (tab)
  "(3) Plutôt pas d'accord", # fr (alt)
  "(3) Plutôt pas d’accord",
  "(3) Донякъде несъгласен/на",
  "(3) Донякъде несъгласен/на",
  "(3) Spíše nesouhlasím", # cs
  "(3) Ret uenig", # da
  "(3)\tRet uenig", # da (tab)
  "(3) Mõneti ei nõustu", # et
  "(3)\tMõneti ei nõustu", # et (tab)
  "(3) Jossain määrin eri mieltä", # fi
  "(3) Somewhat disagree", # en
  "(3) Διαφωνώ σε κάποιο βαθμό", # el
  "(3) Inkább nem értek egyet", # hu
  "(3)\tInkább nem értek egyet", # hu (tab)
  "(3) Zināmā mērā nepiekrītu", # lv
  "(3)\tZināmā mērā nepiekrītu", # lv (tab)
  "(3) Veikiau nesutinku", # lt
  "(3) Częściowo się nie zgadzam", # pl
  "(3)\tCzęściowo się nie zgadzam", # pl (tab)
  "(3) Discordo um pouco", # pt
  "(3) Dezacord parțial", # ro
  "(3) Do určitej miery nesúhlasím", # sk
  "(3)\tDo určitej miery nesúhlasím", # sk (tab)
  "(3) Delno se ne strinjam", # sl
  "(3) Algo en desacuerdo", # es
  "(3) Instämmer inte i viss utsträckning", # sv
  "(3)\tInstämmer inte i viss utsträckning", # sv (tab)
  "(3) Abbastanza in disaccordo", # it
  "(3) Djelomično se ne slažem" # hr
)
# 4
neither_nor_vec <- c(
  "(4) Stimme weder zu noch nicht zu", # de
  "(4) Niet mee eens of oneens", # nl
  "4)\tNi d'accord, ni pas d'accord", # fr (tab)
  "(4) Ni d'accord, ni pas d'accord", # fr (alt)
  "(4) Ni d’accord, ni pas d’accord",
  "(4) Mám neutrální názor", # cs
  "(4) Hverken enig eller uenig", # da
  "(4)\tHverken enig eller uenig", # da (tab)
  "(4) Ei nõus ega vastu", # et
  "(4)\tEi nõus ega vastu", # et (tab)
  "(4) Ei samaa eikä eri mieltä", # fi
  "(4) Neither agree nor disagree", # en
  "(4) Neither agree or disagree",
  "(4) Нито съгласен/на, нито несъгласен/на",
  "(4) Ούτε συμφωνώ ούτε διαφωνώ", # el
  "(4) Nem értek egyet, de el sem utasítom", # hu
  "(4)\tNem értek egyet, de el sem utasítom", # hu (tab)
  "(4) Nedz piekrītu, nedz nepiekrītu", # lv
  "(4)\tNedz piekrītu, nedz nepiekrītu", # lv (tab)
  "(4) Nei sutinku, nei nesutinku", # lt
  "(4) Mam neutralny stosunek", # pl
  "(4)\tMam neutralny stosunek", # pl (tab)
  "(4) Ani się zgadzam, ani się nie zgadzam", # pl (alt)
  "(4) Nem concordo nem discordo", # pt
  "(4) Neutru", # ro
  "(4) Nemám na to názor", # sk
  "(4) Ani súhlasím, ani nesúhlasím", # sk (alt)
  "(4) Niti se strinjam niti se ne strinjam", # sl
  "(4) Ni de acuerdo ni en desacuerdo", # es
  "(4) Varken instämmer eller inte instämmer", # sv
  "(4)\tVarken instämmer eller inte instämmer", # sv (tab)
  "(4) Né in accordo né in disaccordo", # it
  "(4) Niti se slažem niti ne slažem", # hr
  "(4) Niti se slažem niti ne  slažem" # hr (double space)
  "(4)  Нито съгласен/на, нито несъгласен/на"
)
# 5
somewhat_agree_vec <- c(
  "(5) Stimme eher zu", # de
  "(5) Enigszins mee eens", # nl
  "5)\tPlutôt d'accord", # fr (tab)
  "(5) Plutôt d'accord", # fr (alt)
  "(5) Spíše souhlasím", # cs
  "(5) Донякъде съгласен/на",
  "(5) Ret enig", # da
  "(5)\tRet enig", # da (tab)
  "(5) Mõneti nõustun", # et
  "(5)\tMõneti nõustun", # et (tab)
  "(5) Jossain määrin samaa mieltä", # fi
  "(5) Somewhat agree", # en
  "(5) Συμφωνώ σε κάποιο βαθμό", # el
  "(5) Valamelyest egyetértek", # hu
  "(5)\tValamelyest egyetértek", # hu (tab)
  "(5) Zināmā mērā piekrītu", # lv
  "(5)\tZināmā mērā piekrītu", # lv (tab)
  "(5) Veikiau sutinku", # lt
  "(5) Częściowo się zgadzam", # pl
  "(5)\tCzęściowo się zgadzam", # pl (tab)
  "(5) Concordo um pouco", # pt
  "(5) Acord parțial", # ro
  "(5) Do určitej miery súhlasím", # sk
  "(5)\tDo určitej miery súhlasím", # sk (tab)
  "(5) Delno se strinjam", # sl
  "(5) Algo de acuerdo", # es
  "(5) Instämmer i viss utsträckning", # sv
  "(5)\tInstämmer i viss utsträckning", # sv (tab)
  "(5) Abbastanza d'accordo", # it
  "(5) Djelomično se slažem" # hr
)
# 6
agree_vec <- c(
  "(6) Stimme zu", # de
  "(6) Mee eens", # nl
  "6)\tD'accord", # fr (tab)
  "(6) D'accord", # fr (alt)
  "(6) D’accord",
  "(6) Съгласен/на",
  "(6) Souhlasím", # cs
  "(6) Enig", # da
  "(6)\tEnig", # da (tab)
  "(6) Nõustun", # et
  "(6)\tNõustun", # et (tab)
  "(6) Samaa mieltä", # fi
  "(6) Agree", # en
  "(6) Συμφωνώ", # el
  "(6) Egyetértek", # hu
  "(6)\tEgyetértek", # hu (tab)
  "(6) Piekrītu", # lv
  "(6)\tPiekrītu", # lv (tab)
  "(6) Sutinku", # lt
  "(6) Zgadzam się", # pl
  "(6)\tZgadzam się", # pl (tab)
  "(6) Concordo", # pt
  "(6) Acord", # ro
  "(6) Súhlasím", # sk
  "(6)\tSúhlasím", # sk (tab)
  "(6) Strinjam se", # sl
  "(6) De acuerdo", # es
  "(6) Instämmer", # sv
  "(6)\tInstämmer", # sv (tab)
  "(6) D'accordo", # it
  "(6) D’accordo",
  "(6) Slažem se" # hr
)
# 7
strongly_agree_vec <- c(
  "(7) Stimme vollkommen zu", # de
  "(7) Sterk mee eens", # nl
  "7)\tTout à fait d'accord", # fr (tab)
  "(7) Tout à fait d'accord", # fr (alt)
  "(7) Tout à fait d’accord",
  "(7) Rozhodně souhlasím", # cs
  "(7) Meget enig", # da
  "(7)\tMeget enig", # da (tab)
  "(7) Nõustun täiesti", # et
  "(7)\tNõustun täiesti", # et (tab)
  "(7) Täysin samaa mieltä", # fi
  "(7) Strongly agree", # en
  "(7) Напълно съгласен/на",
  "(7) Συμφωνώ σε μεγάλο βαθμό", # el
  "(7) Teljesen egyetértek", # hu
  "(7)\tTeljesen egyetértek", # hu (tab)
  "(7) Pilnībā piekrītu", # lv
  "(7)\tPilnībā piekrītu", # lv (tab)
  "(7) Visiškai sutinku", # lt
  "(7) W pełni się zgadzam", # pl
  "(7)\tW pełni się zgadzam", # pl (tab)
  "(7) Concordo totalmente", # pt
  "(7) Acord puternic", # ro
  "(7) Úplne súhlasím", # sk
  "(7)\tÚplne súhlasím", # sk (tab)
  "(7) Močno se strinjam", # sl
  "(7) Totalmente de acuerdo", # es
  "(7) Instämmer starkt", # sv
  "(7)\tInstämmer starkt", # sv (tab)
  "(7) Molto d'accordo", # it
  "(7) Molto d’accordo",
  "(7) U potpunosti se slažem" # hr
)
```

```{r}
#| label: pop-recoding
df_stacked_recoded <- df_stacked_recoded |>
  mutate(
    q_pop_will = case_when(
      q_pop_will_raw %in% strongly_disagree_vec ~ 1,
      q_pop_will_raw %in% disagree_vec ~ 2,
      q_pop_will_raw %in% somewhat_disagree_vec ~ 3,
      q_pop_will_raw %in% neither_nor_vec ~ 4,
      q_pop_will_raw %in% somewhat_agree_vec ~ 5,
      q_pop_will_raw %in% agree_vec ~ 6,
      q_pop_will_raw %in% strongly_agree_vec ~ 7,
      .default = NA
    ),
    q_pop_people = case_when(
      q_pop_people_raw %in% strongly_disagree_vec ~ 1,
      q_pop_people_raw %in% disagree_vec ~ 2,
      q_pop_people_raw %in% somewhat_disagree_vec ~ 3,
      q_pop_people_raw %in% neither_nor_vec ~ 4,
      q_pop_people_raw %in% somewhat_agree_vec ~ 5,
      q_pop_people_raw %in% agree_vec ~ 6,
      q_pop_people_raw %in% strongly_agree_vec ~ 7,
      .default = NA
    ),
    q_pop_citizen = case_when(
      q_pop_citizen_raw %in% strongly_disagree_vec ~ 1,
      q_pop_citizen_raw %in% disagree_vec ~ 2,
      q_pop_citizen_raw %in% somewhat_disagree_vec ~ 3,
      q_pop_citizen_raw %in% neither_nor_vec ~ 4,
      q_pop_citizen_raw %in% somewhat_agree_vec ~ 5,
      q_pop_citizen_raw %in% agree_vec ~ 6,
      q_pop_citizen_raw %in% strongly_agree_vec ~ 7,
      .default = NA
    ),
    q_pop_reps = case_when(
      q_pop_reps_raw %in% strongly_disagree_vec ~ 1,
      q_pop_reps_raw %in% disagree_vec ~ 2,
      q_pop_reps_raw %in% somewhat_disagree_vec ~ 3,
      q_pop_reps_raw %in% neither_nor_vec ~ 4,
      q_pop_reps_raw %in% somewhat_agree_vec ~ 5,
      q_pop_reps_raw %in% agree_vec ~ 6,
      q_pop_reps_raw %in% strongly_agree_vec ~ 7,
      .default = NA
    ),
    q_pop_goodevil = case_when(
      q_pop_goodevil_raw %in% strongly_disagree_vec ~ 1,
      q_pop_goodevil_raw %in% disagree_vec ~ 2,
      q_pop_goodevil_raw %in% somewhat_disagree_vec ~ 3,
      q_pop_goodevil_raw %in% neither_nor_vec ~ 4,
      q_pop_goodevil_raw %in% somewhat_agree_vec ~ 5,
      q_pop_goodevil_raw %in% agree_vec ~ 6,
      q_pop_goodevil_raw %in% strongly_agree_vec ~ 7,
      .default = NA
    ),
    q_pop_compromise = case_when(
      q_pop_compromise_raw %in% strongly_disagree_vec ~ 1,
      q_pop_compromise_raw %in% disagree_vec ~ 2,
      q_pop_compromise_raw %in% somewhat_disagree_vec ~ 3,
      q_pop_compromise_raw %in% neither_nor_vec ~ 4,
      q_pop_compromise_raw %in% somewhat_agree_vec ~ 5,
      q_pop_compromise_raw %in% agree_vec ~ 6,
      q_pop_compromise_raw %in% strongly_agree_vec ~ 7,
      .default = NA
    ),
  )
```

```{r}
#| label: validate-pop-recode
df_stacked_recoded |>
  select(q_pop_will, q_pop_will_raw) |>
  filter(is.na(q_pop_will) & !is.na(q_pop_will_raw)) |>
  distinct(q_pop_will_raw)

df_stacked_recoded |>
  select(q_pop_people, q_pop_people_raw) |>
  filter(is.na(q_pop_people) & !is.na(q_pop_people_raw)) |>
  distinct(q_pop_people_raw)

df_stacked_recoded |>
  select(q_pop_citizen, q_pop_citizen_raw) |>
  filter(is.na(q_pop_citizen) & !is.na(q_pop_citizen_raw)) |>
  distinct(q_pop_citizen_raw)

df_stacked_recoded |>
  select(q_pop_reps, q_pop_reps_raw) |>
  filter(is.na(q_pop_reps) & !is.na(q_pop_reps_raw)) |>
  distinct(q_pop_reps_raw)

df_stacked_recoded |>
  select(q_pop_goodevil, q_pop_goodevil_raw) |>
  filter(is.na(q_pop_goodevil) & !is.na(q_pop_goodevil_raw)) |>
  distinct(q_pop_goodevil_raw)

df_stacked_recoded |>
  select(q_pop_compromise, q_pop_compromise_raw) |>
  filter(is.na(q_pop_compromise) & !is.na(q_pop_compromise_raw)) |>
  distinct(q_pop_compromise_raw)
```

## EU Attitude Variables

```{r}
#| label: eu-attitude-values
# uses 7 scale agree/disagree answers, so existing vectors can be used
```

```{r}
#| label: eu-attitude-recoding
#| eval: false
df_stacked_recoded <- df_stacked_recoded |>
  mutate(
    q_eu_longterm = case_when(
      q_eu_longterm_raw %in% strongly_disagree_vec ~ 1L,
      q_eu_longterm_raw %in% disagree_vec ~ 2L,
      q_eu_longterm_raw %in% somewhat_disagree_vec ~ 3L,
      q_eu_longterm_raw %in% neither_nor_vec ~ 4L,
      q_eu_longterm_raw %in% somewhat_agree_vec ~ 5L,
      q_eu_longterm_raw %in% agree_vec ~ 6L,
      q_eu_longterm_raw %in% strongly_agree_vec ~ 7L,
      .default = NA
    ),
    q_eu_responsive = case_when(
      q_eu_responsive_raw %in% strongly_disagree_vec ~ 1L,
      q_eu_responsive_raw %in% disagree_vec ~ 2L,
      q_eu_responsive_raw %in% somewhat_disagree_vec ~ 3L,
      q_eu_responsive_raw %in% neither_nor_vec ~ 4L,
      q_eu_responsive_raw %in% somewhat_agree_vec ~ 5L,
      q_eu_responsive_raw %in% agree_vec ~ 6L,
      q_eu_responsive_raw %in% strongly_agree_vec ~ 7L,
      .default = NA
    ),
    q_eu_efficacy_understand = case_when(
      q_eu_efficacy_understand_raw %in% strongly_disagree_vec ~ 1L,
      q_eu_efficacy_understand_raw %in% disagree_vec ~ 2L,
      q_eu_efficacy_understand_raw %in% somewhat_disagree_vec ~ 3L,
      q_eu_efficacy_understand_raw %in% neither_nor_vec ~ 4L,
      q_eu_efficacy_understand_raw %in% somewhat_agree_vec ~ 5L,
      q_eu_efficacy_understand_raw %in% agree_vec ~ 6L,
      q_eu_efficacy_understand_raw %in% strongly_agree_vec ~ 7L,
      .default = NA
    ),
    q_eu_efficacy_care = case_when(
      q_eu_efficacy_care_raw %in% strongly_disagree_vec ~ 1L,
      q_eu_efficacy_care_raw %in% disagree_vec ~ 2L,
      q_eu_efficacy_care_raw %in% somewhat_disagree_vec ~ 3L,
      q_eu_efficacy_care_raw %in% neither_nor_vec ~ 4L,
      q_eu_efficacy_care_raw %in% somewhat_agree_vec ~ 5L,
      q_eu_efficacy_care_raw %in% agree_vec ~ 6L,
      q_eu_efficacy_care_raw %in% strongly_agree_vec ~ 7L,
      .default = NA
    ),
    q_eu_efficacy_nosay = case_when(
      q_eu_efficacy_nosay_raw %in% strongly_disagree_vec ~ 1L,
      q_eu_efficacy_nosay_raw %in% disagree_vec ~ 2L,
      q_eu_efficacy_nosay_raw %in% somewhat_disagree_vec ~ 3L,
      q_eu_efficacy_nosay_raw %in% neither_nor_vec ~ 4L,
      q_eu_efficacy_nosay_raw %in% somewhat_agree_vec ~ 5L,
      q_eu_efficacy_nosay_raw %in% agree_vec ~ 6L,
      q_eu_efficacy_nosay_raw %in% strongly_agree_vec ~ 7L,
      .default = NA
    ),
    q_eu_abolish = case_when(
      q_eu_abolish_raw %in% strongly_disagree_vec ~ 1L,
      q_eu_abolish_raw %in% disagree_vec ~ 2L,
      q_eu_abolish_raw %in% somewhat_disagree_vec ~ 3L,
      q_eu_abolish_raw %in% neither_nor_vec ~ 4L,
      q_eu_abolish_raw %in% somewhat_agree_vec ~ 5L,
      q_eu_abolish_raw %in% agree_vec ~ 6L,
      q_eu_abolish_raw %in% strongly_agree_vec ~ 7L,
      .default = NA
    ),
    q_eu_satisfaction = case_when(
      q_eu_satisfaction_raw %in% strongly_disagree_vec ~ 1L,
      q_eu_satisfaction_raw %in% disagree_vec ~ 2L,
      q_eu_satisfaction_raw %in% somewhat_disagree_vec ~ 3L,
      q_eu_satisfaction_raw %in% neither_nor_vec ~ 4L,
      q_eu_satisfaction_raw %in% somewhat_agree_vec ~ 5L,
      q_eu_satisfaction_raw %in% agree_vec ~ 6L,
      q_eu_satisfaction_raw %in% strongly_agree_vec ~ 7L,
      .default = NA
    )
  )
```

How to test: print recoded variables NA values against non-NA raw variables

```{r}
#| label: validate-euattitude-recode
df_stacked_recoded |>
  select(q_eu_satisfaction, q_eu_satisfaction_raw) |>
  filter(is.na(q_eu_satisfaction) & !is.na(q_eu_satisfaction_raw)) |>
  distinct(q_eu_satisfaction_raw)
```

## Conjoint Behavioral Game Variables

```{r}
#| label: value-labels-cj-rel
# CJ Religion Attribute --------------------------------------------------------
cj_muslim_vec <- c(
  "Muslimisch",
  "Moslim",
  "Musulman",
  "мюсюлманин",
  "Musliman",
  "Muslim",
  "Muslim",
  "Moslim",
  "Moslem",
  "Muslimi",
  "Musulman",
  "Muslimisch",
  "Μουσουλμάνος",
  "Muzulmán",
  "Musulmana",
  "musulmanis",
  "Musulmanis", #Lv
  "Musulmonas",
  "Muzułmańskie",
  "Muçulmano",
  "Musulman",
  "Moslimské",
  "Muslimanska",
  "Musulmana",
  "Muslim",
  "Muslim"
)

cj_protestant_vec <- c(
  "Protestantisch",
  "Protestant",
  "Protestant",
  "Protestant",
  "протестант",
  "Protestant",
  "Protestant",
  "Protestant",
  "Protestant",
  "Protestant",
  "Protestantti",
  "Protestant",
  "Protestantisch",
  "Διαμαρτυρόμενος",
  "Protestáns",
  "Protestante",
  "protestants",
  "Protestants", #lv
  "Protestantas",
  "Protestanckie",
  "Protestante",
  "Protestant",
  "Protestantské",
  "Protestantska",
  "Protestante",
  "Protestant"
)

cj_catholic_vec <- c(
  "Katholisch",
  "Catholic",
  "Katholiek",
  "Catholique",
  "католик",
  "Katolik",
  "Katolík",
  "Katolik",
  "Katholiek",
  "Katoliiklane",
  "Katolilainen",
  "Catholique",
  "Katholisch",
  "Καθολικός",
  "Katolikus",
  "Cattolica",
  "katolis",
  "Katolis", #lv
  "Katalikas",
  "Katolickie",
  "Católico",
  "Catolic",
  "Katolícke",
  "Katoliška",
  "Católica",
  "Katolik"
)

cj_nonreli_vec <- c(
  "Keine Religion",
  "No Religion",
  "Geen religie",
  "Sans religion",
  "без религия",
  "Nije vjernik",
  "Bez vyznání",
  "Ikke religiøs",
  "Geen religie",
  "Ei ole usklik",
  "Ei uskontoa",
  "Sans religion",
  "Keine Religion",
  "Χωρίς θρησκεία",
  "Nincs vallása",
  "Nessuna religione",
  "bez reliģiskās piederības",
  "Bez reliģiskās piederības",
  "Nėra religijos",
  "Nie wierzący(-a)",
  "Sem religião",
  "Nicio religie",
  "Žiadne vierovyznanie",
  "Brez religije",
  "Sin religión",
  "Ingen religion"
)
```

```{r}
#| label: recode-vars-cj-games
# to look up country specific value codings, copy and run
# purrr::keep(groups_named[["Austria"]], ~ any(grepl("q_identity", .x)))
# in the R console

# character variables: comment out
df_stacked_recoded <- df_stacked_recoded |>
  mutate(
    # cj_attr_order = ,
    cj_dict_instr_firstclick = as.integer(cj_dict_instr_firstclick),
    cj_dict_instr_lastclick = as.integer(cj_dict_instr_lastclick),
    cj_dict_instr_pagesubmit = as.integer(cj_dict_instr_pagesubmit),
    cj_dict_instr_clickcount = as.integer(cj_dict_instr_clickcount),
    cj_dict1_pl1 = as.integer(cj_dict1_pl1),
    cj_dict1_pl2 = as.integer(cj_dict1_pl2),
    cj_dict1_firstclick = as.integer(cj_dict1_firstclick),
    cj_dict1_lastclick = as.integer(cj_dict1_lastclick),
    cj_dict1_pagesubmit = as.integer(cj_dict1_pagesubmit),
    cj_dict1_clickcount = as.integer(cj_dict1_clickcount),
    # cj_dict1_nat = ,
    # cj_dict1_party = ,
    # cj_dict1_eupos = ,
    cj_dict1_rel = case_when(
      cj_dict1_rel_raw %in% cj_muslim_vec ~ "muslim",
      cj_dict1_rel_raw %in% cj_protestant_vec ~ "protestant",
      cj_dict1_rel_raw %in% cj_catholic_vec ~ "catholic",
      cj_dict1_rel_raw %in% cj_nonreli_vec ~ "non-religious",
    ),
    # cj_dict1_age = ,
    # cj_dict1_sex = ,
    # cj_dict1_class = ,
    cj_dict2_pl1 = as.integer(cj_dict2_pl1),
    cj_dict2_pl2 = as.integer(cj_dict2_pl2),
    cj_dict2_firstclick = as.integer(cj_dict2_firstclick),
    cj_dict2_lastclick = as.integer(cj_dict2_lastclick),
    cj_dict2_pagesubmit = as.integer(cj_dict2_pagesubmit),
    cj_dict2_clickcount = as.integer(cj_dict2_clickcount),
    # cj_dict2_nat = ,
    # cj_dict2_party = ,
    # cj_dict2_eupos = ,
    cj_dict2_rel = case_when(
      cj_dict2_rel_raw %in% cj_muslim_vec ~ "muslim",
      cj_dict2_rel_raw %in% cj_protestant_vec ~ "protestant",
      cj_dict2_rel_raw %in% cj_catholic_vec ~ "catholic",
      cj_dict2_rel_raw %in% cj_nonreli_vec ~ "non-religious",
    ),
    # cj_dict2_age = ,
    # cj_dict2_sex = ,
    # cj_dict2_class = ,
    cj_dict3_pl1 = as.integer(cj_dict3_pl1),
    cj_dict3_pl2 = as.integer(cj_dict3_pl2),
    cj_dict3_firstclick = as.integer(cj_dict3_firstclick),
    cj_dict3_lastclick = as.integer(cj_dict3_lastclick),
    cj_dict3_pagesubmit = as.integer(cj_dict3_pagesubmit),
    cj_dict3_clickcount = as.integer(cj_dict3_clickcount),
    # cj_dict3_nat = ,
    # cj_dict3_party = ,
    # cj_dict3_eupos = ,
    cj_dict3_rel = case_when(
      cj_dict3_rel_raw %in% cj_muslim_vec ~ "muslim",
      cj_dict3_rel_raw %in% cj_protestant_vec ~ "protestant",
      cj_dict3_rel_raw %in% cj_catholic_vec ~ "catholic",
      cj_dict3_rel_raw %in% cj_nonreli_vec ~ "non-religious",
    ),
    # cj_dict3_age = ,
    # cj_dict3_sex = ,
    # cj_dict3_class = ,
    cj_trust_instr_firstclick = as.integer(cj_trust_instr_firstclick),
    cj_trust_instr_lastclick = as.integer(cj_trust_instr_lastclick),
    cj_trust_instr_pagesubmit = as.integer(cj_trust_instr_pagesubmit),
    cj_trust_instr_clickcount = as.integer(cj_trust_instr_clickcount),
    cj_trust1_pl1 = as.integer(cj_trust1_pl1),
    cj_trust1_pl2 = as.integer(cj_trust1_pl2),
    cj_trust1_firstclick = as.integer(cj_trust1_firstclick),
    cj_trust1_lastclick = as.integer(cj_trust1_lastclick),
    cj_trust1_pagesubmit = as.integer(cj_trust1_pagesubmit),
    cj_trust1_clickcount = as.integer(cj_trust1_clickcount),
    # cj_trust1_nat = ,
    # cj_trust1_party = ,
    # cj_trust1_eupos = ,
    cj_trust1_rel = case_when(
      cj_trust1_rel_raw %in% cj_muslim_vec ~ "muslim",
      cj_trust1_rel_raw %in% cj_protestant_vec ~ "protestant",
      cj_trust1_rel_raw %in% cj_catholic_vec ~ "catholic",
      cj_trust1_rel_raw %in% cj_nonreli_vec ~ "non-religious",
    ),
    # cj_trust1_age = ,
    # cj_trust1_sex = ,
    # cj_trust1_class = ,
    cj_trust2_pl1 = as.integer(cj_trust2_pl1),
    cj_trust2_pl2 = as.integer(cj_trust2_pl2),
    cj_trust2_firstclick = as.integer(cj_trust2_firstclick),
    cj_trust2_lastclick = as.integer(cj_trust2_lastclick),
    cj_trust2_pagesubmit = as.integer(cj_trust2_pagesubmit),
    cj_trust2_clickcount = as.integer(cj_trust2_clickcount),
    # cj_trust2_nat = ,
    # cj_trust2_party = ,
    # cj_trust2_eupos = ,
    cj_trust2_rel = case_when(
      cj_trust2_rel_raw %in% cj_muslim_vec ~ "muslim",
      cj_trust2_rel_raw %in% cj_protestant_vec ~ "protestant",
      cj_trust2_rel_raw %in% cj_catholic_vec ~ "catholic",
      cj_trust2_rel_raw %in% cj_nonreli_vec ~ "non-religious",
    ),
    # cj_trust2_age = ,
    # cj_trust2_sex = ,
    # cj_trust2_class = ,
    cj_trust3_pl1 = as.integer(cj_trust3_pl1),
    cj_trust3_pl2 = as.integer(cj_trust3_pl2),
    cj_trust3_firstclick = as.integer(cj_trust3_firstclick),
    cj_trust3_lastclick = as.integer(cj_trust3_lastclick),
    cj_trust3_pagesubmit = as.integer(cj_trust3_pagesubmit),
    cj_trust3_clickcount = as.integer(cj_trust3_clickcount),
    # cj_trust3_nat = ,
    # cj_trust3_party = ,
    # cj_trust3_eupos = ,
    cj_trust3_rel = case_when(
      cj_trust3_rel_raw %in% cj_muslim_vec ~ "muslim",
      cj_trust3_rel_raw %in% cj_protestant_vec ~ "protestant",
      cj_trust3_rel_raw %in% cj_catholic_vec ~ "catholic",
      cj_trust3_rel_raw %in% cj_nonreli_vec ~ "non-religious",
    ),
    # cj_trust3_age = ,
    # cj_trust3_sex = ,
    # cj_trust3_class = ,
    # q_religion_other = ,
    # q_thermo_1 = ,
    # q_thermo_2 = ,
    # q_thermo_3 = ,
    # q_thermo_4 = ,
    # q_thermo_5 = ,
    # q_thermo_6 = ,
    # prime_cjeu_condition = ,
    # prime_cjeu_text = ,
    # cj_rand_issue_order = ,
    # cj_rand_party_a = ,
    # cj_rand_party_b = ,
    # cj_rand_party_c = ,
    # cj_rand_party_d = ,
    # cj_rand_party_e = ,
    # cj_rand_party_f = ,
    # q_policy_comp_val_market = ,
    # q_policy_comp_val_security = ,
    # q_policy_comp_val_immigration = ,
    # q_policy_comp_val_environment = ,
    # q_policy_comp_val_trade = ,
    # q_policy_comp_val_agriculture = ,
    # q_policy_comp_eu_natgov = ,
    # q_eu_trust_val = ,
    # q_policy_comp_pos_market = ,
    # q_policy_comp_pos_security = ,
    # q_policy_comp_pos_immigration = ,
    # q_policy_comp_pos_environment = ,
    # q_policy_comp_pos_trade = ,
    # q_policy_comp_pos_agriculture = ,
    # cj_task1_firstclick = ,
    # cj_task1_lastclick = ,
    # cj_task1_pagesubmit = ,
    # cj_task1_clickcount = ,
    # cj_task1_choice = ,
    # cj_task1_eval_a = ,
    # cj_task1_eval_b = ,
    # cj_task2_firstclick = ,
    # cj_task2_lastclick = ,
    # cj_task2_pagesubmit = ,
    # cj_task2_clickcount = ,
    # cj_task2_choice = ,
    # cj_task2_eval_c = ,
    # cj_task2_eval_d = ,
    # cj_task3_firstclick = ,
    # cj_task3_lastclick = ,
    # cj_task3_pagesubmit = ,
    # cj_task3_clickcount = ,
    # cj_task3_choice = ,
    # cj_task3_eval_e = ,
    # cj_task3_eval_f = ,
    # q_attn_check = ,
    # q_attn_check_text = ,
    # q_pop_elite = ,
    # q_eu_vote_2014 = ,
    # q_eu_vote_2014_text = ,
    # q_eu_longterm_gre = ,
    # q_eu_responsive_gre = ,
    # q_resp_verif = ,
    # q_party_id_text = ,
    # q_party_closeness = ,
    # q_gridlock_manip = ,
    # prime_compliance_firstclick = ,
    # prime_compliance_lastclick = ,
    # prime_compliance_pagesubmit = ,
    # prime_compliance_clickcount = ,
    # q_approval_natgov = ,
    # q_approval_eu = ,
    # q_compliance_verif = ,
    # q_eu_informed_ecb = ,
    # q_eu_trust_ecb = ,
    # q_natcourt_informed = ,
    # prime_court_firstclick = ,
    # prime_court_lastclick = ,
    # prime_court_pagesubmit = ,
    # prime_court_clickcount = ,
    # q_natcourt_1 = ,
    # q_natcourt_2 = ,
    # q_court_pos = ,
    # q_eu_benefit_nat = ,
    # q_eu_pos_personal = ,
    # q_elec_issue_imp_pos = ,
    # q_elec_issue_imp_val = ,
    # q_pol_market = ,
    # q_pol_security = ,
    # q_pol_immigration = ,
    # q_pol_environment = ,
    # q_pol_trade = ,
    # q_pol_agriculture = ,
    # q_lr_gov_nat = ,
    # q_lr_court_nat = ,
    # q_lr_ecb = ,
    # q_eff_internal = ,
    # q_eff_external_resp = ,
    # q_eff_external_nosay = ,
    # q_vote_eu_2014 = ,
    # q_vote_eu_2014_rec = ,
    # q_vote_eu_2014_rec_text = ,
    # q_euint_ecb = ,
    # q_econ_eval_retro = ,
    # q_econ_resp_natgov = ,
    # q_econ_resp_eu = ,
    # q_econ_resp_imm = ,
    # q_econ_resp_global = ,
    # q_news_online = ,
    # q_news_print = ,
    # q_fin_strain = ,
    # q_euint_party_9 = ,
    # q_euint_party_10 = ,
    # q_lr_party_13 = ,
    # prime_respresp_condition = ,
    # prime_gridlock_condition = ,
    # prime_compliance_condition = ,
    # prime_court_condition = ,
    # prime_econblame_condition = ,
    # cj_task_instruction = ,
    # prime_respresp_text = ,
    # prime_gridlock_text = ,
    # prime_compliance_text = ,
    # prime_court_text = ,
    # prime_moreeu_firstclick = ,
    # prime_moreeu_lastclick = ,
    # prime_moreeu_pagesubmit = ,
    # prime_moreeu_clickcount = ,
    # q_vote_turnout_confirm = ,
    # q_vote_choice_intended = ,
    # q_vote_choice_intended_other = ,
    # q_election_challenge_polgroups = ,
    # q_election_impact_eu = ,
    # q_election_importance_self = ,
    # q_news_newspaper = ,
    # q_news_radio = ,
    # q_news_social = ,
    # q_news_internet = ,
    # q_news_personal = ,
    # q_news_other = ,
    # q_news_other_text = ,
    # q_eu_efficacy_understand_fra = ,
    # q_eu_efficacy_care_fra = ,
    # q_eu_efficacy_nosay_fra = ,
    # q_pop_will_fra = ,
    # q_pop_people_fra = ,
    # q_pop_citizen_fra = ,
    # q_pop_reps_fra = ,
    # q_pop_goodevil_fra = ,
    # q_pop_compromise_fra = ,
    # q_dem_compromise_fra = ,
    # q_dem_listen_fra = ,
    # q_tech_experts_fra = ,
    # q_tech_leaders_fra = ,
    # q_party_harm_fra = ,
    # q_people_incompetent_fra = ,
    # q_eu_longterm_fra = ,
    # q_eu_responsive_fra = ,
    # q_eu_imp_nat_econ_fra = ,
    # q_eu_imp_nat_cul_fra = ,
    # q_eu_imp_nat_pol_fra = ,
    # q_eu_abolish_fra = ,
    # q_eu_satisfaction_fra = ,
    # q_euint_pos_fra = ,
    # q_vote_turnout_reason_fra = ,
    # q_vote_choice_past_fra = ,
    # q_vote_choice_past_other_fra = ,
    # q_vote_choice_hypo_fra = ,
    # q_vote_choice_hypo_other_fra = ,
    # q_vote_choice_ep2014_fra = ,
    # q_vote_choice_ep2014_other_fra = ,
    # q_party_id_fra = ,
    # q_party_id_other_fra = ,
    # q_eu_campaign_sources_fra = ,
    # q_eu_campaign_sources_other_fra = ,
    # q_campaign_activity_fra = ,
    # q_campaign_activity_other_fra = ,
    # prime_cjeu_fra_firstclick = ,
    # prime_cjeu_fra_lastclick = ,
    # prime_cjeu_fra_pagesubmit = ,
    # prime_cjeu_fra_clickcount = ,
    # q_cjeu_abolish_fra = ,
    # q_cjeu_satisfaction_fra = ,
    # q_cjeu_pos_fra = ,
    # q_norm_tolerance_fra = ,
    # q_norm_order_fra = ,
    # q_norm_unjust_law_fra = ,
    # q_norm_unvoted_gov_fra = ,
    # q_norm_bypass_law_fra = ,
    # q_norm_gov_bypass_fra = ,
    # q_eval_econ_eur_fra = ,
    # q_eval_econ_nat_fra = ,
    # q_eval_fin_household_fra = ,
    # q_eval_job_fra = ,
    # q_nativ_econ_fra = ,
    # q_nativ_cult_fra = ,
    # q_nativ_3_fra = ,
    # q_nativ_4_fra = ,
    # q_satis_demo_nat_fra = ,
    # q_satis_demo_eu_fra = ,
    # q_nat_int_fra = ,
    # q_eu_int_fra = ,
    # q_nativ_econ_b_fra = ,
    # q_nativ_cult_b_fra = ,
    # q_eu_know_1_fra = ,
    # q_eu_know_2_fra = ,
    # q_eu_know_3_fra = ,
    # q_eu_know_4_fra = ,
    # q_eu_know_5_fra = ,
    # q_eu_informed_com_fra = ,
    # q_eu_informed_cou_fra = ,
    # q_eu_informed_ep_fra = ,
    # q_eu_informed_cjeu_fra = ,
    # q_eu_trust_com_fra = ,
    # q_eu_trust_cou_fra = ,
    # q_eu_trust_ep_fra = ,
    # q_eu_trust_cjeu_fra = ,
    # q_risk_taking_fra = ,
    # q_future_discount_fra = ,
    # prime_moreeu_condition = ,
    # prime_moreeu_text = ,
    # q_vote_exp_rank_party_1 = ,
    # q_vote_exp_rank_party_2 = ,
    # q_vote_exp_rank_party_3 = ,
    # q_vote_exp_rank_party_4 = ,
    # q_vote_exp_rank_party_5 = ,
    # q_vote_exp_rank_party_6 = ,
    # prime_cjeu_fra_condition = ,
    # prime_cjeu_fra_text = ,
    # q_campaign_activity = ,
    # q_campaign_activity_other = ,
    # q_nativ_3 = ,
    # q_nativ_4 = ,
    # q_nativ_econ_b = ,
    # q_nativ_cult_b = ,
  )
```

```{r}
#| label: validate-cjgames-recode
df_stacked_recoded |>
  select(cj_dict1_rel, cj_dict1_rel_raw) |>
  filter(is.na(cj_dict1_rel) & !is.na(cj_dict1_rel_raw)) |>
  distinct(cj_dict1_rel_raw)

df_stacked_recoded |>
  select(cj_dict2_rel, cj_dict2_rel_raw) |>
  filter(is.na(cj_dict2_rel) & !is.na(cj_dict2_rel_raw)) |>
  distinct(cj_dict2_rel_raw)

df_stacked_recoded |>
  select(cj_dict3_rel, cj_dict3_rel_raw) |>
  filter(is.na(cj_dict3_rel) & !is.na(cj_dict3_rel_raw)) |>
  distinct(cj_dict3_rel_raw)

df_stacked_recoded |>
  select(cj_trust1_rel, cj_trust1_rel_raw) |>
  filter(is.na(cj_trust1_rel) & !is.na(cj_trust1_rel_raw)) |>
  distinct(cj_trust1_rel_raw)

df_stacked_recoded |>
  select(cj_trust2_rel, cj_trust2_rel_raw) |>
  filter(is.na(cj_trust2_rel) & !is.na(cj_trust2_rel_raw)) |>
  distinct(cj_trust2_rel_raw)

df_stacked_recoded |>
  select(cj_trust3_rel, cj_trust3_rel_raw) |>
  filter(is.na(cj_trust3_rel) & !is.na(cj_trust3_rel_raw)) |>
  distinct(cj_trust3_rel_raw)
```

# Save Full Recoded Wide EU25 Dataset

```{r}
#| label: save
write_rds(
  df_stacked_recoded,
  file = here(
    "data",
    "03_final",
    "eu25games2019.rds"
  )
)
```

## CONTINUE

```{r}
#| label: continue
#| eval: false

# purrr::keep(groups_named[["FR"]], ~ any(grepl("_raw", .x)))

# df_stacked_recoded <- df_stacked_recoded |>
#   mutate(
    # q_eu_longterm = ,
    # q_eu_responsive = ,
    # q_eu_efficacy_understand = ,
    # q_eu_efficacy_care = ,
    # q_eu_efficacy_nosay = ,
    # q_eu_abolish = ,
    # q_eu_satisfaction = ,
    # q_party_id = ,
    # q_eu_informed_com = ,
    # q_eu_informed_cou = ,
    # q_eu_informed_ep = ,
    # q_eu_informed_cjeu = ,
    # q_eu_trust_com = ,
    # q_eu_trust_cou = ,
    # q_eu_trust_ep = ,
    # q_eu_trust_cjeu = ,
    # q_cjeu_abolish = ,
    # q_cjeu_satisfaction = ,
    # q_nat_int = ,
    # q_eu_int = ,
    # q_nativ_econ = ,
    # q_nativ_cult = ,
    # q_eu_know_1 = ,
    # q_eu_know_2 = ,
    # q_eu_know_3 = ,
    # q_eu_know_4 = ,
    # q_eu_know_5 = ,
    # q_lr_self = ,
    # q_lr_party_1 = ,
    # q_lr_party_2 = ,
    # q_lr_party_3 = ,
    # q_lr_party_4 = ,
    # q_lr_party_5 = ,
    # q_lr_party_6 = ,
    # q_lr_party_7 = ,
    # q_lr_party_8 = ,
    # q_lr_com = ,
    # q_lr_cou = ,
    # q_lr_ep = ,
    # q_lr_cjeu = ,
    # q_euint_self = ,
    # q_euint_party_1 = ,
    # q_euint_party_2 = ,
    # q_euint_party_3 = ,
    # q_euint_party_4 = ,
    # q_euint_party_5 = ,
    # q_euint_party_6 = ,
    # q_euint_party_7 = ,
    # q_euint_party_8 = ,
    # q_euint_com = ,
    # q_euint_cou = ,
    # q_euint_ep = ,
    # q_euint_cjeu = ,
    # q_edu_age_stop = ,
    # q_occ_current = ,
    # q_occ_last = ,
    # meta_country = ,
    # meta_psid = ,
    # meta_pid = ,
    # meta_device = ,
    # q_news_tv = ,
    # q_lr_party_9 = ,
    # q_lr_party_10 = ,
    # q_lr_party_11 = ,
    # q_lr_party_12 = ,
    # q_norm_tol_opposition = ,
    # q_norm_order_over_freedom = ,
    # q_norm_disobey_unjustlaw = ,
    # q_norm_disobey_gov = ,
    # q_norm_bypass_law = ,
    # q_norm_gov_bend_law = ,
    # q_religion = ,
    # q_class = ,
    # q_verif = ,
    # q_verif2 = ,
    # q_euint_pos = ,
    # q_dem_compromise = ,
    # q_dem_listen = ,
    # q_tech_experts = ,
    # q_tech_leaders = ,
    # q_party_harm = ,
    # q_people_incompetent = ,
    # q_eu_imp_nat_econ = ,
    # q_eu_imp_nat_cul = ,
    # q_eu_imp_nat_pol = ,
    # q_vote_turnout_likelihood = ,
    # q_vote_choice_past = ,
    # q_vote_choice_past_other = ,
    # q_vote_choice_hypo = ,
    # q_vote_choice_hypo_other = ,
    # q_vote_choice_past2014 = ,
    # q_vote_choice_past2014_other = ,
    # q_party_id_other = ,
    # q_eu_campaign_sources = ,
    # q_eu_campaign_sources_other = ,
    # prime_cjeu_firstclick = ,
    # prime_cjeu_lastclick = ,
    # prime_cjeu_pagesubmit = ,
    # prime_cjeu_clickcount = ,
    # q_cjeu_pos = ,
    # q_eval_econ_eur = ,
    # q_eval_econ_nat = ,
    # q_eval_fin_household = ,
    # q_eval_job = ,
    # q_satis_demo_nat = ,
    # q_satis_demo_eu = ,
    # q_risk_taking = ,
    # q_future_discount = ,
    # q_eu_efficacy_understand_c = ,
    # q_eu_efficacy_care_c = ,
    # q_eff_external_nosay_c = ,
    # q_rural_urban = ,
    # q_postal_code = ,
    # q_region = ,
  )
```



# Session Info {#sec-session}

```{r}
#| label: exec-time
#| eval: true
end_time <- Sys.time()
cat("Execution time:", round(end_time - start_time, 2), "seconds\n")
```

```{r}
#| label: session-info
#| eval: true
sessioninfo::session_info()
```
