---
title: |
  Code Notebook 2
subtitle: |
  EU 25 Behavioral Games Survey Experiment 2019: Recode Variables
author:
  - name: Tristan Muno
    email: tristan.muno@uni-mannheim.de
    affiliations:
      - name: University of Mannheim
        department: School of Social Sciences
date: last-modified
date-format: MMMM D, YYYY
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: true
    code-tools: true
    embed-resources: true
execute:
  echo: true
  warning: true
  eval: true
  message: true
---

# Setup {#sec-setup}

```{r}
#| label: setup

start_time <- Sys.time()

options(width = 80)

p_required <- c(
  "tidyverse", # data wrangling
  "here", # relative paths
  "future", # parallel backend
  "furrr", # parallel map() functions
  "janitor", # tabyl
  "sessioninfo" # session info
)
packages <- rownames(installed.packages())
p_to_install <- p_required[!(p_required %in% packages)]
if (length(p_to_install) > 0) {
  install.packages(p_to_install)
}
sapply(p_required, require, character.only = TRUE)
rm(p_required, p_to_install, packages)
```

```{r}
#| label: load-data

# stacked waves ----------------------------------------------------------------
df_stacked <- read_rds(
  here(
    "data",
    "02_processed",
    "waves_stacked.rds"
  )
)

# load wording map
wording_map <- read_csv(
  here(
    "data",
    "02_processed",
    "question_wording_map.csv"
  )
)
```

# Recode Variable Values (Phase 8)

CONTINUE HERE: LET CLAUDE DYNAMICALLY RECEIVE INFO FOR ALL LANGUAGES AND THEN UPDATE THE SCALE MAP VECTORS

THEN HAVE HIM IMPLEMENT THE RECODING CONSISTENTLY

Strategy:

Collect vars to recode
divide into numeric and categorical
group numerics into scales
harmonize categorical to english
recode numerical to numeric

do this variable by variable

```{r}
#| label: collect-information
# colnames and current type ----------------------------------------------------
cols <- tibble(
  cols = df_stacked |> colnames(),
  col_type = df_stacked |> map_chr(class)
)
# pre-split by country — workers receive slices, not full df ------------------
countries <- df_stacked |> distinct(meta_country) |> pull(meta_country)
df_by_country <- countries |>
  set_names() |>
  lapply(function(country) filter(df_stacked, meta_country == country))
col_names <- names(df_stacked) # small vector, fine to export
compute_groups <- function(df_country) {
  cat(paste0("starting\n"))
  # signatures in one pass -----------------------------------------------------
  signatures <- sapply(seq_len(ncol(df_country)), function(i) {
    df_country[[i]] |>
      as.character() |>
      unique() |>
      sort() |>
      paste(collapse = "||")
  })
  # group + name back ----------------------------------------------------------
  groups <- split(seq_along(signatures), signatures)
  lapply(groups, function(idx) col_names[idx])
}
# run in parallel for each country --------------------------------------------
plan(multisession)
groups_named <- future_map(df_by_country, compute_groups)
plan(sequential)
```

```{r}
#| label: value-labels

# GENDER -----------------------------------------------------------------------
male_vec <- c(
  "Male",
  "Männlich",
  "Мъж",
  "Muškarac",
  "Muž",
  "Mand",
  "Mees",
  "Mies",
  "Homme",
  "Männlich",
  "Άνδρας",
  "Férfi",
  "Maschio",
  "Vīrietis",
  "Vyras",
  "Man",
  "Mężczyzna",
  "Masculino",
  "Bărbat",
  "Muž",
  "Moški",
  "Hombre",
  "Man",
  "Man"
)
female_vec <- c(
  "Female",
  "Weiblich",
  "Жена",
  "Žena",
  "Žena",
  "Kvinde",
  "Naine",
  "Nainen",
  "Femme",
  "Weiblich",
  "Γυναίκα",
  "Nő",
  "Femmina",
  "Sieviete",
  "Moteris",
  "Vrouw",
  "Kobieta",
  "Feminino",
  "Femenino",
  "Femeie",
  "Žena",
  "Ženski",
  "Mujer",
  "Kvinna",
  "Vrouw",
  "2"
)

# NATIONALITY ------------------------------------------------------------------
austria_vec <- c(
  "Österreich",
  "Австрия",
  "Austrija",
  "Rakousko",
  "Austria",
  "Itävalta",
  "Autriche",
  "Αυστρία",
  "Ausztria",
  "Oostenrijk",
  "Avstrija",
  "Österrike"
)

belgium_vec <- c(
  "Belgien",
  "Belgique",
  "België",
  "Белгия",
  "Belgija",
  "Belgie",
  "Belgia",
  "Belgio",
  "Belgium",
  "Beļģija",
  "Belgija",
  "Belgicko",
  "Bélgica"
)

bulgaria_vec <- c(
  "Bulgarien",
  "България",
  "Bugarska",
  "Bulgaaria",
  "Bulgaria",
  "Bulgarie",
  "Βουλγαρία",
  "Bulgária",
  "Bulgārija",
  "Bulgarija",
  "Bulgarije",
  "Bułgaria",
  "Bolgarija",
  "Bulharsko"
)

croatia_vec <- c(
  "Kroatien",
  "Hrvatska",
  "Chorvatsko",
  "Kroatia",
  "Croatie",
  "Croazia",
  "Croatia",
  "Kroatija",
  "Chorwacja",
  "Croaţia",
  "Hrvaška",
  "Croacia"
)

czechia_vec <- c(
  "Tschechische Republik",
  "Tsjechië",
  "Češka",
  "Česká republika",
  "Csehország",
  "Czech Republic",
  "Čekijos Respublika",
  "Czechy",
  "Češka republika",
  "Tjeckien"
)

denmark_vec <- c(
  "Dänemark",
  "Danemark",
  "Denemarken",
  "Дания",
  "Danska",
  "Dania",
  "Danmark",
  "Tanska",
  "Denmark",
  "Dānija",
  "Danija",
  "Danemarca",
  "Dánsko"
)

estonia_vec <- c(
  "Estland",
  "Estonija",
  "Estonsko",
  "Eesti",
  "Viro",
  "Estonie",
  "Észtország",
  "Estonia",
  "Igaunija",
  "Estonija"
)

finland_vec <- c(
  "Finnland",
  "Finska",
  "Finland",
  "Suomi",
  "Finlande",
  "Φινλανδία",
  "Finnország",
  "Suomija",
  "Finlanda"
)

france_vec <- c(
  "Frankreich",
  "France",
  "Frankrijk",
  "Francuska",
  "Frankrig",
  "Ranska",
  "Γαλλία",
  "Francija",
  "França",
  "Franţa",
  "Francúzsko",
  "Francia",
  "Frankrike"
)

germany_vec <- c(
  "Deutschland",
  "Allemagne",
  "Duitsland",
  "Германия",
  "Njemačka",
  "Tyskland",
  "Saksa",
  "Γερμανία",
  "Németország",
  "Germania",
  "Germany",
  "Vācija",
  "Niemcy",
  "Alemanha",
  "Nemčija",
  "Nemecko",
  "Alemania"
)

greece_vec <- c(
  "Griechenland",
  "Řecko",
  "Ελλάδα",
  "Grecia",
  "Greece",
  "Grieķija",
  "Graikija",
  "Griekenland",
  "Grecja",
  "Grčija",
  "Grécko",
  "Grekland"
)

hungary_vec <- c(
  "Ungarn",
  "Mađarska",
  "Ungari",
  "Magyarország",
  "Hungary",
  "Hongarije",
  "Ungaria",
  "Madžarska",
  "Maďarsko"
)

ireland_vec <- c(
  "Irska",
  "Ireland",
  "Īrija",
  "Airija",
  "Ierland",
  "Irlandia",
  "Irlanda"
)

italy_vec <- c(
  "Italien",
  "Italie",
  "Italië",
  "Italija",
  "Olaszország",
  "Italia",
  "Italy",
  "Itālija",
  "Itália"
)

latvia_vec <- c(
  "Lettland",
  "Letland",
  "Läti",
  "Lettonia",
  "Latvia",
  "Λετονία",
  "Latvija",
  "Letonia"
)

lithuania_vec <- c(
  "Litauen",
  "Lituanie",
  "Litouwen",
  "Leedu",
  "Lithuania",
  "Lietuva",
  "Litwa",
  "Lituania",
  "Litva"
)

netherlands_vec <- c(
  "Niederlande",
  "Pays-Bas",
  "Nederland",
  "Nizozemska",
  "Nederlandene",
  "Alankomaat (Hollanti)",
  "Netherlands",
  "Holandia",
  "Holanda",
  "Nizozemska"
)

poland_vec <- c(
  "Polen",
  "Pologne",
  "Poljska",
  "Polsko",
  "Poola",
  "Puola",
  "Πολωνία",
  "Polonia",
  "Poland",
  "Polija",
  "Lenkija",
  "Polska",
  "Polónia",
  "Poľsko"
)

portugal_vec <- c(
  "Portugal",
  "Португалия",
  "Portugalsko",
  "Portugali",
  "Portugalija",
  "Portugalia"
)

romania_vec <- c(
  "Rumänien",
  "Roumanie",
  "Roemenië",
  "Rumænien",
  "Romania",
  "Ρουμανία",
  "Románia",
  "România",
  "Rumunsko",
  "Rumanía"
)

slovakia_vec <- c(
  "Slowakei",
  "Slovaquie",
  "Slovačka",
  "Slovensko",
  "Slovakkia",
  "Szlovákia",
  "Slovakia",
  "Slovaška"
)

slovenia_vec <- c(
  "Slowenien",
  "Slovenija",
  "Slovinsko",
  "Slovenien",
  "Sloveenia",
  "Slovenia",
  "Slovēnija",
  "Slovėnija",
  "Eslovénia",
  "Eslovenia"
)

spain_vec <- c(
  "Spanien",
  "Espagne",
  "Spanje",
  "Hispaania",
  "Spagna",
  "Spain",
  "Ispanija",
  "Espanha",
  "Španija",
  "Španielsko",
  "España"
)

sweden_vec <- c(
  "Suède",
  "Zweden",
  "Sverige",
  "Ruotsi",
  "Sweden",
  "Švedija",
  "Szwecja",
  "Suedia",
  "Švedska"
)

united_kingdom_vec <- c(
  "Vereinigtes Königreich (Großbritannien, Nordirland)",
  "Verenigd Koninkrijk (Groot-Brittannië, Noord-Ierland)",
  "Ujedinjena Kraljevina Velike Britanije i Sjeverne Irske",
  "Velká Británie",
  "Storbritannien, Nordirland",
  "Yhdistynyt kuningaskunta (Iso-Britannia, Pohjois-Irlanti)",
  "Royaume-Uni (Grande Bretagne, Irlande du Nord)",
  "Egyesült Királyság (Nagy-Britannia, Észak-Írország)",
  "United Kingdom (Great Britain, Northern Ireland)",
  "Apvienotā Karaliste (Lielbritānija, Ziemeļīrija)",
  "Jungtinė Karalystė (Didžioji Britanija, Šiaurės Airija)",
  "Zjednoczone Królestwo (Wielka Brytania, Irlandia Północna)",
  "Reino Unido (Grã-Bretanha, Irlanda do Norte)",
  "Regatul Unit (Marea Britanie, Irlanda de Nord)",
  "Združeno kraljestvo (Velika Britanija, Severna Irska)",
  "Reino Unido (Gran Bretaña, Irlanda del Norte)",
  "Storbritannien (England, Skottland, Wales, Nordirland)"
)

luxembourg_vec <- c(
  "Luxemburg",
  "Luxembourg",
  "Luksemburg",
  "Liuksemburgas"
)

malta_vec <- c(
  "Malta",
  "Málta"
)

cyprus_vec <- c(
  "Cipar",
  "Kyperská republika",
  "Cypern (Syd)",
  "Cipro (sud)",
  "Κυπριακή Δημοκρατία",
  "Ciprusi - Köztársaság",
  "Kipro Respublika",
  "Cypr (południowy)",
  "Republic of Cyprus"
)

other_country_vec <- c(
  "Andere Länder",
  "Autre pays",
  "Andere landen",
  "Друга държава",
  "Ostale zemlje",
  "Jiná země",
  "Andre lande",
  "Muu riik",
  "Joku muu maa/maat",
  "Άλλες χώρες",
  "Más ország",
  "Altri paesi",
  "Other countries",
  "Citas valstis",
  "Kitos valstybės",
  "Inne kraje",
  "Outros países",
  "Alte ţări",
  "Druge države",
  "Iné krajiny",
  "Otros países",
  "Annat land",
  "Other country"
)

dont_know_vec <- c(
  "Weiß nicht",
  "Ne zna",
  "Ne znam",
  "Nevím",
  "Ved ikke",
  "Ei oska öelda",
  "En tiedä",
  "Ne sait pas",
  "Nem tudom",
  "Don't know",
  "Nezinu",
  "Nežinau",
  "Weet niet",
  "Nie wiem",
  "Não sei",
  "Nu ştiu",
  "Ne vem",
  "Nevie, bez odpovede",
  "Neviem",
  "No lo sé",
  "Vet ej"
)

# Nationality lookup
nat_lookup <- c(
  setNames(rep("Austria", length(austria_vec)), austria_vec),
  setNames(rep("Belgium", length(belgium_vec)), belgium_vec),
  setNames(rep("Bulgaria", length(bulgaria_vec)), bulgaria_vec),
  setNames(rep("Croatia", length(croatia_vec)), croatia_vec),
  setNames(rep("Czechia", length(czechia_vec)), czechia_vec),
  setNames(rep("Denmark", length(denmark_vec)), denmark_vec),
  setNames(rep("Estonia", length(estonia_vec)), estonia_vec),
  setNames(rep("Finland", length(finland_vec)), finland_vec),
  setNames(rep("France", length(france_vec)), france_vec),
  setNames(rep("Germany", length(germany_vec)), germany_vec),
  setNames(rep("Greece", length(greece_vec)), greece_vec),
  setNames(rep("Hungary", length(hungary_vec)), hungary_vec),
  setNames(rep("Ireland", length(ireland_vec)), ireland_vec),
  setNames(rep("Italy", length(italy_vec)), italy_vec),
  setNames(rep("Latvia", length(latvia_vec)), latvia_vec),
  setNames(rep("Lithuania", length(lithuania_vec)), lithuania_vec),
  setNames(rep("Luxembourg", length(luxembourg_vec)), luxembourg_vec),
  setNames(rep("Malta", length(malta_vec)), malta_vec),
  setNames(rep("Cyprus", length(cyprus_vec)), cyprus_vec),
  setNames(rep("Netherlands", length(netherlands_vec)), netherlands_vec),
  setNames(rep("Poland", length(poland_vec)), poland_vec),
  setNames(rep("Portugal", length(portugal_vec)), portugal_vec),
  setNames(rep("Romania", length(romania_vec)), romania_vec),
  setNames(rep("Slovakia", length(slovakia_vec)), slovakia_vec),
  setNames(rep("Slovenia", length(slovenia_vec)), slovenia_vec),
  setNames(rep("Spain", length(spain_vec)), spain_vec),
  setNames(rep("Sweden", length(sweden_vec)), sweden_vec),
  setNames(
    rep("United Kingdom", length(united_kingdom_vec)),
    united_kingdom_vec
  ),
  setNames(rep("Other", length(other_country_vec)), other_country_vec)
)

# Translate tokens via lookup
translate_nat <- function(x) {
  if (is.na(x)) {
    return(NA_character_)
  }
  tokens <- str_trim(str_split(x, ",")[[1]])
  translated <- nat_lookup[tokens]
  # keep original token if not found
  translated[is.na(translated)] <- tokens[is.na(translated)]
  paste(translated, collapse = ", ")
}


# CJ Religion Attribute --------------------------------------------------------
cj_muslim_vec <- c(
  "Muslimisch",
  "Moslim",
  "Musulman",
  "мюсюлманин",
  "Musliman",
  "Muslim",
  "Muslim",
  "Moslim",
  "Moslem",
  "Muslimi",
  "Musulman",
  "Muslimisch",
  "Μουσουλμάνος",
  "Muzulmán",
  "Musulmana",
  "musulmanis",
  "Musulmanis", #Lv
  "Musulmonas",
  "Muzułmańskie",
  "Muçulmano",
  "Musulman",
  "Moslimské",
  "Muslimanska",
  "Musulmana",
  "Muslim",
  "Muslim"
)

cj_protestant_vec <- c(
  "Protestantisch",
  "Protestant",
  "Protestant",
  "Protestant",
  "протестант",
  "Protestant",
  "Protestant",
  "Protestant",
  "Protestant",
  "Protestant",
  "Protestantti",
  "Protestant",
  "Protestantisch",
  "Διαμαρτυρόμενος",
  "Protestáns",
  "Protestante",
  "protestants",
  "Protestants", #lv
  "Protestantas",
  "Protestanckie",
  "Protestante",
  "Protestant",
  "Protestantské",
  "Protestantska",
  "Protestante",
  "Protestant"
)

cj_catholic_vec <- c(
  "Katholisch",
  "Catholic",
  "Katholiek",
  "Catholique",
  "католик",
  "Katolik",
  "Katolík",
  "Katolik",
  "Katholiek",
  "Katoliiklane",
  "Katolilainen",
  "Catholique",
  "Katholisch",
  "Καθολικός",
  "Katolikus",
  "Cattolica",
  "katolis",
  "Katolis", #lv
  "Katalikas",
  "Katolickie",
  "Católico",
  "Catolic",
  "Katolícke",
  "Katoliška",
  "Católica",
  "Katolik"
)

cj_nonreli_vec <- c(
  "Keine Religion",
  "No Religion",
  "Geen religie",
  "Sans religion",
  "без религия",
  "Nije vjernik",
  "Bez vyznání",
  "Ikke religiøs",
  "Geen religie",
  "Ei ole usklik",
  "Ei uskontoa",
  "Sans religion",
  "Keine Religion",
  "Χωρίς θρησκεία",
  "Nincs vallása",
  "Nessuna religione",
  "bez reliģiskās piederības",
  "Bez reliģiskās piederības",
  "Nėra religijos",
  "Nie wierzący(-a)",
  "Sem religião",
  "Nicio religie",
  "Žiadne vierovyznanie",
  "Brez religije",
  "Sin religión",
  "Ingen religion"
)
```

Recoding code: comment variables that stay character, recode to numeric (integer if possible), logical, date or factor for all others

```{r}
#| label: recode-vars

# character variables: comment out
df_stacked_recoded <- df_stacked |>
  mutate(
    # META VARS ----------------------------------------------------------------
    meta_wave = as.integer(meta_wave),
    # meta_country = ,
    meta_startdate = as.POSIXct(meta_startdate),
    meta_enddate = as.POSIXct(meta_enddate),
    # meta_status = ,
    # meta_ipaddress = ,
    meta_progress = as.integer(meta_progress),
    meta_duration_s = as.integer(meta_duration_s),
    meta_finished = as.logical(meta_finished),
    meta_recordeddate = as.POSIXct(meta_recordeddate),
    # meta_responseid = ,
    # meta_recipient_lastname = ,
    # meta_recipient_firstname = ,
    # meta_recipient_email = ,
    # meta_external_ref = ,
    meta_latitude = as.numeric(meta_latitude),
    meta_longitude = as.numeric(meta_longitude),
    # meta_distchannel = ,
    # meta_lang = ,
    # GENDER -------------------------------------------------------------------
    q_gender = case_when(
      q_gender_raw %in% male_vec ~ "male",
      q_gender_raw %in% female_vec ~ "female",
      !is.na(q_gender_raw) ~ "other"
    ),
    # AGE ----------------------------------------------------------------------
    q_age = as.integer(str_extract(q_age_raw, "\\d+")),
    # NATIONALITY --------------------------------------------------------------
    q_nationality = map_chr(q_nationality_raw, translate_nat),
    q_nationality_n = map_int(q_nationality_raw, \(x) {
      if (is.na(x)) NA_integer_ else length(str_split(x, ",")[[1]])
    }),
    q_nationality_other = case_when(
      str_trim(q_nationality_other_raw) %in%
        c("afghan", "afghanistanskt") ~ "Afghanistan",
      str_trim(q_nationality_other_raw) %in%
        c("Albanië", "albania") ~ "Albania",
      str_trim(q_nationality_other_raw) %in%
        c("Algérie", "algerie", "ALGERIE") ~ "Algeria",
      str_trim(q_nationality_other_raw) %in% c("angola", "Angola") ~ "Angola",
      str_trim(q_nationality_other_raw) %in%
        c(
          "Argentina",
          "argentina",
          "Argentinien",
          "ARGENTINA",
          "argentine"
        ) ~ "Argentina",
      str_trim(q_nationality_other_raw) %in%
        c("Armenia", "Armenien") ~ "Armenia",
      str_trim(q_nationality_other_raw) %in%
        c("Australien", "AUSTRALIA", "Australia") ~ "Australia",
      str_trim(q_nationality_other_raw) %in%
        c("Österreich", "austria") ~ "Austria",
      str_trim(q_nationality_other_raw) %in%
        c("Azerbajdzjan", "Azerbaijan") ~ "Azerbaijan",
      str_trim(q_nationality_other_raw) %in%
        c("Bangladesh", "BANGLADESHI") ~ "Bangladesh",
      str_trim(q_nationality_other_raw) %in%
        c(
          "Беларусь",
          "Belarus",
          "belarus",
          "Bělorusko",
          "valko-venäjä"
        ) ~ "Belarus",
      str_trim(q_nationality_other_raw) %in% c("Bolivia") ~ "Bolivia",
      str_trim(q_nationality_other_raw) %in%
        c(
          "BiH",
          "Bih",
          "Bosna i Hercegovina",
          "Bosna in Herzegovina",
          "Bosnien & Hercegovina",
          "Bosnien & Hercegovina",
          "Bosnia",
          "bosnien",
          "Bosnien"
        ) ~ "Bosnia and Herzegovina",
      str_trim(q_nationality_other_raw) %in%
        c(
          "Brésil",
          "Brasil",
          "brasil",
          "BRASIL",
          "Brazil",
          "brazil",
          "Brazilie",
          "Brasilien",
          "ΒΡΑΖΙΛΙΑ",
          "brazilian",
          "Brazilian",
          "Brasilian",
          "Brasileira"
        ) ~ "Brazil",
      str_trim(q_nationality_other_raw) %in%
        c(
          "Kanada",
          "Canada",
          "canada",
          "Canadian",
          "canadian",
          "Kanadishe",
          "ΚΑΝΑΔΑΣ"
        ) ~ "Canada",
      str_trim(q_nationality_other_raw) %in%
        c("cabo verde", "Cabo Verde") ~ "Cape Verde",
      str_trim(q_nationality_other_raw) %in%
        c("cameroun", "Cameroun", "Cameroon") ~ "Cameroon",
      str_trim(q_nationality_other_raw) %in%
        c("centrafricaine") ~ "Central African Republic",
      str_trim(q_nationality_other_raw) %in% c("chile") ~ "Chile",
      str_trim(q_nationality_other_raw) %in%
        c("China", "Chinese", "CHINOISE") ~ "China",
      str_trim(q_nationality_other_raw) %in%
        c("colombia", "Colombia") ~ "Colombia",
      str_trim(q_nationality_other_raw) %in%
        c(
          "Hrvatska",
          "hrvatska",
          "Hrvatsko",
          "croatia"
        ) ~ "Croatia",
      str_trim(q_nationality_other_raw) %in%
        c("cubaanse", "Cuba", "cuba") ~ "Cuba",
      str_trim(q_nationality_other_raw) %in%
        c("RD CONGO") ~ "Democratic Republic of the Congo",
      str_trim(q_nationality_other_raw) %in% c("Ecuador") ~ "Ecuador",
      str_trim(q_nationality_other_raw) %in%
        c("Egypt", "Egy", "egyptian") ~ "Egypt",
      str_trim(q_nationality_other_raw) %in% c("El Salvador") ~ "El Salvador",
      str_trim(q_nationality_other_raw) %in%
        c("Eesti", "eesti", "eestlane") ~ "Estonia",
      str_trim(q_nationality_other_raw) %in% c("Fijian") ~ "Fiji",
      str_trim(q_nationality_other_raw) %in%
        c("suomi", "finska", "finland", "Finland") ~ "Finland",
      str_trim(q_nationality_other_raw) %in% c("Gruzinsko") ~ "Georgia",
      str_trim(q_nationality_other_raw) %in% c("DDR", "Tyskland") ~ "Germany",
      str_trim(q_nationality_other_raw) %in% c("Ghana") ~ "Ghana",
      str_trim(q_nationality_other_raw) %in% c("Guatemala") ~ "Guatemala",
      str_trim(q_nationality_other_raw) %in% c("guyana") ~ "Guyana",
      str_trim(q_nationality_other_raw) %in% c("Haiti") ~ "Haiti",
      str_trim(q_nationality_other_raw) %in%
        c(
          "unkari",
          "magyar",
          "Magyarország",
          "magyarország",
          "MAGYARORSZÁG"
        ) ~ "Hungary",
      str_trim(q_nationality_other_raw) %in% c("Island") ~ "Iceland",
      str_trim(q_nationality_other_raw) %in%
        c(
          "Indien",
          "india",
          "India",
          "ind",
          "Indian",
          "indian",
          "INDIA",
          "indien"
        ) ~ "India",
      str_trim(q_nationality_other_raw) %in% c("Iran", "iran") ~ "Iran",
      str_trim(q_nationality_other_raw) %in% c("irak") ~ "Iraq",
      str_trim(q_nationality_other_raw) %in%
        c(
          "Ireland",
          "Republic of Ireland",
          "republic of Ireland",
          "ireland",
          "ire"
        ) ~ "Ireland",
      str_trim(q_nationality_other_raw) %in% c("Izraela", "Israel") ~ "Israel",
      str_trim(q_nationality_other_raw) %in% c("italian") ~ "Italy",
      str_trim(q_nationality_other_raw) %in% c("Jamaica") ~ "Jamaica",
      str_trim(q_nationality_other_raw) %in%
        c("Japan", "japan", "Japanese") ~ "Japan",
      str_trim(q_nationality_other_raw) %in% c("Kazakstan") ~ "Kazakhstan",
      str_trim(q_nationality_other_raw) %in% c("kenya") ~ "Kenya",
      str_trim(q_nationality_other_raw) %in% c("Korea") ~ "Korea",
      str_trim(q_nationality_other_raw) %in% c("Latvija") ~ "Latvia",
      str_trim(q_nationality_other_raw) %in%
        c("Lebanon", "Libanon") ~ "Lebanon",
      str_trim(q_nationality_other_raw) %in%
        c("Liechtenstein") ~ "Liechtenstein",
      str_trim(q_nationality_other_raw) %in%
        c(
          "lietuva",
          "LIETUVA",
          "Lietuva",
          "Lithuania"
        ) ~ "Lithuania",
      str_trim(q_nationality_other_raw) %in% c("Madagascar") ~ "Madagascar",
      str_trim(q_nationality_other_raw) %in% c("Malawian") ~ "Malawi",
      str_trim(q_nationality_other_raw) %in%
        c("Malaysia", "malaysia") ~ "Malaysia",
      str_trim(q_nationality_other_raw) %in% c("Malta") ~ "Malta",
      str_trim(q_nationality_other_raw) %in% c("Mauritius") ~ "Mauritius",
      str_trim(q_nationality_other_raw) %in% c("Mexico") ~ "Mexico",
      str_trim(q_nationality_other_raw) %in%
        c(
          "Moldavia",
          "moldavia",
          "Republica Moldova"
        ) ~ "Moldova",
      str_trim(q_nationality_other_raw) %in%
        c("Crna Gora", "Czarnogóra") ~ "Montenegro",
      str_trim(q_nationality_other_raw) %in%
        c(
          "Morocco",
          "maroc",
          "Marokko",
          "marokko",
          "maruecos"
        ) ~ "Morocco",
      str_trim(q_nationality_other_raw) %in% c("Moçambique") ~ "Mozambique",
      str_trim(q_nationality_other_raw) %in% c("namibia") ~ "Namibia",
      str_trim(q_nationality_other_raw) %in%
        c("Nederland", "nl", "nederland") ~ "Netherlands",
      str_trim(q_nationality_other_raw) %in% c("Newzealand") ~ "New Zealand",
      str_trim(q_nationality_other_raw) %in%
        c(
          "Nigeria",
          "Nigerian",
          "nigerian",
          "nigeria",
          "NIGERIA"
        ) ~ "Nigeria",
      str_trim(q_nationality_other_raw) %in%
        c("Makedonija") ~ "North Macedonia",
      str_trim(q_nationality_other_raw) %in%
        c(
          "Norge",
          "NORGE",
          "Norwegia",
          "norge",
          "Norge.",
          "Noruego"
        ) ~ "Norway",
      str_trim(q_nationality_other_raw) %in%
        c("Pakistan", "pakistan") ~ "Pakistan",
      str_trim(q_nationality_other_raw) %in% c("Palestine") ~ "Palestine",
      str_trim(q_nationality_other_raw) %in% c("Perú", "peru") ~ "Peru",
      str_trim(q_nationality_other_raw) %in%
        c(
          "FILIPPIINI",
          "Filippiini",
          "philippines",
          "Philippines",
          "Filippernerne",
          "Filippinerna",
          "filippinerne",
          "filipinsk",
          "philiippines"
        ) ~ "Philippines",
      str_trim(q_nationality_other_raw) %in% c("poland", "Polska") ~ "Poland",
      str_trim(q_nationality_other_raw) %in% c("Portugal") ~ "Portugal",
      str_trim(q_nationality_other_raw) %in%
        c(
          "Romania",
          "Romania+",
          "romina",
          "roman",
          "Romana",
          "Rumenien",
          "romania"
        ) ~ "Romania",
      str_trim(q_nationality_other_raw) %in%
        c(
          "Russland",
          "Rußland",
          "Ryssland",
          "Россия",
          "Русия",
          "Ρωσία",
          "Ρωσσια",
          "ΡΩΣΙΑ",
          "Russia",
          "russia",
          "Venemaa",
          "venemaa",
          "Vene",
          "vene",
          "venäjä",
          "Venäjä",
          "rysska",
          "ryska",
          "Rusland",
          "Krievija",
          "krevija",
          "krievija",
          "Krīveja",
          "Rusija",
          "Rusia"
        ) ~ "Russia",
      str_trim(q_nationality_other_raw) %in%
        c(
          "Serbien",
          "Srbija",
          "Srbsko",
          "Serbisch",
          "Σερβία"
        ) ~ "Serbia",
      str_trim(q_nationality_other_raw) %in% c("Singapore") ~ "Singapore",
      str_trim(q_nationality_other_raw) %in%
        c(
          "slovensko",
          "SLOVENSKO",
          "Slovensko",
          "Slovenská republika"
        ) ~ "Slovakia",
      str_trim(q_nationality_other_raw) %in%
        c("slovenija", "SLOVENIJA") ~ "Slovenia",
      str_trim(q_nationality_other_raw) %in%
        c(
          "South Africa",
          "South African",
          "SOUTH AFRICAN",
          "south africa",
          "south Africa",
          "south african",
          "Zuid Afrika",
          "južna afrika"
        ) ~ "South Africa",
      str_trim(q_nationality_other_raw) %in% c("españa") ~ "Spain",
      str_trim(q_nationality_other_raw) %in% c("suriname") ~ "Suriname",
      str_trim(q_nationality_other_raw) %in% c("sverige", "Sverige") ~ "Sweden",
      str_trim(q_nationality_other_raw) %in%
        c(
          "schweiz",
          "Schweiz",
          "Svájc",
          "Suíça"
        ) ~ "Switzerland",
      str_trim(q_nationality_other_raw) %in%
        c(
          "Syrien",
          "syrien",
          "Syrian",
          "Syria",
          "syrer"
        ) ~ "Syria",
      str_trim(q_nationality_other_raw) %in%
        c("Thailand", "thailand") ~ "Thailand",
      str_trim(q_nationality_other_raw) %in% c("togo") ~ "Togo",
      str_trim(q_nationality_other_raw) %in%
        c("Trinidadian") ~ "Trinidad and Tobago",
      str_trim(q_nationality_other_raw) %in%
        c("Tunisie", "tunisie", "Tunisien") ~ "Tunisia",
      str_trim(q_nationality_other_raw) %in%
        c(
          "turque",
          "Turque",
          "Türkei",
          "turkki",
          "Турция",
          "Turkiet",
          "turkiet",
          "Turkki",
          "Turkey",
          "turkije",
          "Turkije",
          "Tyrkiet",
          "Turcija"
        ) ~ "Turkey",
      str_trim(q_nationality_other_raw) %in%
        c(
          "Ukraine",
          "украина",
          "ukr",
          "Ucrânia",
          "ucraina",
          "ukraine",
          "Украйна",
          "ukraina",
          "Ukraina",
          "oekraine",
          "Ucrania",
          "Ukrainian"
        ) ~ "Ukraine",
      str_trim(q_nationality_other_raw) %in%
        c(
          "England",
          "ENGLAND",
          "English",
          "Scotland",
          "Scottish",
          "Welsh"
        ) ~ "United Kingdom",
      str_trim(q_nationality_other_raw) %in%
        c(
          "Verenigde staten",
          "usa",
          "USA",
          "United States",
          "ΗΠΑ",
          "United States of America",
          "Estados Unidos",
          "EEUU"
        ) ~ "United States",
      str_trim(q_nationality_other_raw) %in%
        c("uruguay", "Uruguay") ~ "Uruguay",
      str_trim(q_nationality_other_raw) %in%
        c(
          "venezuela",
          "Venezuela",
          "VENEZUELA",
          "venezolano",
          "Venezolana",
          "venezuelana"
        ) ~ "Venezuela",
      str_trim(q_nationality_other_raw) %in%
        c("Vietnam", "vietnam") ~ "Vietnam",
      .default = NA_character_
    ),
    # q_identity_country = ,
    # q_identity_eu = ,
    # q_identity_europe = ,
    # q_pop_will = ,
    # q_pop_people = ,
    # q_pop_citizen = ,
    # q_pop_reps = ,
    # q_pop_goodevil = ,
    # q_pop_compromise = ,
    # q_eu_longterm = ,
    # q_eu_responsive = ,
    # q_eu_efficacy_understand = ,
    # q_eu_efficacy_care = ,
    # q_eu_efficacy_nosay = ,
    # q_eu_abolish = ,
    # q_eu_satisfaction = ,
    # q_party_id = ,
    # q_eu_informed_com = ,
    # q_eu_informed_cou = ,
    # q_eu_informed_ep = ,
    # q_eu_informed_cjeu = ,
    # q_eu_trust_com = ,
    # q_eu_trust_cou = ,
    # q_eu_trust_ep = ,
    # q_eu_trust_cjeu = ,
    # q_cjeu_abolish = ,
    # q_cjeu_satisfaction = ,
    # q_nat_int = ,
    # q_eu_int = ,
    # q_nativ_econ = ,
    # q_nativ_cult = ,
    # q_eu_know_1 = ,
    # q_eu_know_2 = ,
    # q_eu_know_3 = ,
    # q_eu_know_4 = ,
    # q_eu_know_5 = ,
    # q_lr_self = ,
    # q_lr_party_1 = ,
    # q_lr_party_2 = ,
    # q_lr_party_3 = ,
    # q_lr_party_4 = ,
    # q_lr_party_5 = ,
    # q_lr_party_6 = ,
    # q_lr_party_7 = ,
    # q_lr_party_8 = ,
    # q_lr_com = ,
    # q_lr_cou = ,
    # q_lr_ep = ,
    # q_lr_cjeu = ,
    # q_euint_self = ,
    # q_euint_party_1 = ,
    # q_euint_party_2 = ,
    # q_euint_party_3 = ,
    # q_euint_party_4 = ,
    # q_euint_party_5 = ,
    # q_euint_party_6 = ,
    # q_euint_party_7 = ,
    # q_euint_party_8 = ,
    # q_euint_com = ,
    # q_euint_cou = ,
    # q_euint_ep = ,
    # q_euint_cjeu = ,
    # q_edu_age_stop = ,
    # q_occ_current = ,
    # q_occ_last = ,
    # meta_country = ,
    # meta_psid = ,
    # meta_pid = ,
    # meta_device = ,
    # q_news_tv = ,
    # q_lr_party_9 = ,
    # q_lr_party_10 = ,
    # q_lr_party_11 = ,
    # q_lr_party_12 = ,
    # q_norm_tol_opposition = ,
    # q_norm_order_over_freedom = ,
    # q_norm_disobey_unjustlaw = ,
    # q_norm_disobey_gov = ,
    # q_norm_bypass_law = ,
    # q_norm_gov_bend_law = ,
    # q_religion = ,
    # q_class = ,
    # q_verif = ,
    # q_verif2 = ,
    # q_euint_pos = ,
    # q_dem_compromise = ,
    # q_dem_listen = ,
    # q_tech_experts = ,
    # q_tech_leaders = ,
    # q_party_harm = ,
    # q_people_incompetent = ,
    # q_eu_imp_nat_econ = ,
    # q_eu_imp_nat_cul = ,
    # q_eu_imp_nat_pol = ,
    # q_vote_turnout_likelihood = ,
    # q_vote_choice_past = ,
    # q_vote_choice_past_other = ,
    # q_vote_choice_hypo = ,
    # q_vote_choice_hypo_other = ,
    # q_vote_choice_past2014 = ,
    # q_vote_choice_past2014_other = ,
    # q_party_id_other = ,
    # q_eu_campaign_sources = ,
    # q_eu_campaign_sources_other = ,
    # prime_cjeu_firstclick = ,
    # prime_cjeu_lastclick = ,
    # prime_cjeu_pagesubmit = ,
    # prime_cjeu_clickcount = ,
    # q_cjeu_pos = ,
    # q_eval_econ_eur = ,
    # q_eval_econ_nat = ,
    # q_eval_fin_household = ,
    # q_eval_job = ,
    # q_satis_demo_nat = ,
    # q_satis_demo_eu = ,
    # q_risk_taking = ,
    # q_future_discount = ,
    # q_eu_efficacy_understand_c = ,
    # q_eu_efficacy_care_c = ,
    # q_eff_external_nosay_c = ,
    # q_rural_urban = ,
    # q_postal_code = ,
    # q_region = ,
    # cj_attr_order = ,
    cj_dict_instr_firstclick = as.integer(cj_dict_instr_firstclick),
    cj_dict_instr_lastclick = as.integer(cj_dict_instr_lastclick),
    cj_dict_instr_pagesubmit = as.integer(cj_dict_instr_pagesubmit),
    cj_dict_instr_clickcount = as.integer(cj_dict_instr_clickcount),
    cj_dict1_pl1 = as.integer(cj_dict1_pl1),
    cj_dict1_pl2 = as.integer(cj_dict1_pl2),
    cj_dict1_firstclick = as.integer(cj_dict1_firstclick),
    cj_dict1_lastclick = as.integer(cj_dict1_lastclick),
    cj_dict1_pagesubmit = as.integer(cj_dict1_pagesubmit),
    cj_dict1_clickcount = as.integer(cj_dict1_clickcount),
    # cj_dict1_nat = ,
    # cj_dict1_party = ,
    # cj_dict1_eupos = ,
    cj_dict1_rel = case_when(
      cj_dict1_rel_raw %in% cj_muslim_vec ~ "muslim",
      cj_dict1_rel_raw %in% cj_protestant_vec ~ "protestant",
      cj_dict1_rel_raw %in% cj_catholic_vec ~ "catholic",
      cj_dict1_rel_raw %in% cj_nonreli_vec ~ "non-religious",
    ),
    # cj_dict1_age = ,
    # cj_dict1_sex = ,
    # cj_dict1_class = ,
    cj_dict2_pl1 = as.integer(cj_dict2_pl1),
    cj_dict2_pl2 = as.integer(cj_dict2_pl2),
    cj_dict2_firstclick = as.integer(cj_dict2_firstclick),
    cj_dict2_lastclick = as.integer(cj_dict2_lastclick),
    cj_dict2_pagesubmit = as.integer(cj_dict2_pagesubmit),
    cj_dict2_clickcount = as.integer(cj_dict2_clickcount),
    # cj_dict2_nat = ,
    # cj_dict2_party = ,
    # cj_dict2_eupos = ,
    cj_dict2_rel = case_when(
      cj_dict2_rel_raw %in% cj_muslim_vec ~ "muslim",
      cj_dict2_rel_raw %in% cj_protestant_vec ~ "protestant",
      cj_dict2_rel_raw %in% cj_catholic_vec ~ "catholic",
      cj_dict2_rel_raw %in% cj_nonreli_vec ~ "non-religious",
    ),
    # cj_dict2_age = ,
    # cj_dict2_sex = ,
    # cj_dict2_class = ,
    cj_dict3_pl1 = as.integer(cj_dict3_pl1),
    cj_dict3_pl2 = as.integer(cj_dict3_pl2),
    cj_dict3_firstclick = as.integer(cj_dict3_firstclick),
    cj_dict3_lastclick = as.integer(cj_dict3_lastclick),
    cj_dict3_pagesubmit = as.integer(cj_dict3_pagesubmit),
    cj_dict3_clickcount = as.integer(cj_dict3_clickcount),
    # cj_dict3_nat = ,
    # cj_dict3_party = ,
    # cj_dict3_eupos = ,
    cj_dict3_rel = case_when(
      cj_dict3_rel_raw %in% cj_muslim_vec ~ "muslim",
      cj_dict3_rel_raw %in% cj_protestant_vec ~ "protestant",
      cj_dict3_rel_raw %in% cj_catholic_vec ~ "catholic",
      cj_dict3_rel_raw %in% cj_nonreli_vec ~ "non-religious",
    ),
    # cj_dict3_age = ,
    # cj_dict3_sex = ,
    # cj_dict3_class = ,
    cj_trust_instr_firstclick = as.integer(cj_trust_instr_firstclick),
    cj_trust_instr_lastclick = as.integer(cj_trust_instr_lastclick),
    cj_trust_instr_pagesubmit = as.integer(cj_trust_instr_pagesubmit),
    cj_trust_instr_clickcount = as.integer(cj_trust_instr_clickcount),
    cj_trust1_pl1 = as.integer(cj_trust1_pl1),
    cj_trust1_pl2 = as.integer(cj_trust1_pl2),
    cj_trust1_firstclick = as.integer(cj_trust1_firstclick),
    cj_trust1_lastclick = as.integer(cj_trust1_lastclick),
    cj_trust1_pagesubmit = as.integer(cj_trust1_pagesubmit),
    cj_trust1_clickcount = as.integer(cj_trust1_clickcount),
    # cj_trust1_nat = ,
    # cj_trust1_party = ,
    # cj_trust1_eupos = ,
    cj_trust1_rel = case_when(
      cj_trust1_rel_raw %in% cj_muslim_vec ~ "muslim",
      cj_trust1_rel_raw %in% cj_protestant_vec ~ "protestant",
      cj_trust1_rel_raw %in% cj_catholic_vec ~ "catholic",
      cj_trust1_rel_raw %in% cj_nonreli_vec ~ "non-religious",
    ),
    # cj_trust1_age = ,
    # cj_trust1_sex = ,
    # cj_trust1_class = ,
    cj_trust2_pl1 = as.integer(cj_trust2_pl1),
    cj_trust2_pl2 = as.integer(cj_trust2_pl2),
    cj_trust2_firstclick = as.integer(cj_trust2_firstclick),
    cj_trust2_lastclick = as.integer(cj_trust2_lastclick),
    cj_trust2_pagesubmit = as.integer(cj_trust2_pagesubmit),
    cj_trust2_clickcount = as.integer(cj_trust2_clickcount),
    # cj_trust2_nat = ,
    # cj_trust2_party = ,
    # cj_trust2_eupos = ,
    cj_trust2_rel = case_when(
      cj_trust2_rel_raw %in% cj_muslim_vec ~ "muslim",
      cj_trust2_rel_raw %in% cj_protestant_vec ~ "protestant",
      cj_trust2_rel_raw %in% cj_catholic_vec ~ "catholic",
      cj_trust2_rel_raw %in% cj_nonreli_vec ~ "non-religious",
    ),
    # cj_trust2_age = ,
    # cj_trust2_sex = ,
    # cj_trust2_class = ,
    cj_trust3_pl1 = as.integer(cj_trust3_pl1),
    cj_trust3_pl2 = as.integer(cj_trust3_pl2),
    cj_trust3_firstclick = as.integer(cj_trust3_firstclick),
    cj_trust3_lastclick = as.integer(cj_trust3_lastclick),
    cj_trust3_pagesubmit = as.integer(cj_trust3_pagesubmit),
    cj_trust3_clickcount = as.integer(cj_trust3_clickcount),
    # cj_trust3_nat = ,
    # cj_trust3_party = ,
    # cj_trust3_eupos = ,
    cj_trust3_rel = case_when(
      cj_trust3_rel_raw %in% cj_muslim_vec ~ "muslim",
      cj_trust3_rel_raw %in% cj_protestant_vec ~ "protestant",
      cj_trust3_rel_raw %in% cj_catholic_vec ~ "catholic",
      cj_trust3_rel_raw %in% cj_nonreli_vec ~ "non-religious",
    ),
    # cj_trust3_age = ,
    # cj_trust3_sex = ,
    # cj_trust3_class = ,
    # q_religion_other = ,
    # q_thermo_1 = ,
    # q_thermo_2 = ,
    # q_thermo_3 = ,
    # q_thermo_4 = ,
    # q_thermo_5 = ,
    # q_thermo_6 = ,
    # prime_cjeu_condition = ,
    # prime_cjeu_text = ,
    # cj_rand_issue_order = ,
    # cj_rand_party_a = ,
    # cj_rand_party_b = ,
    # cj_rand_party_c = ,
    # cj_rand_party_d = ,
    # cj_rand_party_e = ,
    # cj_rand_party_f = ,
    # q_policy_comp_val_market = ,
    # q_policy_comp_val_security = ,
    # q_policy_comp_val_immigration = ,
    # q_policy_comp_val_environment = ,
    # q_policy_comp_val_trade = ,
    # q_policy_comp_val_agriculture = ,
    # q_policy_comp_eu_natgov = ,
    # q_eu_trust_val = ,
    # q_policy_comp_pos_market = ,
    # q_policy_comp_pos_security = ,
    # q_policy_comp_pos_immigration = ,
    # q_policy_comp_pos_environment = ,
    # q_policy_comp_pos_trade = ,
    # q_policy_comp_pos_agriculture = ,
    # cj_task1_firstclick = ,
    # cj_task1_lastclick = ,
    # cj_task1_pagesubmit = ,
    # cj_task1_clickcount = ,
    # cj_task1_choice = ,
    # cj_task1_eval_a = ,
    # cj_task1_eval_b = ,
    # cj_task2_firstclick = ,
    # cj_task2_lastclick = ,
    # cj_task2_pagesubmit = ,
    # cj_task2_clickcount = ,
    # cj_task2_choice = ,
    # cj_task2_eval_c = ,
    # cj_task2_eval_d = ,
    # cj_task3_firstclick = ,
    # cj_task3_lastclick = ,
    # cj_task3_pagesubmit = ,
    # cj_task3_clickcount = ,
    # cj_task3_choice = ,
    # cj_task3_eval_e = ,
    # cj_task3_eval_f = ,
    # q_attn_check = ,
    # q_attn_check_text = ,
    # q_pop_elite = ,
    # q_eu_vote_2014 = ,
    # q_eu_vote_2014_text = ,
    # q_eu_longterm_gre = ,
    # q_eu_responsive_gre = ,
    # q_resp_verif = ,
    # q_party_id_text = ,
    # q_party_closeness = ,
    # q_gridlock_manip = ,
    # prime_compliance_firstclick = ,
    # prime_compliance_lastclick = ,
    # prime_compliance_pagesubmit = ,
    # prime_compliance_clickcount = ,
    # q_approval_natgov = ,
    # q_approval_eu = ,
    # q_compliance_verif = ,
    # q_eu_informed_ecb = ,
    # q_eu_trust_ecb = ,
    # q_natcourt_informed = ,
    # prime_court_firstclick = ,
    # prime_court_lastclick = ,
    # prime_court_pagesubmit = ,
    # prime_court_clickcount = ,
    # q_natcourt_1 = ,
    # q_natcourt_2 = ,
    # q_court_pos = ,
    # q_eu_benefit_nat = ,
    # q_eu_pos_personal = ,
    # q_elec_issue_imp_pos = ,
    # q_elec_issue_imp_val = ,
    # q_pol_market = ,
    # q_pol_security = ,
    # q_pol_immigration = ,
    # q_pol_environment = ,
    # q_pol_trade = ,
    # q_pol_agriculture = ,
    # q_lr_gov_nat = ,
    # q_lr_court_nat = ,
    # q_lr_ecb = ,
    # q_eff_internal = ,
    # q_eff_external_resp = ,
    # q_eff_external_nosay = ,
    # q_vote_eu_2014 = ,
    # q_vote_eu_2014_rec = ,
    # q_vote_eu_2014_rec_text = ,
    # q_euint_ecb = ,
    # q_econ_eval_retro = ,
    # q_econ_resp_natgov = ,
    # q_econ_resp_eu = ,
    # q_econ_resp_imm = ,
    # q_econ_resp_global = ,
    # q_news_online = ,
    # q_news_print = ,
    # q_fin_strain = ,
    # q_euint_party_9 = ,
    # q_euint_party_10 = ,
    # q_lr_party_13 = ,
    # prime_respresp_condition = ,
    # prime_gridlock_condition = ,
    # prime_compliance_condition = ,
    # prime_court_condition = ,
    # prime_econblame_condition = ,
    # cj_task_instruction = ,
    # prime_respresp_text = ,
    # prime_gridlock_text = ,
    # prime_compliance_text = ,
    # prime_court_text = ,
    # prime_moreeu_firstclick = ,
    # prime_moreeu_lastclick = ,
    # prime_moreeu_pagesubmit = ,
    # prime_moreeu_clickcount = ,
    # q_vote_turnout_confirm = ,
    # q_vote_choice_intended = ,
    # q_vote_choice_intended_other = ,
    # q_election_challenge_polgroups = ,
    # q_election_impact_eu = ,
    # q_election_importance_self = ,
    # q_news_newspaper = ,
    # q_news_radio = ,
    # q_news_social = ,
    # q_news_internet = ,
    # q_news_personal = ,
    # q_news_other = ,
    # q_news_other_text = ,
    # q_eu_efficacy_understand_fra = ,
    # q_eu_efficacy_care_fra = ,
    # q_eu_efficacy_nosay_fra = ,
    # q_pop_will_fra = ,
    # q_pop_people_fra = ,
    # q_pop_citizen_fra = ,
    # q_pop_reps_fra = ,
    # q_pop_goodevil_fra = ,
    # q_pop_compromise_fra = ,
    # q_dem_compromise_fra = ,
    # q_dem_listen_fra = ,
    # q_tech_experts_fra = ,
    # q_tech_leaders_fra = ,
    # q_party_harm_fra = ,
    # q_people_incompetent_fra = ,
    # q_eu_longterm_fra = ,
    # q_eu_responsive_fra = ,
    # q_eu_imp_nat_econ_fra = ,
    # q_eu_imp_nat_cul_fra = ,
    # q_eu_imp_nat_pol_fra = ,
    # q_eu_abolish_fra = ,
    # q_eu_satisfaction_fra = ,
    # q_euint_pos_fra = ,
    # q_vote_turnout_reason_fra = ,
    # q_vote_choice_past_fra = ,
    # q_vote_choice_past_other_fra = ,
    # q_vote_choice_hypo_fra = ,
    # q_vote_choice_hypo_other_fra = ,
    # q_vote_choice_ep2014_fra = ,
    # q_vote_choice_ep2014_other_fra = ,
    # q_party_id_fra = ,
    # q_party_id_other_fra = ,
    # q_eu_campaign_sources_fra = ,
    # q_eu_campaign_sources_other_fra = ,
    # q_campaign_activity_fra = ,
    # q_campaign_activity_other_fra = ,
    # prime_cjeu_fra_firstclick = ,
    # prime_cjeu_fra_lastclick = ,
    # prime_cjeu_fra_pagesubmit = ,
    # prime_cjeu_fra_clickcount = ,
    # q_cjeu_abolish_fra = ,
    # q_cjeu_satisfaction_fra = ,
    # q_cjeu_pos_fra = ,
    # q_norm_tolerance_fra = ,
    # q_norm_order_fra = ,
    # q_norm_unjust_law_fra = ,
    # q_norm_unvoted_gov_fra = ,
    # q_norm_bypass_law_fra = ,
    # q_norm_gov_bypass_fra = ,
    # q_eval_econ_eur_fra = ,
    # q_eval_econ_nat_fra = ,
    # q_eval_fin_household_fra = ,
    # q_eval_job_fra = ,
    # q_nativ_econ_fra = ,
    # q_nativ_cult_fra = ,
    # q_nativ_3_fra = ,
    # q_nativ_4_fra = ,
    # q_satis_demo_nat_fra = ,
    # q_satis_demo_eu_fra = ,
    # q_nat_int_fra = ,
    # q_eu_int_fra = ,
    # q_nativ_econ_b_fra = ,
    # q_nativ_cult_b_fra = ,
    # q_eu_know_1_fra = ,
    # q_eu_know_2_fra = ,
    # q_eu_know_3_fra = ,
    # q_eu_know_4_fra = ,
    # q_eu_know_5_fra = ,
    # q_eu_informed_com_fra = ,
    # q_eu_informed_cou_fra = ,
    # q_eu_informed_ep_fra = ,
    # q_eu_informed_cjeu_fra = ,
    # q_eu_trust_com_fra = ,
    # q_eu_trust_cou_fra = ,
    # q_eu_trust_ep_fra = ,
    # q_eu_trust_cjeu_fra = ,
    # q_risk_taking_fra = ,
    # q_future_discount_fra = ,
    # prime_moreeu_condition = ,
    # prime_moreeu_text = ,
    # q_vote_exp_rank_party_1 = ,
    # q_vote_exp_rank_party_2 = ,
    # q_vote_exp_rank_party_3 = ,
    # q_vote_exp_rank_party_4 = ,
    # q_vote_exp_rank_party_5 = ,
    # q_vote_exp_rank_party_6 = ,
    # prime_cjeu_fra_condition = ,
    # prime_cjeu_fra_text = ,
    # q_campaign_activity = ,
    # q_campaign_activity_other = ,
    # q_nativ_3 = ,
    # q_nativ_4 = ,
    # q_nativ_econ_b = ,
    # q_nativ_cult_b = ,
  )
```

# Save Full Recoded Wide EU25 Dataset

```{r}
#| label: save

write_rds(
  df_stacked_recoded,
  file = here(
    "data",
    "03_final",
    "eu25games2019.rds"
  )
)
```


# Session Info {#sec-session}

```{r}
#| label: exec-time
#| eval: true

end_time <- Sys.time()
cat("Execution time:", round(end_time - start_time, 2), "seconds\n")
```

```{r}
#| label: session-info
#| eval: true

sessioninfo::session_info()
```
