---
title: |
  Code Notebook 3
subtitle: |
  EU 25 Behavioral Games Survey Experiment 2019: Variable Codebook
author:
  - name: Tristan Muno
    email: tristan.muno@uni-mannheim.de
    affiliations:
      - name: University of Mannheim
        department: School of Social Sciences
date: last-modified
date-format: MMMM D, YYYY
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: true
    code-tools: true
    embed-resources: true
execute:
  echo: true
  warning: true
  eval: true
  message: true
---

# Setup {#sec-setup}

```{r}
#| label: setup
start_time <- Sys.time()

options(width = 80)

p_required <- c(
  "tidyverse", # data wrangling
  "here", # relative paths
  "knitr", # kable tables
  "sessioninfo" # session info
)
packages <- rownames(installed.packages())
p_to_install <- p_required[!(p_required %in% packages)]
if (length(p_to_install) > 0) {
  install.packages(p_to_install)
}
sapply(p_required, require, character.only = TRUE)
rm(p_required, p_to_install, packages)
```

# About this codebook {#sec-about}

This document is generated programmatically from the final dataset and its metadata.
For every variable in `data/03_final/eu25games2019.rds` — taken in the saved column
order — it reports the renamed name and its `_raw` sibling, the original Dynata
code(s), the waves in which the variable carries data, the question wording in every
available language (English first), and the meaning of the values derived directly
from the data (coded ↔ raw mapping for coded variables, range and endpoints for
numeric scales, the category set for categorical variables, or an explicit note for
raw-only / free-text fields).

```{r}
#| label: load-data
df <- read_rds(here("data", "03_final", "eu25games2019.rds"))
crosswalk <- read_csv(
  here("data", "03_final", "variable_crosswalk.csv"),
  show_col_types = FALSE
)
wording <- read_csv(
  here("data", "02_processed", "question_wording_map.csv"),
  show_col_types = FALSE
)

cat("dataset:", nrow(df), "rows x", ncol(df), "columns\n")
```

```{r}
#| label: helpers
# reduce any column to the stem that links a raw var to its derived siblings
deriv_stem <- function(cols) {
  cols |>
    str_remove("^ext_") |>
    str_remove("_pf_(name|id)$") |>
    str_remove("_raw$")
}

# make a string safe for a pipe-table cell (no pipes / newlines)
clean_cell <- function(x) {
  x |>
    as.character() |>
    str_replace_all("[\r\n]+", " ") |>
    str_replace_all("\\|", "/") |>
    str_squish()
}

# truncate a character vector of distinct values to a single readable string
join_capped <- function(x, cap = 12) {
  x <- x[!is.na(x)]
  x <- clean_cell(x)
  x <- x[x != ""]
  if (length(x) == 0) {
    return("—")
  }
  if (length(x) > cap) {
    paste0(paste(head(x, cap), collapse = "; "), " … (+", length(x) - cap, " more)")
  } else {
    paste(x, collapse = "; ")
  }
}

# category label from the variable prefix
var_category <- function(g) {
  p <- str_extract(g, "^[^_]+")
  dplyr::case_when(
    p == "meta" ~ "Metadata & paradata",
    p == "q" ~ "Survey questions",
    p == "cj" ~ "Conjoint experiment",
    p == "prime" ~ "Priming experiment",
    p == "der" ~ "Derived variables",
    p == "ext" ~ "External (Party Facts)",
    .default = "Other"
  )
}

# anchor id safe for HTML
anchor_id <- function(g) {
  paste0("var-", str_replace_all(str_to_lower(g), "[^a-z0-9]+", "-"))
}

english_first <- function(tbl) {
  tbl |>
    mutate(.rank = dplyr::case_when(
      country == "United Kingdom" ~ 1L,
      country == "Ireland" ~ 2L,
      .default = 3L
    )) |>
    arrange(.rank, country) |>
    select(-.rank)
}

# build the ordered list of variable groups (saved column order)
all_cols <- names(df)
gk <- deriv_stem(all_cols)
gk[str_detect(all_cols, "^cj_att_pos_")] <- "cj_attr_order"
groups <- tibble(col = all_cols, gk = gk, ord = seq_along(all_cols)) |>
  group_by(gk) |>
  summarise(first = min(ord), cols = list(col), .groups = "drop") |>
  arrange(first)

# per-column class string
col_class <- map_chr(df, ~ class(.x)[1])

cat("variable groups:", nrow(groups), "\n")
```

# Variables {#sec-variables}

```{r}
#| label: codebook
#| results: asis
cur_cat <- ""

for (i in seq_len(nrow(groups))) {
  g <- groups$gk[i]
  members <- groups$cols[[i]]

  # category header
  cat_g <- var_category(g)
  if (cat_g != cur_cat) {
    cat("\n\n## ", cat_g, "\n\n", sep = "")
    cur_cat <- cat_g
  }

  cat("\n\n### `", g, "` {#", anchor_id(g), "}\n\n", sep = "")

  # ---- classify member columns ----------------------------------------------
  raw_col <- members[str_detect(members, "_raw$")]
  raw_col <- if (length(raw_col) > 0) raw_col[1] else NA_character_
  coded_col <- if (g %in% members) g else NA_character_
  ext_name <- members[str_detect(members, "^ext_.*_pf_name$")]
  ext_id <- members[str_detect(members, "^ext_.*_pf_id$")]
  pos_cols <- members[str_detect(members, "^cj_att_pos_")]

  primary <- dplyr::coalesce(
    coded_col, raw_col,
    members[!str_detect(members, "^ext_|^cj_att_pos_")][1],
    members[1]
  )

  # ---- crosswalk lookup ------------------------------------------------------
  xw <- crosswalk |> filter(renamed_var == g)
  orig_codes <- xw |>
    distinct(original_col) |>
    filter(!is.na(original_col)) |>
    pull(original_col)
  eng_wording <- xw |>
    distinct(question_wording) |>
    filter(!is.na(question_wording)) |>
    pull(question_wording)

  # ---- waves present (empirical) ---------------------------------------------
  waves_present <- df |>
    filter(!is.na(.data[[primary]])) |>
    distinct(meta_wave) |>
    arrange(meta_wave) |>
    pull(meta_wave)

  # ---- metadata table --------------------------------------------------------
  meta_tbl <- tibble::tribble(
    ~Field, ~Value,
    "Variable (renamed)", paste0("`", g, "`"),
    "Columns in dataset", paste0("`", members, "` (", col_class[members], ")", collapse = ", "),
    "Raw column", if (is.na(raw_col)) "— (no `_raw` sibling)" else paste0("`", raw_col, "`"),
    "Original Dynata code(s)", if (length(orig_codes) == 0) "—" else paste(orig_codes, collapse = ", "),
    "Waves present", if (length(waves_present) == 0) "—" else paste(waves_present, collapse = ", "),
    "English wording", if (length(eng_wording) == 0) "—" else clean_cell(eng_wording[1])
  )
  cat(knitr::kable(meta_tbl, format = "pipe"), sep = "\n")
  cat("\n\n")

  # ---- multilingual wording --------------------------------------------------
  if (length(orig_codes) > 0) {
    wtab <- wording |>
      filter(col_name %in% orig_codes) |>
      distinct(country, wording) |>
      filter(!is.na(wording))
    if (nrow(wtab) > 0) {
      wtab <- english_first(wtab) |>
        transmute(Country = country, Wording = clean_cell(wording))
      cat("**Question wording by language**\n\n")
      cat(knitr::kable(wtab, format = "pipe"), sep = "\n")
      cat("\n\n")
    }
  }

  # ---- value / scale meaning -------------------------------------------------
  cat("**Values**\n\n")

  if (!is.na(coded_col)) {
    v <- df[[coded_col]]
    nd <- dplyr::n_distinct(v[!is.na(v)])

    if (!is.na(raw_col) && (is.numeric(v) || is.integer(v)) && nd > 25) {
      # continuous numeric coded from a raw string
      rng <- range(v, na.rm = TRUE)
      cat(
        "Numeric, derived from the raw string. Range **", rng[1], "–", rng[2],
        "**; ", nd, " distinct non-missing values; ",
        sum(is.na(v)), " missing (don't-know / refusal / not asked).\n\n",
        sep = ""
      )
    } else if (!is.na(raw_col)) {
      # coded <-> raw empirical mapping
      mp <- tibble(
        coded = as.character(v),
        raw = as.character(df[[raw_col]])
      ) |>
        filter(!(is.na(coded) & is.na(raw))) |>
        group_by(coded) |>
        summarise(
          n = dplyr::n(),
          raw_values = join_capped(unique(raw)),
          .groups = "drop"
        ) |>
        mutate(coded = ifelse(is.na(coded), "NA (missing / don't-know)", coded)) |>
        arrange(coded != "NA (missing / don't-know)", coded) |>
        transmute(`Coded value` = coded, `n` = n, `Raw value(s)` = raw_values)
      cat(knitr::kable(mp, format = "pipe"), sep = "\n")
      cat("\n\n")
    } else if (is.numeric(v) || is.integer(v)) {
      rng <- range(v, na.rm = TRUE)
      cat(
        "Numeric. Range **", rng[1], "–", rng[2], "**; ", nd,
        " distinct non-missing values; ", sum(is.na(v)), " missing.\n\n",
        sep = ""
      )
    } else if (is.logical(v)) {
      tb <- as.data.frame(table(v, useNA = "ifany"))
      names(tb) <- c("Value", "n")
      cat(knitr::kable(tb, format = "pipe"), sep = "\n")
      cat("\n\n")
    } else {
      lv <- df |>
        count(.data[[coded_col]], name = "n") |>
        rename(Value = 1) |>
        mutate(Value = ifelse(is.na(Value), "NA (missing)", as.character(Value))) |>
        arrange(desc(n))
      cat("Categorical, ", nrow(lv), " distinct values:\n\n", sep = "")
      cat(knitr::kable(head(lv, 60), format = "pipe"), sep = "\n")
      cat("\n\n")
    }

    # position integers attached to cj_attr_order
    if (length(pos_cols) > 0) {
      cat(
        "Companion display-slot integers (1–7): ",
        paste0("`", pos_cols, "`", collapse = ", "), ".\n\n",
        sep = ""
      )
    }
  } else if (length(ext_name) > 0) {
    # party-name variable harmonised to Party Facts (no plain coded sibling)
    pf <- df[[ext_name[1]]]
    nd <- dplyr::n_distinct(pf[!is.na(pf)])
    cat(
      "Party identity is harmonised to Party Facts in `", ext_name[1],
      "` (name) and `", ext_id[1], "` (id). The `_raw` column holds the original ",
      "party spelling (free text). ", nd, " distinct Party Facts names; examples: ",
      join_capped(unique(pf), cap = 15), ".\n\n",
      sep = ""
    )
  } else if (!is.na(raw_col)) {
    rv <- df[[raw_col]]
    nd <- dplyr::n_distinct(rv[!is.na(rv)])
    cat(
      "Raw only (kept verbatim, no coded sibling). ", nd,
      " distinct non-missing values. Examples: ",
      join_capped(unique(rv), cap = 8), ".\n\n",
      sep = ""
    )
  } else {
    # no coded, no raw: metadata / paradata / design column
    v <- df[[primary]]
    if (is.numeric(v) || is.integer(v)) {
      rng <- suppressWarnings(range(v, na.rm = TRUE))
      cat(
        "Numeric/paradata. Range **", rng[1], "–", rng[2], "**; ",
        dplyr::n_distinct(v[!is.na(v)]), " distinct non-missing values.\n\n",
        sep = ""
      )
    } else if (inherits(v, "POSIXct") || inherits(v, "Date")) {
      rng <- suppressWarnings(range(v, na.rm = TRUE))
      cat("Timestamp. Range **", as.character(rng[1]), "** to **",
        as.character(rng[2]), "**.\n\n",
        sep = ""
      )
    } else if (is.logical(v)) {
      tb <- as.data.frame(table(v, useNA = "ifany"))
      names(tb) <- c("Value", "n")
      cat(knitr::kable(tb, format = "pipe"), sep = "\n")
      cat("\n\n")
    } else {
      nd <- dplyr::n_distinct(v[!is.na(v)])
      cat(
        nd, " distinct non-missing values. Examples: ",
        join_capped(unique(v), cap = 10), ".\n\n",
        sep = ""
      )
    }
  }
}
```

# Session Info {#sec-session}

```{r}
#| label: exec-time
#| eval: true
end_time <- Sys.time()
cat("Execution time:", round(end_time - start_time, 2), "seconds\n")
```

```{r}
#| label: session-info
#| eval: true
sessioninfo::session_info()
```
